### 2021-10-19 docs/pap/pap.Rmd
compendium set-up

---
title: "Pre-Analysis Plan: The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
output: 
  pdf_document:
    toc: yes
    number_sections: true
editor_options: 
  chunk_output_type: console
bibliography: references.bib
urlcolor: blue
linkcolor: blue
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{amsmath}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
   - \usepackage[utf8]{inputenc}
---
```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
#library(printr)
library(tidyverse)
library(kableExtra)
options(kableExtra.latex.load_packages = FALSE)
```

\newpage

# Expectations

**Ethnic Conception hypothesis** (_H1_):  All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is lower for an ethnic conception of the 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger).e.

**Exclusive National Identity hypothesis** (_H2a_):  All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is higher for an ethnic conception of 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger) when the respondent adheres to an exclusive national identity.

**Far Right Party ID hypothesis** (_H2b_): All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is higher for an ethnic conception of 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger) when the respondent votes for a far right party.

# Research Desing and Protocol

## Sample
We will conduct the survey experiment in Germany in October 2021 -- approximately three weeks after the general elections of 26 September 2021.
The sample, recruited through [Respondi](https://www.respondi.com/EN/), will consist of 8,000 participants (based on the power analysis presented in Figure \ref{fig:power}) of 18 years and older.
Respondi works with opt-in respondents, so we have implemented quota on age, gender, and education.
Moreover, we measure some more demographic background variables (see [Section 3.2](\#control-variables)).
Balance checks will be conducted to demonstrate whether certain categories are over represented in a certain experimental group.
The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the \textit{Vrije Universiteit Amsterdam} (see the approval [here](LINK)).
To ensure good quality of our data, two attention checks (discussed in more detail in [Section 3.3](\#attention-checks)) are included.
Each respondent failing the attention check will be excluded and replaced with another 'good' response.

## Experimental Protocol
The study is conducted online and in German.
Participants are told that they are taking part in a survey to get an overview of how German people form their views on politics.
After reading an informed consent message participants are forwarded to the main questionnaire (or the survey will be terminated if they do not agree to the consent form).

First, participants complete a set of demographic variables (i.e. income, employment, and degree of urbanization).
This block ends with one of the two attention checks included in this survey.
When participants fail this attention check, a warning appears asking them to read the question again
carefully  and  to  answer  again.
Thereafter, a set of background variables are asked on their stances on the political issues, some are used in the experiment (i.e. top tax, speed limit, education, legalization of Cannabis), their political interest and knowledge, as well as on their ideological position -- the full codeboek can be viewed [here](#).[^1]
Before entering the experimental condition, respondents get a second attention check.
Only when they have answered it correctly, they enter the first round of the experiment -- if they fail to answer the question correctly, they are thrown out of the survey.
The stimuli in the experiment are to translate the word _people_ into it's civic conception (i.e. _Bürger_) or it's ethnic conception (i.e. _Volk_) for the items 2, 3, and 4 of the populism attitude scale [@akkerman2014populist].

[^1]: Participants are also part of another experiment -- see details [here](https://github.com/MarikenvdVelden/willingness-to-accept-compromises).

## Power Analysis
As detailed in [Section 4](#analysis), we conduct an OLS regression for each of the dependent variables (i.e. items 2--4): a) "The people, not politicians, should make the most important political decisions"; b) "The politicians in the German Bundestag need to follow the will of the people"; and c) "The political differences between elites and the people are greater than the differences among citizens".
  The manipulation, i.e. the civic conception (i.e. _Bürger_) or th ethnic conception (i.e. _Volk_) as well as respondents national identity and far right party ID are the main independent variables.

To calculate power for the hypotheses, the R package `DeclareDesign` is used [@blair2019declaring].
The effect sizes are between $b = 0.2$ and $b = 0.1$ -- i.e. a small effect visualized by the purple and blue lines in Figure \ref{fig:power1}.
The hypothesis are directional, Figure \ref{fig:power1} therefore displays one-tailed tests with $\alpha = 0.05$.
The power analysis shows that testing hypotheses 1 and 2 requires a sample size of $8,000$ participants (x-axis) to reach very high levels of power, i.e. $>95\%$, (indicated by the black dashed line in Figure \ref{fig:power}).

```{r power-example, eval = FALSE, echo = TRUE}
  source(here::here("docs/pre-analysis-plan/poweranalysis.R"))
```

```{r power, fig.align = 'center', out.width = "100%", fig.cap = "\\label{fig:power1}Power Analysis", fig.topcaption=TRUE}
  knitr::include_graphics(here::here("report/figures/power_analysis.png"))
```

# Measures

## Dependent Variables
We rely on the three items in the populism scale that mention the people: a) "The people, not politicians, should make the most important political decisions"; b) "The politicians in the German Bundestag need to follow the will of the people"; and c) "The political differences between elites and the people are greater than the differences among citizens". All items are measured on a 5-point Likert-scale: `very much disagree`, `disagree`, `neutral`, `agree`, `very much agree`.

See Table \ref{tab:dv} for the exact phrasing of the question.

```{r dv, topcaption=TRUE}
d <- tibble(Variable = c("Item 2 (DV1)",
                         "Item 3 (DV2)",
                         "Item 4 (DV3)"), 
            `Wording ENG` = c("The people, not politicians, should make the most important political decisions","he politicians in the German Bundestag need to follow the will of the people", "The political differences between elites and the people are greater than the differences among citizens"),
            `Wording DE` = c("[Die Bürger/Das Volk], und nicht die Politiker, sollte(n) die wichtigsten politischen Entscheidungen treffen", "Die Abgeordneten des Deutschen Bundestags müssen dem Willen [der Bürger/des Volkes] Folge leisten", "Die politischen Unterschiede zwischen den Eliten und [den Bürgern/dem Volk] sind größer als die Unterschiede (zwischen Bürgern)"))

kbl(d, booktabs =T, caption = "\\label{tab:dv}Survey Questions - DV") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "7cm") %>%
  column_spec(3, width = "7cm")

```

## Treatment
Respondents are randomly assigned to the populism items translated into German using either the civic conception (i.e. _Bürger_) or the ethnic conception (i.e. _Volk_).

&nbsp;

## Control Variables

As control variables, the following _demographics_ are measured: gender, age, education, geographical region, level of urbanness, vote choice in the 2021 parliamentary elections, employment, and income.
For the analysis, only variables that are unbalanced over the experimental conditions will be included.
Table \ref{tab:demographics} gives an overview of the questions asked in the survey as well as their English translations.

- _Gender_ is measured as `sex` based on the advice of Kieskompas. The answer categories are `Male` (value of `1`), `Female` (value of `0`), and `No answer` (value of `999`).

- _Age_ is measured using 6 categories: `17 or younger`, `18--29`, `30--39`, `40--49`, `50--59`, `60--74`.

- _Education_ is measured as the highest successfully completed level of education, recoded into four categories: `low`, `middle`, `high`, and `none`.
I create dummy variables for each level of education with the lowest category as base category.

- _Urbanness_ Respondents are asked for what the type of location they live: `big city`, `suburb of a large city`, `middle-szed or small city`, `rural village`, `detached house in the countryside`, `don't know/won't say`.

- _Vote Recall_ Respondents were asked which party they voted for in the last election with their second vote. Answering categories were: `CDU/CSU`, `SPD`, `AfD`, `FDP`, `DIE LINKE`, `BÜNDNIS 90/DIE GRÜNEN`, `Other party:`, `I didn't vote/wasn't eligble to vote`, `Don't know/won't say`.

- _Employment_ Respondents were asked which category of employment -- `Full-time employed`, `Part-time employed`, `Entrepreneur`, `Unemployed and searching for a job`, `Unemployed and not searching for a job or incapacitated`, `Housewife/Househusband or else`, `Retired`, `Student or full-time education` -- applied most to them.

- _Income_ Respondents were questioned on their monthly income in bins of €500 -- `€500 or less`, `€501-€1000`, `€1001-€1500`, `€1501-€2000`, `€2001-€2500`, `€2501-€3000`, `€3001-€3500`, `€3501-€4000`, `€4501-€7500`, `€7501 or more` -- as well as giving them the options of `won't  say` and `don't know`.

- _Geographical region_ is measured using the same questions as the [German Longitudinal Election Study](https://www.gesis.org/wahlen/gles), asking respondents where they are born and currently live, differentiating between the different German provinces (_Bundesl{\"a}nder_): Baden-W{\"u}rtemberg, Bavaria, Berlin, Brandenburg, Bremen, Hamburg, Hessen, Lower Saxony, Mecklenburg-Western Pomerania, North Rhine-
Westphalia, Rhineland-Palatinate, Saarland, Saxony, Saxony-Anholt, Schleswig-Holstein, and Thuringia.

```{r demographics, topcaption=TRUE}
d <- tibble(Variable = c("gender (D1)", "age (D2)", "education (D3)",
                         "geographical-region (D4)", "vote-recall2 (D6)", "employment (D7)",
                         "income (D8)", "living-place (D9)", "birth-place (D10)"), 
            `Wording ENG` = c("Which gender do you feel you belong to?", "To which of the following age groups do you belong?",
                              "What is your highest educational qualification?", 
                             "Which of the following categories best describes where you live?",
                             "Which party did you vote for with your second vote in the last federal election in September 2021?",
                             "Now we would like to ask you something about your employment. Which of this list applies to you?",
                              "What is the total monthly net income of your household? This refers to the sum that remains after deducting taxes and social security contributions.",
                             "In which federal state or on the territory of which present federal state do you currently live?",
                              "And in which federal state or on the territory of which present federal state were you born?"),
            `Wording DE` = c("Welchem Geschlecht fühlen Sie sich zugehörig?", 
                             "Zu welcher der nachfolgenden Altersgruppen gehören Sie?",
                             "Was ist Ihr höchster Bildungsabschluss?",
                             "Welche der folgenden Kategorien beschreibt am besten, wo Sie wohnen?",
                             "Welche Partei haben Sie bei der letzten Bundestagswahl im September 2021 mit Ihrer Zweitstimme gewählt?",
                             "Nun möchten wir Sie gerne etwas zu Ihrer Erwerbstätigkeit fragen. Was von dieser Liste trifft auf Sie zu?",
                             "Wie hoch ist das monatliche Netto-Einkommen Ihres Haushaltes insgesamt? Gemeint ist die Summe, die nach Abzug von Steuern und Sozialversicherungsbeiträgen übrig bleibt.",
                             "Im welchen Bundesland bzw. auf dem Gebiet welches heutigen Bundeslandes wohnen Sie derzeit?",
                             "Und in welchem Bundesland bzw. auf dem Gebiet welches heutigen Bundeslandes wurden Sie geboren?"))

kbl(d, booktabs =T, caption = "\\label{tab:demographics}Survey Questions - Demographics") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "7cm") %>%
  column_spec(3, width = "7cm")

```

In addition, pre-treatment, respondents' ideological position, political knowledge, interest, and attitude towards national identity are measured (see Table \ref{tab:pret}).
Those variables will only be included in the analyses if balance checks indicate they are necessary.
Moreover, the variables will be used to explore heterogeneous relationships.

- _Ideological position_ is measured using an 11-point scale ranging from left (`0`) to right (`10`).

- _Exclusive national identity_ is measured with four statements ("being born in Germany", "having German ancestors", "being able to speak German", "adhering to German traditions and customs") on a 5-point Likert-scale: `very much disagree`, `disagree`, `neutral`, `agree`, `very much agree`. If `Cronbach's` $\alpha =>0.8$, we will construct an additive scale for this measure.
When `Cronbach's` $\alpha <0.8$, we will add the statement as seperate dependent variables in the multiverse analysis.

```{r pret, topcaption=TRUE}
d <- tibble(Variable = c("political-knowledge1 (PT4)", "political-knowledge2 (PT5)", "political-knowledge3 (PT6)", "political-interest (PT7)","RILE (PT8)", "Exclusive national identity (HT4)", "Exclusive national identity (HT4-1)", "Exclusive national identity (HT4-2)", "Exclusive national identity (HT4-3)", "Exclusive national identity (HT4-4)" ), 
            `Wording ENG` = c("In the federal election, you have two votes, a first vote and a second vote. How is that actually, which of the two votes is decisive for the distribution of seats in the Bundestag?",
                             "Now we would like to know from you, from what percentage of the second votes a party can send deputies in any case in the Bundestag?",
                             "And can you say approximately what the current unemployment rate is in Germany? Is it lower or higher than 10 percent?", 
                             "Once speaking in general terms: How interested are you in politics - very strongly, strongly, moderately, less strongly, or not at all?",
                            "In politics, people often talk about 'left' and 'right.' Where would you classify yourself?",
                            "Some people think that the following points are important to be truly German. Others do not think they are important. How important do you think the following points are to being German?", "being born in Germany", "having German ancestors", "being able to speak German", "adhering to German traditions and customs"),
            `Wording DE` = c("Bei der Bundestagswahl haben Sie ja zwei Stimmen, eine Erststimme und eine Zweitstimme. Wie ist das eigentlich, welche der beiden Stimmen ist ausschlaggebend für die Sitzverteilung im Bundestag?",
                             "Jetzt möchten wir gerne von Ihnen wissen, ab wie viel Prozent der Zweitstimmen eine Partei auf jeden Fall Abgeordnete in den Bundestag entsenden kann? ",
                             "Und können Sie ungefähr sagen, wie hoch die derzeitige Arbeitslosenquote in Deutschland ist? Ist sie niedriger oder höher als 10 Prozent?", 
                             "Einmal ganz allgemein gesprochen: Wie stark interessieren Sie sich für Politik – sehr stark, stark, mittelmäßig, weniger stark oder überhaupt nicht?",
                            "In der Politik reden die Leute häufig von 'links' und 'rechts'. Wo würden Sie sich selbst einordnen?",
                            "Manche Leute meinen, dass die folgenden Punkte wichtig sind, um wirklich deutsch zu sein. Andere halten diese nicht für wichtig. Für wie wichtig halten Sie die folgenden Punkte, um deutsch zu sein?", "in Deutschland geboren sein", "deutsche Vorfahren haben", "deutsch sprechen können", "sich an deutsche Traditionen und Gepflogenheiten halten"))

kbl(d, booktabs =T, caption = "\\label{tab:pret}Survey Questions - PreTreatment Questions") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "7cm") %>%
  column_spec(3, width = "7cm")
```

- _Political knowledge_ is measured with three items. First, respondents are asked which of the two votes is determinative for the seat distribution in parliament: `first vote`, `second vote`, `both`, `don't know`. Secondly, respondents are asked about the electoral threshold. Last, respondents are asked whether or not the unemployment rate is over ten procent.

- _Political interest_ is measured by asking people how strongly they are interested in politics using a 5-point Likert-scale (`very strong`, `strong`, `medium`, `less strong`, `not at all`) and a `don't know/won't say` option.

## Attention Checks
We include two attention checks in the survey.
The first one is after the demographic covariates, the second one is asked just before respondents enter the round of the experimental treatments.
The attention checks are taken from @berinsky2014separating and adapted to the German context by the authors.
If a respondents fails the first attention check, a warning appears and the respondent can only continue with the survey once the respondent has correctly answered the question correctly.
The second attention check also has a warning -- meaning that respondents have to select two options -- but if they fail to correctly pass the check, they are excluded.
Each excluded respondent due to failing an attention check is replaced with another ``good respondent".

**Attention Check 1**  When a big news story breaks people often go online to get up-to-the-minute details on what is going on.
We want to know which websites people trust to get this information.
We also want to know if people are paying attention to the question.
To show that you have read this much, please ignore the question and select BILD-Zeitung and Süddeutsche Zeitung as your two answers.
When there is a big news story, which is the one news website you would visit first? (Please only choose one).
Eight (German) news outlets are provided to choose from.
Respondents pass the attention check if they select _BILD-Zeitung_ and _Süddeutsche Zeitung_.

**Attention Check 2**:
We would like to get a sense of your general preferences.
Most  modern  theories  of  decision  making  recognize  that  decisions  do  not take  place  in  a  vacuum.
Individual  preferences  and  knowledge,  along  with  situational variables can greatly impact the decision process.
To demonstrate that you've read this much,  just  go  ahead  and  select  both  red  and  green  among  the  alternatives  below,  no matter what your favourite color is.  Yes, ignore the question below and select both of those options.
What is your favourite color?
Six colors are provided to choose from, respondents pass the attention check if they select red and green.

## Exclusion Criteria
Participants are required to respond to each question.
Participants who fail the second attention check will be excluded but replaced by another participant.

# Analysis
We test the hypotheses formulated in [Section 1](#expectations) by fitting linear multivariate regressions separately for the two issues.
In each model, we will estimate the coefficient for whether the party compromised or remained steadfast (H1), whether or not the coalition talks continued (H2), and the interaction of compromise and the outcome (H3).
We will only add control variables in the analyses that are unbalanced, as explained in [Section 4.1](#balance-checks).

## Balance Checks
We will conduct a balance test based on demographics (age, gender, education, geographical region, level of urbanness,employment, and income), vote choice in the 2021 parliamentary elections, ideological self-placement, political knowledge, political interest, party identity strength, and positions on and salience of the three issues, using the `cobalt` R package [@greifer2021]. 
If the groups are unbalanced on one of these variables -- i.e. standardized mean differences $<0.05$ -- I will add the covariates to the analyses.
I will use the code below to conduct the balance tests (see [here](https://github.com/MarikenvdVelden/compromise-punish/tree/main/src/analysis/balance-test.R) for the R script).

```{r balance, eval=FALSE, echo = TRUE}
covs <- d %>%
  mutate(treatment = populism) %>%
  select(populism, D1:D10, PT1:PT8, HT4)

balanced <-bal.tab(treatment ~ factor(D1) + D2 +
                     factor(D3) + D4 + D5 + 
                     factor(D6) + D7 + D8 + D9 +
                     D10 + PT4 + PT5 + PT6 + PT7 + 
                     PT8 + HT4,
                     data = covs,
          thresholds = c(m = 0.05))[[1]] 
```

## Hypothesis 1
We test the _Ethnic Conception hypothesis_, we will conduct a difference in means for the group who received the ethnic and the civic question wording, for all populist items containing a reference to _the people_ -- see code chunck below.

```{r h1, eval = FALSE, echo = TRUE}
source(here::here("src/lib/functions.R"))

df %>% 
  mutate(ethnic == if_else(populist=="Volk", "Ethnic", "Civic")) %>%
  select(`POST-2`, `POST-3`, `POST-4`, ethnic) %>%
  gather(key = variable, value = value, -ethnic) %>%
  group_by(ethnic, variable) %>%
  summarise(value = list(value)) %>% 
  spread(ethnic, value) %>% 
  group_by(variable) %>% 
  mutate(p_value = t.test(unlist(Ethnic), unlist(Civic))$p.value,
         t_value = t.test(unlist(Ethnic), unlist(Civic))$statistic)
```

## Hypothesis 2a

We test the _Exclusive National Identity hypothesis_ using the equation and the code chunk below.
The coefficient of $\beta_{1}$ denotes the difference in populist attitude for civic and ethnic conceptions of the people.
The coefficient of $\beta_{2}$ denotes the difference in populist attitude for different levels of national identity.
The coefficient of $\beta_{3}$ is the interaction of the  $\beta_{1}$ and  $\beta_{2}$.
If the Average Marginal Effect of $\beta_{1}$ is positive and statistically significant for higher values of $\beta_{2}$ (i.e. stronger national identity), then H2a will be confirmed.

$$\begin{aligned}
    \hat{Y}_{item} = \beta_{0} + \beta_{1}Ethnic  +
    \beta_{2}National \ Identity + \beta_{3} Ethnic * National \ Identity + \nonumber \\
    \beta_{4}Unbalanced \ Covariates + \varepsilon
  \end{aligned}$$

```{r h2a, eval = FALSE, echo = TRUE}
source(here::here("src/lib/functions.R"))

df <- d %>% 
  mutate(ethnic == if_else(populist=="Volk", "Ethnic", "Civic"))  %>%
  select(`POST-2`, ethnic, HT4)
h2a_1 <- lm(`POST-2` ~  ethnic * HT4,
                   data = df)

df <- d %>% 
  mutate(ethnic == if_else(populist=="Volk", "Ethnic", "Civic"))  %>%
  select(`POST-3`, ethnic, HT4)
h2a_2 <- lm(`POST-3` ~  ethnic * HT4,
                   data = df)

df <- d %>% 
  mutate(ethnic == if_else(populist=="Volk", "Ethnic", "Civic"))  %>%
  select(`POST-4`, ethnic, HT4)
h2a_3 <- lm(`POST-4` ~  ethnic * HT4,
                   data = df)
```

## Hypothesis 2b

We test the _Far Right Party ID hypothesis_ using the equation and the code chunk below.
The coefficient of $\beta_{1}$ denotes the difference in populist attitude for civic and ethnic conceptions of the people.
The coefficient of $\beta_{2}$ denotes the difference in populist attitude for whether or not a respondent has voted for a far right party.
The coefficient of $\beta_{3}$ is the interaction of the  $\beta_{1}$ and  $\beta_{2}$.
If the Average Marginal Effect of $\beta_{1}$ is positive and statistically significant for higher values of $\beta_{2}=1$ (i.e. voted for a radical right party), then H2b will be confirmed.

$$\begin{aligned}
    \hat{Y}_{item} = \beta_{0} + \beta_{1}Ethnic  +
    \beta_{2}Far \ Right \ Party \ ID + \beta_{3} Ethnic * Far \ Right \ Party \ ID + \nonumber\\
    \beta_{4}Unbalanced \ Covariates + \varepsilon
  \end{aligned}$$

```{r h2b, eval = FALSE, echo = TRUE}
source(here::here("src/lib/functions.R"))

df <- d %>% 
  mutate(afd_vote == if_else(`D6-3`==1, 1, 0),
         ethnic == if_else(populist=="Volk", "Ethnic", "Civic"))  %>%
  select(`POST-2`, ethnic, afd_vote)
h2a_1 <- lm(`POST-2` ~  ethnic * afd_vote,
                   data = df)

df <- d %>% 
  mutate(afd_vote == if_else(`D6-3`==1, 1, 0),
         ethnic == if_else(populist=="Volk", "Ethnic", "Civic"))  %>%
  select(`POST-3`, ethnic, afd_vote)
h2a_2 <- lm(`POST-3` ~  ethnic * afd_vote,
                   data = df)

df <- d %>% 
  mutate(afd_vote == if_else(`D6-3`==1, 1, 0),
         ethnic == if_else(populist=="Volk", "Ethnic", "Civic"))  %>%
  select(`POST-4`, ethnic, afd_vote)
h2a_3 <- lm(`POST-4` ~  ethnic * afd_vote,
                   data = df)
```

## Statistical Significance
All the hypotheses are directional, and therefore all of the tests will be one-tailed.
We will use an $\alpha$-value of $0.05$ as the value for statistical significance in all models above.

\newpage
# References

### 2021-10-19 src/data-processing/data_preparations.Rmd
compendium set-up

---
title: "Preprare Data"
output: 
  github_document:
  toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(printr)
library(rmarkdown)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2021-10-19 docs/pap/power_analysis.R

@@ -1,0 +1,48 @@
+# Power Analysis
+rm(list = ls())
+library(tidyverse)
+library(DeclareDesign)
+library(scales)
+library(here)
+
+#H1 + H2: pooled over parties
+N <- 100
+assignment_prob <- 0.5 # 1 out of 2: bürger vs. volk
+treatment_effect <- 0.1
+
+population <- declare_population(N = N, u = rnorm(N))
+potential_outcomes <- declare_potential_outcomes(Y_Z_0 = u, Y_Z_1 = Y_Z_0 + treatment_effect)
+estimand <- declare_estimand(ATE = mean(Y_Z_1 - Y_Z_0))
+assignment <- declare_assignment(prob = assignment_prob)
+reveal_Y <- declare_reveal()
+estimator <- declare_estimator(Y ~ Z, estimand = estimand, term="Z", model=lm)
+two_arm_design <- population + potential_outcomes + estimand + 
+  assignment + reveal_Y + estimator
+designs <- redesign(design=two_arm_design, N=seq(6000,10000,1000), treatment_effect=seq(0.1,0.2,0.1))
+
+alpha <- .05
+my_diagnosands <- declare_diagnosands(power.onetailed=mean(p.value<alpha), keep_defaults=TRUE)
+diagnosis1 <- diagnose_designs(designs,diagnosands=my_diagnosands)
+diagnosis <- diagnosis1$diagnosands_df
+diagnosis1  <- diagnosis %>% 
+  select(N, treatment_effect, power.onetailed) %>%
+  mutate(id = "Power-Analysis for H1 and H2")
+
+p1 <- diagnosis1 %>%
+  ggplot(aes(x=N, y=power.onetailed, group=factor(treatment_effect), colour=factor(treatment_effect))) +
+  geom_line() +
+  geom_hline(yintercept=0.95, linetype="dashed") +
+  geom_hline(yintercept=0.8, linetype="dashed", color = "grey") +
+  geom_vline(xintercept = 8000,linetype="dotdash", color = "darkgrey") +
+  labs(x = "Number of Respondents", y = "Power: One-Tailed",
+       title = "Issue Specific Analysis",
+       subtitle = "Various Levels of Treatment Effect") +
+  scale_y_continuous(labels=percent) +
+  theme_minimal() +
+  scale_color_viridis_d() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
[…]

### 2021-10-19 src/data-processing/prep_data.Rmd
update

---
title: 'Prepare Data'
author: 
output: 
  github_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(printr)
options(digits = 2)
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Tidy Data](#tidy-data)
- [Save Data for Analysis](#save-data-for-analysis)
- [Check Missing Values](#check-missing-values)
- [Visualization of Data](#visualization-of-data)
  - [Dependent Variable](#dependent-variable)
  - [Treatment Conditions](#treatment-conditions)
  - [Correlations Matrix](#correlations-matrix)

## Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
renv::snapshot()
```

## Tidy Data
This code chuck downloads the data from Qualtrics using the API and cleans the raw data.

```{r "get data from Qualtrics", results="hide"}
source(here("src/data-processing/tidy_data.R"))
source(here("src/data-processing/Urbaness.R"))
```

## Save Data for Analysis
```{r "save data",eval=FALSE}
save(d, file = here("data/intermediate/cleaned_data.RData"))
```

## Visualization of Data

### Dependent Variable
```{r "Dependent Variable", echo=F, fig.width=10, fig.height=8}
d <- d %>%
  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
               values_to = "name",
               names_to = "issue") %>%
  drop_na(name) %>%
  mutate(issue = recode(issue, 
                        name_C = "COVID",
                        name_D = "Defense",
                        name_E = "Education",
                        name_I = "Immigration")) %>%
  pivot_longer(cols = c(PT_D1, PT_E1, PT_C1, PT_I1),
               values_to = "PT1",
               names_to = "issue1") %>%
  drop_na(PT1) %>%
  mutate(issue1 = recode(issue1, 
                        PT_C1 = "COVID",
                        PT_D1 = "Defense",
                        PT_E1 = "Education",
                        PT_I1 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D2, PT_E2, PT_C2, PT_I2),
               values_to = "PT2",
               names_to = "issue2") %>%
  mutate(issue2 = recode(issue2, 
                        PT_C2 = "COVID",
                        PT_D2 = "Defense",
                        PT_E2 = "Education",
                        PT_I2 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D3, PT_E3, PT_C3, PT_I3),
               values_to = "PT3",
               names_to = "issue3") %>%
  mutate(issue3 = recode(issue3, 
                         PT_C3 = "COVID",
                         PT_D3 = "Defense",
                         PT_E3 = "Education",
                         PT_I3 = "Immigration")) %>%
  pivot_longer(cols = c(PT_D4, PT_E4, PT_C4, PT_I4),
               values_to = "PT4",
               names_to = "issue4") %>%
  mutate(issue4 = recode(issue4, 
                         PT_C4 = "COVID",
                         PT_D4 = "Defense",
                         PT_E4 = "Education",
                         PT_I4 = "Immigration"),
        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
  filter(check == 1)

d %>%
  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
  mutate(PT1 = PT1 * 2) %>%
  #mutate_at(c("PT1", "PT2", "PT3", "PT4"), ~(scale(.) %>% as.vector)) %>%
  pivot_longer(cols = PT1:PT4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                       PT1 = "DV: Trait Evaluation",
                       PT2 = "DV: Favorability",
                       PT3 = "DV: Representation",
                       PT4 = "DV: Career Prospects")) %>%
  group_by(issue, dvs) %>%
  summarise(means = mean(value, na.rm=T),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev)) %>% 
  ggplot(aes(x = dvs, y = means, colour = issue,
             ymin = lower, ymax = upper, label = issue)) +
  geom_point(position = position_dodge(.5)) + 
  geom_errorbar(position = position_dodge(.5), width = 0) +
  geom_text(aes(y = upper +.5), 
            position = position_dodge(.5),na.rm = TRUE) + 
  labs(y = "0 (negative) - 10 (positive)", 
       x = "") +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  theme_minimal() +
  scale_color_manual(values = fig_cols) +
  coord_flip() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank()) 
```

### Treatment Conditions
```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=10, fig.height=10}
d %>%
  pivot_longer(cols = c(compromise_D, compromise_I, compromise_E, compromise_C),
               names_to = "value",
               values_to = "compromise") %>%
  mutate(compromise = recode(compromise, `een compromis` = "Compromise", `geen compromis` = "No Compromise")) %>%
  unite("treatment", c("name", "compromise"), sep = "\n ") %>%
  select(treatment, issue) %>%
  group_by(issue, treatment) %>%
  summarise(n = n()) %>%
  mutate(perc = round(n/sum(n),2),
         perc2 = paste0(perc*100, "%")) %>%
  ggplot(aes(x = perc, y = issue, fill = treatment, label = perc2)) +
  geom_col(position = 'fill', width=0.75) + 
  geom_text(position = position_fill(vjust=0.5), color = "white", fontface = "bold") +
  labs(y = "", x = "", title = "Distribution of Treatments") +
  scale_x_continuous(labels=scales::percent) +
  theme_minimal() +
  scale_fill_manual(values = fig_cols) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.title = element_blank()) +
  guides(fill=guide_legend(ncol=4,byrow=TRUE))
```

### Correlations Matrix
```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
d %>%
  select(`Gender` = F1,
         `Age` = F2,
         `Education` = F9,
         `Region`  = F3,
         `Urbanness`  = F4,
         `Migration Background`  = F5,
         `Job`  = F7,
         `Income`  = F8,
         `Position: Immigration (%)`  = PreT1,
         `Position: Immigration`  = PreT2,
         `Position: Defense`  = PreT3,
         `Position: Education`  = PreT4,
         `Position: Attitude Women in Politics`  = PreT5,
         `Ideology`  = PreT6,
         `Political Efficacy` = PreT7, 
         `Position: COVID-19 Policy` = PreT8,
         `DV: Trait Evaluation` = PT1,
         `DV: Favorability` = PT2,
         `DV: Representation` = PT3,
         `DV: Career Prospects` = PT4) %>%
  ggcorrmat(
  type = "robust", # correlation method
  cor.vars = c(everything()), # a range of variables can be selected
  colors = c(fig_cols[1], fig_cols[4], fig_cols[8]),
  title = "Correlalogram for Variables under Study"
)
```

### 2021-10-19 src/data-processing/prep_data.Rmd
add structure data analysis

@@
 ## Required Packages &amp; Reproducibility
-```{r "env", message=FALSE, warning=F}
+```{r "env", message=FALSE, warning=F, results='hide'}
 rm(list=ls())
@@
 ```{r "get data from Qualtrics", results="hide"}
-source(here("src/data-processing/tidy_data.R"))
-source(here("src/data-processing/Urbaness.R"))
+d <- fetch_survey(surveyID = "SV_7PoXOEVMUF1JZn8", 
+                    verbose = TRUE, force_request = T,
+                    label = FALSE, convert = FALSE)
+source(here("src/data-processing/clean_data.R"))
 ```
@@
 ```{r "Dependent Variable", echo=F, fig.width=10, fig.height=8}
-d <- d %>%
-  mutate(PT_D1 = round((PT_D1_1 + PT_D1_2 + PT_D1_3 + PT_D1_4 + PT_D1_5 + PT_D1_6)/6, 0),
-         PT_E1 = round((PT_E1_1 + PT_E1_2 + PT_E1_3 + PT_E1_4 + PT_E1_5 + PT_E1_6)/6, 0),
-         PT_C1 = round((PT_C1_1 + PT_C1_2 + PT_C1_3 + PT_C1_4 + PT_C1_5 + PT_C1_6)/6, 0),
-         PT_I1 = round((PT_I1_1 + PT_I1_2 + PT_I1_3 + PT_I1_4 + PT_I1_5 + PT_I1_6)/6, 0),
-         PreT5 = round((PreT5_1 + PreT5_2 + PreT5_3 + PreT5_4)/4,0),
-         PreT7 = round((PreT7_1 + PreT7_2 + PreT7_3 + PreT7_4 + PreT7_5 + PreT7_6 + PreT7_7)/7,0)) %>%
-  pivot_longer(cols = c(name_D, name_I, name_E, name_C),
-               values_to = "name",
-               names_to = "issue") %>%
-  drop_na(name) %>%
-  mutate(issue = recode(issue, 
-                        name_C = "COVID",
-                        name_D = "Defense",
-                        name_E = "Education",
-                        name_I = "Immigration")) %>%
-  pivot_longer(cols = c(PT_D1, PT_E1, PT_C1, PT_I1),
-               values_to = "PT1",
-               names_to = "issue1") %>%
-  drop_na(PT1) %>%
-  mutate(issue1 = recode(issue1, 
-                        PT_C1 = "COVID",
-                        PT_D1 = "Defense",
-                        PT_E1 = "Education",
-                        PT_I1 = "Immigration")) %>%
-  pivot_longer(cols = c(PT_D2, PT_E2, PT_C2, PT_I2),
-               values_to = "PT2",
-               names_to = "issue2") %>%
-  mutate(issue2 = recode(issue2, 
-                        PT_C2 = "COVID",
-                        PT_D2 = "Defense",
-                        PT_E2 = "Education",
-                        PT_I2 = "Immigration")) %>%
-  pivot_longer(cols = c(PT_D3, PT_E3, PT_C3, PT_I3),
-               values_to = "PT3",
-               names_to = "issue3") %>%
-  mutate(issue3 = recode(issue3, 
-                         PT_C3 = "COVID",
-                         PT_D3 = "Defense",
-                         PT_E3 = "Education",
-                         PT_I3 = "Immigration")) %>%
-  pivot_longer(cols = c(PT_D4, PT_E4, PT_C4, PT_I4),
-               values_to = "PT4",
-               names_to = "issue4") %>%
-  mutate(issue4 = recode(issue4, 
-                         PT_C4 = "COVID",
-                         PT_D4 = "Defense",
-                         PT_E4 = "Education",
-                         PT_I4 = "Immigration"),
-        check = if_else(issue == issue1 & issue == issue2 & issue == issue3 & issue == issue4, 1,0)) %>%
-  filter(check == 1)
-
 d %>%
-  select(PT1, PT2, PT3, PT4, issue = issue1) %>%
-  mutate(PT1 = PT1 * 2) %>%
-  #mutate_at(c("PT1", "PT2", "PT3", "PT4"), ~(scale(.) %>% as.vector)) %>%
-  pivot_longer(cols = PT1:PT4,
+  select(POST_2, POST_3, POST_4) %>%
+  pivot_longer(cols = POST_2:POST_4,
                names_to = "dvs") %>%
   mutate(dvs = recode(dvs,
-                       PT1 = "DV: Trait Evaluation",
-                       PT2 = "DV: Favorability",
-                       PT3 = "DV: Representation",
-                       PT4 = "DV: Career Prospects")) %>%
-  group_by(issue, dvs) %>%
+                       POST_2 = "Item 2",
+                       POST_3 = "Item 3",
+                       POST_4 = "Item 4"),
+         value = as.numeric(value)) %>%
+  group_by(dvs) %>%
   summarise(means = mean(value, na.rm=T),
@@
          upper = means + (1.56 * stdev)) %>% 
-  ggplot(aes(x = dvs, y = means, colour = issue,
-             ymin = lower, ymax = upper, label = issue)) +
+  ggplot(aes(x = dvs, y = means,
+             ymin = lower, ymax = upper)) +
   geom_point(position = position_dodge(.5)) + 
   geom_errorbar(position = position_dodge(.5), width = 0) +
-  geom_text(aes(y = upper +.5), 
-            position = position_dodge(.5),na.rm = TRUE) + 
-  labs(y = "0 (negative) - 10 (positive)", 
+  labs(y = "1 (Strongly disagree) - 5 (Strongly Agree)", 
        x = "") +
-  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
   theme_minimal() +
@@
 d %>%
-  pivot_longer(cols = c(compromise_D, compromise_I, compromise_E, compromise_C),
-               names_to = "value",
-               values_to = "compromise") %>%
-  mutate(compromise = recode(compromise, `een compromis` = "Compromise", `geen compromis` = "No Compromise")) %>%
-  unite("treatment", c("name", "compromise"), sep = "\n ") %>%
-  select(treatment, issue) %>%
-  group_by(issue, treatment) %>%
+  select(populism) %>%
+  mutate(populism = recode(populism, 
+                           `Burgers` = "Civic Conception", 
+                           `Volk` = "Ethnic Conception")) %>%
+  group_by(populism) %>%
   summarise(n = n()) %>%
@@
          perc2 = paste0(perc*100, "%")) %>%
-  ggplot(aes(x = perc, y = issue, fill = treatment, label = perc2)) +
-  geom_col(position = 'fill', width=0.75) + 
-  geom_text(position = position_fill(vjust=0.5), color = "white", fontface = "bold") +
+  ggplot(aes(x = perc, y = populism, label = perc2)) +
+  geom_col(width=0.75) + 
+  geom_text(position = position_fill(vjust=0.25), color = "white", fontface = "bold") +
   labs(y = "", x = "", title = "Distribution of Treatments") +
@@
 ### Correlations Matrix
-```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
+```{r "Correlations Matrix", eval = F, echo=F, message=T, warning=T, fig.width=15, fig.height=15}
 d %>%

### 2021-10-19 src/data-processing/clean_data.R

@@ -1,0 +1,48 @@
+# Tidy Qualtrics Data
+
+# Clean demographics
+dem <- d %>%
+  filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
+         tic != "359766d9041e7d8c345c0c2838781095", 
+         tic != "daabba41247f457b637205e066bbe39b",
+         tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
+  select(matches("D\\d"), id = tic) %>%
+  select(-matches("D6_7_TEXT")) %>%
+  select(id, D4:D10)%>%
+  drop_na()
+
+pret <- d %>%
+  filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
+         tic != "359766d9041e7d8c345c0c2838781095", 
+         tic != "daabba41247f457b637205e066bbe39b",
+         tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
+  select(matches("PT\\d"), matches("HT4_\\d+"), id = tic) %>%
+  select(-matches("PT8_NPS_GROUP"), -matches("PT[13]"), -matches("PT[13]_\\d+")) %>%
+  select(id, PT4:HT4_4)%>%
+  drop_na()
+
+treat <- d %>%
+  filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
+         tic != "359766d9041e7d8c345c0c2838781095", 
+         tic != "daabba41247f457b637205e066bbe39b",
+         tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
+  select(id = tic, populism)
+
+post <- d %>%
+  filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
+         tic != "359766d9041e7d8c345c0c2838781095", 
+         tic != "daabba41247f457b637205e066bbe39b",
+         tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
+  select(id = tic, matches("POST1[ab]_[123456]")) %>%
+  unite(POST_1, matches("POST1[ab]_1"), na.rm = TRUE) %>%
+  unite(POST_2, matches("POST1[ab]_2"), na.rm = TRUE) %>%
+  unite(POST_3, matches("POST1[ab]_3"), na.rm = TRUE) %>%
+  unite(POST_4, matches("POST1[ab]_4"), na.rm = TRUE) %>%
[…]

### 2021-10-19 src/lib/functions.R

@@ -1,0 +1,22 @@
+library(here)
+library(kableExtra)
+library(tidyverse)
+library(DeclareDesign)
+library(ggpubr)
+library(scales)
+library(cobalt)
+library(margins)
+library(lme4)
+library(ggstatsplot)
+library(ggrepel)
+library(haven)
+library(sjlabelled)
+library(patchwork)
+library(qualtRics)
+
+fig_cols <- yarrr::piratepal(palette = "basel", 
+             trans = .2)
+fig_cols <- as.character(fig_cols[1:8])
+
+api_key_fn <- here("data/raw-private/qualtrics_api_key.txt")
+API <- read_file(api_key_fn) %>% trimws()

### 2021-10-19 src/analysis/analyses.Rmd
update:

---
title: 'Analyses'
author: 
output: 
  github_document:
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
library(rmarkdown)
```

# Scripts
- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
- [Analyses](#analyses)
  - [Descriptive Results](#descriptive-results)
  - [Balance Checks](#balance-checks)
  - [Gender Hypothesis](#gender-hypothesis)
  - [Migration Hypothesis](#migration-hypothesis)
  - [Intersection Hypothesis](#intersection-hypothesis)
  - [Intersection Hypothesis -- Pooled](#intersection-hypothesis--pooled)

# Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
```

# Analyses

```{r "data for analyses",  eval = F}
source(here("src/analysis/data-for-analyses.R"))
```

## Check Missing Values
I employ the following criteria:

- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.

```{r "check missings",  eval = F}
descr <- d %>%
  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),4),
            `DV: Favorability` = round(sum(is.na(PT2))/n(),4),
            `DV: Representation` = round(sum(is.na(PT3))/n(),4),
            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),4),
            `Immigration (%)` = round(sum(is.na(PreT1))/n(),4),
            `Position: Immigration` = round(sum(is.na(PreT2))/n(),4),
            `Position: Defense` = round(sum(is.na(PreT3))/n(),4),
            `Position: Education` = round(sum(is.na(PreT4))/n(),4),
            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),4),
            `Ideology` = round(sum(is.na(PreT6))/n(),4),
            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),4),
            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),4),
            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),4),
            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),4),
            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),4),
            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),4),
            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),4),
            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),4),
            `Gender` = round(sum(is.na(F1))/n(),4),
            `Age` = round(sum(is.na(F2))/n(),4),
            `Region` = round(sum(is.na(F3))/n(),4),
            `Urbaness` = round(sum(is.na(F4))/n(),4),
            `Migration Background` = round(sum(is.na(F5))/n(),4),
            `Party Preference` = round(sum(is.na(F6))/n(),4),
            `Employment` = round(sum(is.na(F7))/n(),4),
            `Income` = round(sum(is.na(F8))/n(),4),
            `Education` = round(sum(is.na(F9))/n(),4)) %>%
  pivot_longer(cols = `DV: Trait Evaluation`:`Education`,
              names_to = "Variables", values_to = "% Missing Values") %>%
  filter(`% Missing Values` > 0)

kable(descr) %>%
  kable_styling(full_width = F, position = "center")
```

I recode the missing values of the variables `Urbaness`, `Migration Background`, `Income`, and `Education` to the mean value of the respective variables.

```{r "add missings",  eval = F}
d <- d %>%
  mutate(F4 = replace_na(F4, round(mean(F4, na.rm = T),0)),
         F5 = replace_na(F5, round(mean(F5, na.rm = T),0)),
         F8 = replace_na(F8,round(mean(F8, na.rm = T),0)),
         F9 = replace_na(F9,round(mean(F9, na.rm = T),0)))
rm(descr, scales)
```

Next, we automatically extract a `.md` file for the online appendix, as well as a  latex table for the manuscript. 
We are using jinja2 template [src/analysis/table_descriptives.tex.j2](table.tex.j2) which is called with a json string containing the data.
To replicate, make sure `env/bin/pip install -U j2cli` is installed via your command line.

## Descriptive Results
```{r "descriptive-results",  eval = F,echo=FALSE, fig.height=15, fig.width=10}
d %>%
  select(PT1, PT2, PT3, PT4, issue, name, compromise) %>%
  mutate(PT1 = PT1 * 2) %>%
  pivot_longer(cols = PT1:PT4,
               names_to = "dvs") %>%
  mutate(dvs = recode(dvs,
                      `PT1` = "DV: Trait Evaluation",
                      `PT2` = "DV: Favorability",
                      `PT3` = "DV: Representation",
                      `PT4` = "DV: Career Prospects"),
         compromise = if_else(compromise==1, "Compromise", "No Compromise"),
         compromise = factor(compromise,
                             level = c("No Compromise", "Compromise"))) %>%
  unite("treatment", c("issue", "name"), sep = ": ") %>%
  group_by(treatment, compromise, dvs) %>%
  summarise(means = round(mean(value, na.rm=T),1),
            stdev = sd(value, na.rm=T)) %>%
  mutate(lower = means - (1.56 * stdev),
         upper = means + (1.56 * stdev),
         type = if_else(means <= 5, "below", "above")) %>%
  ggplot(aes(x = treatment, 
             y =means, label = means, color=type,
             ymin = lower, ymax = upper)) +
  geom_point(stat='identity', size=6)  +
  scale_color_manual(values = c("above"=fig_cols[3],
                                "below"=fig_cols[2])) +
  geom_errorbar(width = 0) +
  geom_text(color="white", size=2) +
  facet_grid(dvs~compromise) +
  labs(y = "0 (negative) - 10 (positive)", 
       x = "", title = "Bend or Break") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position="none",
        legend.title = element_blank(),
        axis.text=element_text(size=8)) +
  geom_hline(yintercept = 5, linetype = "dotted", color = "darkgrey") +
  coord_flip() 
```

## Balance Checks

The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`, and `Immigration (%)`.
As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.

```{r "balance-checks", eval = F, fig.height=10, fig.width=10}
source(here("src/analysis/balance-test.R"))
df
```

```{r "visualize-unbalanced-vars",  eval = F, fig.height=15, fig.width=20}
source(here("src/analysis/distribution_unbalanced_vars.R"))
p1 + p2 + p3 + p4 + plot_layout(ncol=2)
```

## Ethnic Conception Hypothesis 
```{r "h1",  eval = F, fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1
```

## National Identity Hypothesis
```{r "h2a", eval = F, fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2
```

## Far Right Party ID Hypothesis
```{r "h2b",  eval = F,fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2b.R"))
p3
```

## Exploration

### 2021-10-19 report/figures/table_descriptives.tex
add code

# Table: Descriptive Information of Variables under Study

<table>
 <thead>
  <tr>
   <th style="text-align:left;"> Variables </th>
   <th style="text-align:right;"> Mean Value </th>
   <th style="text-align:right;"> St. Dev </th>
   <th style="text-align:right;"> Min. Value </th>
   <th style="text-align:right;"> Max. Value </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Far Right Party ID </td>
   <td style="text-align:right;"> 0.13 </td>
   <td style="text-align:right;"> 0.34 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Employment </td>
   <td style="text-align:right;"> 5.86 </td>
   <td style="text-align:right;"> 4.20 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 11 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Income </td>
   <td style="text-align:right;"> 6.16 </td>
   <td style="text-align:right;"> 2.59 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 12 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Treatment: Ethnic Conception </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0.50 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> National Identity </td>
   <td style="text-align:right;"> 2.18 </td>
   <td style="text-align:right;"> 0.92 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Knowledge </td>
   <td style="text-align:right;"> 1.34 </td>
   <td style="text-align:right;"> 0.81 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 3 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 2 </td>
   <td style="text-align:right;"> 3.35 </td>
   <td style="text-align:right;"> 1.19 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 3 </td>
   <td style="text-align:right;"> 3.81 </td>
   <td style="text-align:right;"> 0.98 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> DV: Item 4 </td>
   <td style="text-align:right;"> 3.65 </td>
   <td style="text-align:right;"> 0.98 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 5 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Political Interest </td>
   <td style="text-align:right;"> 2.91 </td>
   <td style="text-align:right;"> 1.14 </td>
   <td style="text-align:right;"> 1 </td>
   <td style="text-align:right;"> 6 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ideology </td>
   <td style="text-align:right;"> 5.02 </td>
   <td style="text-align:right;"> 1.87 </td>
   <td style="text-align:right;"> 0 </td>
   <td style="text-align:right;"> 10 </td>
  </tr>
</tbody>
</table>

### 2021-10-19 src/analysis/analyses.Rmd
add code

@@
 ```{r "data for analyses",  eval = F}
+load(here("data/intermediate/cleaned_experiment.RData"))
 source(here("src/analysis/data-for-analyses.R"))
-```
-
-## Check Missing Values
-I employ the following criteria:
-
-- If 10% or less of the values on the dimension are missing, then we re-code the missing values to the overall mean.
-- If 11% or more of the values on the dimension are missing, then we re-code the missing values to a constant (for instance 0) and include a dummy variable indicating whether the response on the covariate was missing or not.
-
-```{r "check missings",  eval = F}
-descr <- d %>%
-  summarise(`DV: Trait Evaluation` = round(sum(is.na(PT1))/n(),4),
-            `DV: Favorability` = round(sum(is.na(PT2))/n(),4),
-            `DV: Representation` = round(sum(is.na(PT3))/n(),4),
-            `DV: Career Prospects` = round(sum(is.na(PT4))/n(),4),
-            `Immigration (%)` = round(sum(is.na(PreT1))/n(),4),
-            `Position: Immigration` = round(sum(is.na(PreT2))/n(),4),
-            `Position: Defense` = round(sum(is.na(PreT3))/n(),4),
-            `Position: Education` = round(sum(is.na(PreT4))/n(),4),
-            `Attitude: Women in Politics` = round(sum(is.na(PreT5))/n(),4),
-            `Ideology` = round(sum(is.na(PreT6))/n(),4),
-            `Political Efficacy (1)` = round(sum(is.na(PreT7_1))/n(),4),
-            `Political Efficacy (2)` = round(sum(is.na(PreT7_2))/n(),4),
-            `Political Efficacy (3)` = round(sum(is.na(PreT7_3))/n(),4),
-            `Political Efficacy (4)` = round(sum(is.na(PreT7_4))/n(),4),
-            `Political Efficacy (5)` = round(sum(is.na(PreT7_5))/n(),4),
-            `Political Efficacy (6)` = round(sum(is.na(PreT7_6))/n(),4),
-            `Political Efficacy (7)` = round(sum(is.na(PreT7_7))/n(),4),
-            `Position: COVID-19` = round(sum(is.na(PreT8))/n(),4),
-            `Gender` = round(sum(is.na(F1))/n(),4),
-            `Age` = round(sum(is.na(F2))/n(),4),
-            `Region` = round(sum(is.na(F3))/n(),4),
-            `Urbaness` = round(sum(is.na(F4))/n(),4),
-            `Migration Background` = round(sum(is.na(F5))/n(),4),
-            `Party Preference` = round(sum(is.na(F6))/n(),4),
-            `Employment` = round(sum(is.na(F7))/n(),4),
-            `Income` = round(sum(is.na(F8))/n(),4),
-            `Education` = round(sum(is.na(F9))/n(),4)) %>%
-  pivot_longer(cols = `DV: Trait Evaluation`:`Education`,
-              names_to = "Variables", values_to = "% Missing Values") %>%
-  filter(`% Missing Values` > 0)
-
-kable(descr) %>%
-  kable_styling(full_width = F, position = "center")
-```
-
-I recode the missing values of the variables `Urbaness`, `Migration Background`, `Income`, and `Education` to the mean value of the respective variables.
-
-```{r "add missings",  eval = F}
-d <- d %>%
-  mutate(F4 = replace_na(F4, round(mean(F4, na.rm = T),0)),
-         F5 = replace_na(F5, round(mean(F5, na.rm = T),0)),
-         F8 = replace_na(F8,round(mean(F8, na.rm = T),0)),
-         F9 = replace_na(F9,round(mean(F9, na.rm = T),0)))
-rm(descr, scales)
 ```
@@
 
+```{r "Table with Descriptives"}
+source(here("src/analysis/descriptive-information-overview.R"))
+table2 <- knitr::kable(descr, digits=2)
+fn <- here("report/figures/table_descriptives.tex")
+cat("# Table: Descriptive Information of Variables under Study \n\n", file=fn)
+cat(table2, file=fn, sep="\n", append=T)
+
+methodnames <- setNames(as.list(descr$Variables), descr$Variables)
+table <- purrr::map(descr, .f= ".") 
+#render_j2(here("src/analysis/table_descriptives.tex.j2"), here("report/figures/table_descriptives.tex"),
+#          data=list(data=table, methods=methodnames))
+rm(descr, methodnames, table, fn, table2)
+```
+
 ## Descriptive Results
@@
 d %>%
-  select(PT1, PT2, PT3, PT4, issue, name, compromise) %>%
-  mutate(PT1 = PT1 * 2) %>%
-  pivot_longer(cols = PT1:PT4,
+  select(POST_2, POST_3, POST_4, ethnic) %>%
+  pivot_longer(cols = POST_2:POST_4,
                names_to = "dvs") %>%
   mutate(dvs = recode(dvs,
-                      `PT1` = "DV: Trait Evaluation",
-                      `PT2` = "DV: Favorability",
-                      `PT3` = "DV: Representation",
-                      `PT4` = "DV: Career Prospects"),
-         compromise = if_else(compromise==1, "Compromise", "No Compromise"),
-         compromise = factor(compromise,
-                             level = c("No Compromise", "Compromise"))) %>%
-  unite("treatment", c("issue", "name"), sep = ": ") %>%
-  group_by(treatment, compromise, dvs) %>%
+                      `POST_2` = "DV: Item 2",
+                      `POST_3` = "DV: Item 3",
+                      `POST_4` = "DV: Item 4"),
+         ethnic = if_else(ethnic==0, "Civic Conception", "Ethnic Conception")) %>%
+  group_by(ethnic, dvs) %>%
   summarise(means = round(mean(value, na.rm=T),1),
@@
          type = if_else(means <= 5, "below", "above")) %>%
-  ggplot(aes(x = treatment, 
-             y =means, label = means, color=type,
+  ggplot(aes(x = ethnic, 
+             y =means, label = means,
              ymin = lower, ymax = upper)) +
@@
   geom_text(color="white", size=2) +
-  facet_grid(dvs~compromise) +
-  labs(y = "0 (negative) - 10 (positive)", 
-       x = "", title = "Bend or Break") +
+  facet_grid(dvs~.) +
+  labs(y = "0 (negative) - 5 (positive)", 
+       x = "", title = "The People as 'Volk' or 'Bürger'?") +
   theme_minimal() +
@@
 
-The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Age`, `Position: COVID`, `Political Efficacy`, `Ideology`,
-`Attitudes: Women in Politics`, `Position: Education`, `Position: Defense`, `Position: Immigration`, and `Immigration (%)`.
+The figure below shows that the data is unbalanced for the variables: `Education`,`Income`, `Employment`, `Urbaness`, `Living Place`, `Birth Place`, `Age`, `Political Knowledge`, `Political Interest`, and `Ideology`.
 As described in the Pre-Analysis Plan (p.10), I will add these covariates to the analyses as controls.
@@
 ## Ethnic Conception Hypothesis 
-```{r "h1",  eval = F, fig.align="center", fig.height=8, fig.width=8}
+```{r "h1", fig.align="center", fig.height=8, fig.width=8}
 source(here("src/analysis/h1.R"))

### 2021-10-19 src/data-processing/prep_data.Rmd
update
add code

@@
 ```{r "get data from Qualtrics", results="hide"}
+## Match data with RESPONDI quota questions
 d <- fetch_survey(surveyID = "SV_7PoXOEVMUF1JZn8", 
@@
 ```{r "save data",eval=FALSE}
-save(d, file = here("data/intermediate/cleaned_data.RData"))
+save(d, file = here("data/intermediate/cleaned_experiment.RData"))
 ```
@@
 ### Correlations Matrix
-```{r "Correlations Matrix", eval = F, echo=F, message=T, warning=T, fig.width=15, fig.height=15}
+```{r "Correlations Matrix", echo=F, message=T, warning=T, fig.width=15, fig.height=15}
 d %>%
-  select(`Gender` = F1,
-         `Age` = F2,
-         `Education` = F9,
-         `Region`  = F3,
-         `Urbanness`  = F4,
-         `Migration Background`  = F5,
-         `Job`  = F7,
-         `Income`  = F8,
-         `Position: Immigration (%)`  = PreT1,
-         `Position: Immigration`  = PreT2,
-         `Position: Defense`  = PreT3,
-         `Position: Education`  = PreT4,
-         `Position: Attitude Women in Politics`  = PreT5,
-         `Ideology`  = PreT6,
-         `Political Efficacy` = PreT7, 
-         `Position: COVID-19 Policy` = PreT8,
-         `DV: Trait Evaluation` = PT1,
-         `DV: Favorability` = PT2,
-         `DV: Representation` = PT3,
-         `DV: Career Prospects` = PT4) %>%
+  mutate(HT4 = (HT4_1 + HT4_2 + HT4_3 + HT4_4)/4) %>%
+  select(#`Gender` = D1,
+         #`Age` = D2,
+         #`Education` = D3,
+         `Region`  = D9,
+         `Birth-place` = D10,
+         `Urbanness`  = D4,
+         `Job`  = D7,
+         `Income`  = D8,
+         `Political Knowledge (1)`  = PT4,
+         `Political Knowledge (2)`  = PT5,
+         `Political Knowledge (3)`  = PT6,
+         `Political Interest`  = PT7,
+         `Ideology`  = PT8,
+         `Exclusive National Identity` = HT4) %>%
   ggcorrmat(

### 2021-10-19 src/analysis/balance-test.R

@@ -1,0 +1,70 @@
+covs <- d %>%
+  select(ethnic, D4, D7:PT8) 
+
+balanced <-bal.tab(ethnic ~ factor(D4) + D7 + D8 + factor(D9) +
+                     factor(D10) + pol_know + PT7 + PT8,
+                   data = covs,
+                   thresholds = c(m = 0.05))[[1]] 
+df <- balanced %>%
+  mutate(variable = c("Urbanness: Big City", "Urbanness: Countryside", "Urbanness: Middlesized City", 
+                          "Urbanness: Rural Village", "Urbanness: Suburb",
+                          "Employment", "Income", "Living Place: Badem-Würtemberg",
+                          "Living Place: Bavaria", "Living Place: Berlin",
+                          "Living Place: Brandenburg", "Living Place: Bremen",
+                          "Living Place: Hamburg", "Living Place: Hessen",
+                          "Living Place: Lower Saxony", "Living Place: Mecklenburg-Western Pomerania",
+                          "Living Place: North Rhine-Westphalia", "Living Place: Rhineland-Palatinate",
+                          "Living Place: Saarland", "Living Place: Saxony", "Living Place: Saxony-Anholt",
+                          "Living Place: Schleswig-Holstein", "Living Place: Thuringia",
+                          "Birth Place: Badem-Würtemberg",
+                          "Birth Place: Bavaria", "Birth Place: Berlin",
+                          "Birth Place: Brandenburg", "Birth Place: Bremen",
+                          "Birth Place: Hamburg", "Birth Place: Hessen",
+                          "Birth Place: Lower Saxony", "Birth Place: Mecklenburg-Western Pomerania",
+                          "Birth Place: North Rhine-Westphalia", "Birth Place: Not born in Germany", 
+                      "Birth Place: Rhinelad-Palatinate", 
+                          "Birth Place: Saarland", "Birth Place: Saxony", "Birth Place: Saxony-Anholt",
+                          "Birth Place: Schleswig-Holstein", "Birth Place: Thuringia",
+                          "Political Knowledge", "Political Interest",
+                          "Ideology"),
+         variable = factor(variable,
+                           levels = c("Urbanness: Big City", "Urbanness: Countryside", "Urbanness: Middlesized City", 
+                                      "Urbanness: Rural Village", "Urbanness: Suburb",
+                                      "Employment", "Income", "Living Place: Badem-Würtemberg",
+                                      "Living Place: Bavaria", "Living Place: Berlin",
[…]

### 2021-10-19 src/analysis/data-for-analyses.R

@@ -1,0 +1,67 @@
+d <- d %>%
+  mutate(D4 = recode(D4, 
+                     `1` = "Big City",
+                     `2` = "Suburb",
+                     `3` = "Middlesized City",
+                     `4` = "Rural Village",
+                     `5` = "Countryside", .default = "NA"),
+         D6 = recode(D6,
+                     `1` = "CDU/CSU",
+                     `2` = "SPD",
+                     `3` = "AfD",
+                     `4` = "Left",
+                     `5` = "Greens",
+                     `6` = "Other party", .default = "NA"),
+        Afd_vote = if_else(D6 == "AfD", 1, 0),
+        D7 = na_if(D7, 12),
+        D8 = na_if(D8, 14),
+        D9 = recode(D9,
+                    `1` = "Baden-Würtemberg",
+                    `17` = "Bavaria",
+                    `18` = "Berlin",
+                    `19` = "Brandenburg",
+                    `20` = "Bremen",
+                    `21` = "Hamburg",
+                    `22` = "Hessen",
+                    `23` = "Lower Saxony",
+                    `24` = "Mecklenburg-Western Pomerania",
+                    `25` = "North Rhine-Westphalia",
+                    `26` = "Rhineland-Palatinate",
+                    `27` = "Saarland",
+                    `28` = "Saxony",
+                    `29` = "Saxony-Anholt",
+                    `30` = "Schleswig-Holstein",
+                    `31` = "Thuringia"),
+        D10 = recode(D10,
+                    `1` = "Baden-Würtemberg",
+                    `17` = "Bavaria",
+                    `18` = "Berlin",
+                    `19` = "Brandenburg",
+                    `20` = "Bremen",
+                    `21` = "Hamburg",
+                    `22` = "Hessen",
+                    `23` = "Lower Saxony",
+                    `24` = "Mecklenburg-Western Pomerania",
+                    `25` = "North Rhine-Westphalia",
+                    `26` = "Rhineland-Palatinate",
+                    `27` = "Saarland",
+                    `28` = "Saxony",
+                    `29` = "Saxony-Anholt",
+                    `30` = "Schleswig-Holstein",
+                    `31` = "Thuringia",
[…]

### 2021-10-19 src/analysis/descriptive-information-overview.R

@@ -1,0 +1,31 @@
+descr <- d %>%
+  select(D7:D8, pol_know:POST_4, -POST_1) %>%
+  pivot_longer(cols = D7:POST_4,
+               names_to = "Variables") %>%
+  group_by(Variables) %>%
+  summarise(`Mean Value` = mean(value, na.rm = T),
+            `St. Dev` = sd(value, na.rm = T),
+            `Min. Value` = min(value, na.rm = T),
+            `Max. Value` = max(value, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(Variables = recode(Variables,
+                            `D7` = "Employment",
+                            `D8` = "Income",
+                            `pol_know`  = "Political Knowledge",
+                            `PT7`  = "Political Interest",
+                            `PT8`  = "Ideology",
+                            `POST_2`  = "DV: Item 2",
+                            `POST_3`  = "DV: Item 3",
+                            `POST_4`  = "DV: Item 4",
+                            `HT4`  = "National Identity",
+                            `Afd_vote` = "Far Right Party ID",
+                            `ethnic` = "Treatment: Ethnic Conception"),
+         Variables = factor(Variables,
+                            levels = c("DV: Item 2","DV: Item 3", "DV: Item 4",
+                                       "Treatment: Ethnic Conception",
+                                       "National Identity",
+                                       "Far Right Party ID",
+                                       "Ideology", "Political Knowledge",
+                                       "Political Interest",
+                                       "Employment","Income")))
+

### 2021-10-19 src/analysis/h1.R

@@ -1,0 +1,30 @@
+p1 <- d %>% 
+  mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
+  select(POST_2, POST_3, POST_4, ethnic) %>%
+  pivot_longer(cols = POST_2:POST_4) %>%
+  group_by(ethnic, name) %>%
+  summarise(value = list(value)) %>%
+  spread(ethnic, value) %>%
+  group_by(name) %>%
+  mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
+         t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
+         means_civic = t.test(unlist(`Civic Conception`))$estimate,
+         means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
+         means_difference = means_civic - means_ethnic,
+         lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
+         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
+         name = recode(name,
+                       `POST_2` = "DV: Item 2",
+                       `POST_3` = "DV: Item 3",
+                       `POST_4` = "DV: Item 4")) %>%
+  select(name, p_value, t_value, means_difference, lower, higher) %>%
+  ggplot(aes(x = means_difference, y = name,
+         xmin = lower, xmax = higher)) +
+  geom_point() + geom_errorbar(width = 0) +
+  theme_bw() +
+  labs(y="", x= "Means Differences Test") +
+  theme(plot.title = element_text(hjust = 0.5),
+        legend.position="none") +
+  geom_vline(xintercept = 0.0, linetype = "dashed", size = .5, color = "gray80")
+  
+  

### 2021-10-19 src/data-processing/clean_data.R

@@ -18,7 +18,7 @@ pret <- d %>%
          tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
   select(matches("PT\\d"), matches("HT4_\\d+"), id = tic) %>%
   select(-matches("PT8_NPS_GROUP"), -matches("PT[13]"), -matches("PT[13]_\\d+")) %>%
-  select(id, PT4:HT4_4)%>%
+  select(id, PT4, PT5 = PT5_1, PT6:HT4_4)%>%
   drop_na()
 
 treat <- d %>%

### 2021-10-19 src/lib/functions.R

@@ -20,3 +20,8 @@ fig_cols <- as.character(fig_cols[1:8])
 
 api_key_fn <- here("data/raw-private/qualtrics_api_key.txt")
 API <- read_file(api_key_fn) %>% trimws()
+
+render_j2 = function(template, output, data, auto_unbox=TRUE, na="string") {
+  data = jsonlite::toJSON(data, pretty=TRUE, auto_unbox=auto_unbox, na=na)
+  system(glue::glue("env/bin/j2 --format json {template} -o {output}"), input=data)
+}

### 2021-10-20 src/analysis/analyses.Rmd
add all source code

@@
 
-```{r "data for analyses",  eval = F}
+```{r "data for analyses"}
 load(here("data/intermediate/cleaned_experiment.RData"))
@@
 ## Descriptive Results
-```{r "descriptive-results",  eval = F,echo=FALSE, fig.height=15, fig.width=10}
+```{r "descriptive-results", echo=FALSE, fig.height=15, fig.width=10}
 d %>%
@@
 
-```{r "balance-checks", eval = F, fig.height=10, fig.width=10}
+```{r "balance-checks", fig.height=10, fig.width=10}
 source(here("src/analysis/balance-test.R"))
 df
-```
-
-```{r "visualize-unbalanced-vars",  eval = F, fig.height=15, fig.width=20}
-source(here("src/analysis/distribution_unbalanced_vars.R"))
-p1 + p2 + p3 + p4 + plot_layout(ncol=2)
 ```
@@
 ## National Identity Hypothesis
-```{r "h2a", eval = F, fig.align="center", fig.height=8, fig.width=8}
-source(here("src/analysis/h2.R"))
-p2
+```{r "h2a", fig.align="center", fig.height=8, fig.width=8}
+source(here("src/analysis/h2a.R"))
+p2a
 ```
@@
 ## Far Right Party ID Hypothesis
-```{r "h2b",  eval = F,fig.align="center", fig.height=8, fig.width=8}
+```{r "h2b", fig.align="center", fig.height=8, fig.width=8}
 source(here("src/analysis/h2b.R"))
-p3
+p2b
 ```

### 2021-10-20 src/analysis/h2a.R

@@ -1,0 +1,30 @@
+df <- d %>%
+  mutate(a = HT4)
+h2a <- regression(df, a, ethnic) 
+  
+p2a <- h2a %>%
+  mutate(y = recode(y,
+                    `POST_2` = "DV: Item 2",
+                    `POST_3` = "DV: Item 3",
+                    `POST_4` = "DV: Item 4"),
+         ethnic = recode(ethnic,
+                             `1` = "Ethnic Conception",
+                             `0` = "Civic Conception")) %>%
+  ggplot(aes(x = y, 
+             y = AME,
+             color = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  theme_minimal() +
+  labs(x = "", y = "Average Marginal Effects of Levels of Exclusive National Identity",
+       title = "National Identity Hypothesis") +
+  facet_grid(.~ethnic) +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank()) +
+  scale_color_manual(values = fig_cols) +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
+  coord_flip()

### 2021-10-20 src/analysis/h2b.R

@@ -1,0 +1,30 @@
+df <- d %>%
+  mutate(a = Afd_vote)
+h2b <- regression(df, a, ethnic) 
+
+p2b <- h2b %>%
+  mutate(y = recode(y,
+                    `POST_2` = "DV: Item 2",
+                    `POST_3` = "DV: Item 3",
+                    `POST_4` = "DV: Item 4"),
+         ethnic = recode(ethnic,
+                         `1` = "Ethnic Conception",
+                         `0` = "Civic Conception")) %>%
+  ggplot(aes(x = y, 
+             y = AME,
+             color = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  theme_minimal() +
+  labs(x = "", y = "Average Marginal Effects of Voting for a Far Right Party",
+       title = "Far Right Party ID Hypothesis") +
+  facet_grid(.~ethnic) +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank()) +
+  scale_color_manual(values = fig_cols) +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
+  coord_flip()

### 2021-10-20 src/lib/functions.R

@@ -25,3 +25,33 @@ render_j2 = function(template, output, data, auto_unbox=TRUE, na="string") {
   data = jsonlite::toJSON(data, pretty=TRUE, auto_unbox=auto_unbox, na=na)
   system(glue::glue("env/bin/j2 --format json {template} -o {output}"), input=data)
 }
+
+regression <- function(df, a, ethnic){
+  
+  depVarList <- df %>% select(matches("POST_[234]"))
+  indepVarList <- df %>% select(a, ethnic) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic,
+                                                 data= indepVarList))
+  depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "a", at = list(ethnic = 0:1))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, ethnic)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "a", at = list(ethnic = 0:1))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, ethnic)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}

### 2021-10-20 src/analysis/analyses.Rmd
add all source code

@@
 # Scripts
-- [Required Packages &amp; Reproducibility](#required-packages-&amp;-reproducibility)
-- [Analyses](#analyses)
-  - [Descriptive Results](#descriptive-results)
-  - [Balance Checks](#balance-checks)
-  - [Gender Hypothesis](#gender-hypothesis)
-  - [Migration Hypothesis](#migration-hypothesis)
-  - [Intersection Hypothesis](#intersection-hypothesis)
-  - [Intersection Hypothesis -- Pooled](#intersection-hypothesis--pooled)
 
@@
 
-# Analyses
+# Pre-Registered Analyses
 
@@
 
-## Exploration
+# Exploration
+
+## Scaling fit
+
+```{r "scale", fig.align="center", fig.height=8, fig.width=8}
+source(here("src/analysis/explorative_cfa.R"))
+
+```

### 2021-10-20 src/analysis/explorative_cfa.R

@@ -1,0 +1,15 @@
+pa_model <- 'pa_scale = ~ POST_1 + POST_2 + POST_3 + POST_4 + POST_5 + POST_6'
+
+de <- d %>%
+  filter(ethnic == 1)
+cfa_ethnic <- cfa(model = pa_model, data = de)
+#summary(cfa_ethnic, fit.measures = TRUE, standardized = TRUE)
+
+dc <- d %>%
+  filter(ethnic == 0)
+cfa_civic <- cfa(model = pa_model, data = dc)
+#summary(cfa_civic, fit.measures = TRUE, standardized = TRUE)
+
+d <- d %>%
+  mutate(cfa_pa = ifelse(ethnic == 1, predict(cfa_ethnic), predict(cfa_civic)))
+

### 2021-10-20 src/lib/functions.R

@@ -13,6 +13,7 @@ library(haven)
 library(sjlabelled)
 library(patchwork)
 library(qualtRics)
+library(lavaan)
 
 fig_cols <- yarrr::piratepal(palette = "basel", 
              trans = .2)

### 2021-11-10 report/figures/table_descriptives.tex
add data analyses

@@
    <td style="text-align:left;"> Far Right Party ID </td>
-   <td style="text-align:right;"> 0.13 </td>
-   <td style="text-align:right;"> 0.34 </td>
+   <td style="text-align:right;"> 0.10 </td>
+   <td style="text-align:right;"> 0.30 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:left;"> Employment </td>
-   <td style="text-align:right;"> 5.86 </td>
-   <td style="text-align:right;"> 4.20 </td>
+   <td style="text-align:right;"> 4.18 </td>
+   <td style="text-align:right;"> 3.85 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Income </td>
-   <td style="text-align:right;"> 6.16 </td>
-   <td style="text-align:right;"> 2.59 </td>
+   <td style="text-align:right;"> 6.94 </td>
+   <td style="text-align:right;"> 2.64 </td>
    <td style="text-align:right;"> 1 </td>
-   <td style="text-align:right;"> 12 </td>
+   <td style="text-align:right;"> 13 </td>
   </tr>
@@
    <td style="text-align:left;"> National Identity </td>
-   <td style="text-align:right;"> 2.18 </td>
-   <td style="text-align:right;"> 0.92 </td>
+   <td style="text-align:right;"> 3.63 </td>
+   <td style="text-align:right;"> 0.90 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Political Knowledge </td>
-   <td style="text-align:right;"> 1.34 </td>
-   <td style="text-align:right;"> 0.81 </td>
+   <td style="text-align:right;"> 1.47 </td>
+   <td style="text-align:right;"> 0.82 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:left;"> DV: Item 2 </td>
-   <td style="text-align:right;"> 3.35 </td>
-   <td style="text-align:right;"> 1.19 </td>
+   <td style="text-align:right;"> 4.32 </td>
+   <td style="text-align:right;"> 1.17 </td>
    <td style="text-align:right;"> 1 </td>
-   <td style="text-align:right;"> 5 </td>
+   <td style="text-align:right;"> 6 </td>
   </tr>
@@
    <td style="text-align:left;"> DV: Item 3 </td>
-   <td style="text-align:right;"> 3.81 </td>
-   <td style="text-align:right;"> 0.98 </td>
+   <td style="text-align:right;"> 4.84 </td>
+   <td style="text-align:right;"> 0.97 </td>
    <td style="text-align:right;"> 1 </td>
-   <td style="text-align:right;"> 5 </td>
+   <td style="text-align:right;"> 6 </td>
   </tr>
@@
    <td style="text-align:left;"> DV: Item 4 </td>
-   <td style="text-align:right;"> 3.65 </td>
-   <td style="text-align:right;"> 0.98 </td>
+   <td style="text-align:right;"> 4.55 </td>
+   <td style="text-align:right;"> 0.99 </td>
    <td style="text-align:right;"> 1 </td>
-   <td style="text-align:right;"> 5 </td>
+   <td style="text-align:right;"> 6 </td>
   </tr>
@@
    <td style="text-align:left;"> Political Interest </td>
-   <td style="text-align:right;"> 2.91 </td>
-   <td style="text-align:right;"> 1.14 </td>
+   <td style="text-align:right;"> 2.93 </td>
+   <td style="text-align:right;"> 1.09 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Ideology </td>
-   <td style="text-align:right;"> 5.02 </td>
-   <td style="text-align:right;"> 1.87 </td>
+   <td style="text-align:right;"> 4.75 </td>
+   <td style="text-align:right;"> 1.79 </td>
    <td style="text-align:right;"> 0 </td>

### 2021-11-10 src/analysis/balance-test.R

@@ -1,5 +1,10 @@
 covs <- d %>%
-  select(ethnic, D4, D7:PT8) 
+  select(ethnic, D4, D7:PT8) %>%
+  filter(D4 != "NA",
+         D7 != "NA",
+         D8 != "NA",
+         D9 != "NA",
+         D10 != "NA")
 
 balanced <-bal.tab(ethnic ~ factor(D4) + D7 + D8 + factor(D9) +
                      factor(D10) + pol_know + PT7 + PT8,

### 2021-11-10 src/analysis/data-for-analyses.R

@@ -31,7 +31,8 @@ d <- d %>%
                     `28` = "Saxony",
                     `29` = "Saxony-Anholt",
                     `30` = "Schleswig-Holstein",
-                    `31` = "Thuringia"),
+                    `31` = "Thuringia",
+                    .default = "NA"),
         D10 = recode(D10,
                     `1` = "Baden-Würtemberg",
                     `17` = "Bavaria",
@@ -51,6 +52,7 @@ d <- d %>%
                     `31` = "Thuringia",
                     `32` = "Not born in Germany", .default = "NA"),
         HT4 = round((HT4_1 + HT4_2 + HT4_3 + HT4_4)/4, 0),
+        HT4 = 6 - HT4,
         PT4 = if_else(PT4 == 3, 1, 0),
         PT5 = if_else(PT5 == 5, 1, 0),
         PT6 = if_else(PT6==1, 1, 0),
@@ -63,5 +65,4 @@ d <- d %>%
         POST_4 = as_numeric(POST_4),
         POST_5 = as_numeric(POST_5),
         POST_6 = as_numeric(POST_6)) %>%
-  select(id, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_6) %>%
-  drop_na()
+  select(id, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_6)

### 2021-11-10 src/analysis/h2a.R

@@ -1,30 +1,30 @@
 df <- d %>%
   mutate(a = HT4)
-h2a <- regression(df, a, ethnic) 
+h2a <- regression2(df, a, ethnic) 
   
 p2a <- h2a %>%
   mutate(y = recode(y,
                     `POST_2` = "DV: Item 2",
                     `POST_3` = "DV: Item 3",
-                    `POST_4` = "DV: Item 4"),
-         ethnic = recode(ethnic,
-                             `1` = "Ethnic Conception",
-                             `0` = "Civic Conception")) %>%
-  ggplot(aes(x = y, 
+                    `POST_4` = "DV: Item 4")) %>%
+  ggplot(aes(x = a, 
              y = AME,
              color = y,
+             fill = y,
              ymin = lower,
              ymax = upper)) +
-  geom_point(position = position_dodge(.5)) + 
-  geom_errorbar(position = position_dodge(.5), width = 0) +
+  geom_line() + 
+  geom_ribbon(alpha = .2) +
+  #geom_errorbar(position = position_dodge(.5), width = 0) +
   theme_minimal() +
-  labs(x = "", y = "Average Marginal Effects of Levels of Exclusive National Identity",
+  labs(x = "Exclusive National Identity \n (1 = Low, 5 = High)", 
+       y = "Average Marginal Effects of Levels of Ethnic Conception of the People",
        title = "National Identity Hypothesis") +
-  facet_grid(.~ethnic) +
+  facet_grid(.~y) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",
         legend.title = element_blank()) +
   scale_color_manual(values = fig_cols) +
-  geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
-  coord_flip()
+  scale_fill_manual(values = fig_cols) +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed")

### 2021-11-10 src/analysis/h2b.R

@@ -10,6 +10,7 @@ p2b <- h2b %>%
          ethnic = recode(ethnic,
                          `1` = "Ethnic Conception",
                          `0` = "Civic Conception")) %>%
+  filter(ethnic == "Ethnic Conception") %>%
   ggplot(aes(x = y, 
              y = AME,
              color = y,

### 2021-11-10 src/data-processing/clean_data.R

@@ -26,7 +26,8 @@ treat <- d %>%
          tic != "359766d9041e7d8c345c0c2838781095", 
          tic != "daabba41247f457b637205e066bbe39b",
          tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
-  select(id = tic, populism)
+  select(id = tic, populism) %>%
+  drop_na()
 
 post <- d %>%
   filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
@@ -44,5 +45,7 @@ post <- d %>%
 
 d <- left_join(dem, pret, by = "id")
 d <- left_join(d, treat, by = "id")
-d <- left_join(d, post, by = "id") 
+d <- left_join(d, post, by = "id") %>%
+  drop_na()
+
 rm(dem, pret, treat, post)

### 2021-11-10 src/lib/functions.R

@@ -56,3 +56,33 @@ regression <- function(df, a, ethnic){
   }
   return(m)
 }
+
+regression2 <- function(df, a, ethnic){
+  
+  depVarList <- df %>% select(matches("POST_[234]"))
+  indepVarList <- df %>% select(a, ethnic) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic,
+                                                 data= indepVarList))
+  depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "ethnic", at = list(a = 1:5))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, a)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "ethnic", at = list(a = 1:5))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, a)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}

### 2021-11-10 src/analysis/analyses.Rmd
add data analyses
add data analysis

@@
 p1
+# negative values: Ethnic conception > Civic conception 
+# positive values: Ethnic conception < Civic conception 
 ```
@@
 
+```{r "h2", fig.align="center", fig.height=6, fig.width=10, echo = FALSE, fig.show = "hide"}
+p2a + p2b + 
+  plot_layout(widths = c(2, 1))
+```
+
 # Exploration

### 2021-11-10 src/analysis/h1.R

@@ -14,15 +14,17 @@ p1 <- d %>%
          lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
          higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
          name = recode(name,
-                       `POST_2` = "DV: Item 2",
-                       `POST_3` = "DV: Item 3",
-                       `POST_4` = "DV: Item 4")) %>%
+                       `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                       `POST_3` = "DV: MPs should follow \n the will of the people",
+                       `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
   select(name, p_value, t_value, means_difference, lower, higher) %>%
   ggplot(aes(x = means_difference, y = name,
          xmin = lower, xmax = higher)) +
-  geom_point() + geom_errorbar(width = 0) +
+  geom_point(color = fig_cols[1]) + 
+  geom_errorbar(width = 0, color = fig_cols[1]) +
   theme_bw() +
-  labs(y="", x= "Means Differences Test") +
+  labs(y="", x= "Means Differences Test \n t statistic",
+       title = "Ethnic Conception hypothesis") +
   theme(plot.title = element_text(hjust = 0.5),
         legend.position="none") +
   geom_vline(xintercept = 0.0, linetype = "dashed", size = .5, color = "gray80")

### 2021-11-10 src/analysis/h2a.R

@@ -4,9 +4,9 @@ h2a <- regression2(df, a, ethnic)
   
 p2a <- h2a %>%
   mutate(y = recode(y,
-                    `POST_2` = "DV: Item 2",
-                    `POST_3` = "DV: Item 3",
-                    `POST_4` = "DV: Item 4")) %>%
+                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow \n the will of the people",
+                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
   ggplot(aes(x = a, 
              y = AME,
              color = y,

### 2021-11-10 src/analysis/h2b.R

@@ -4,9 +4,9 @@ h2b <- regression(df, a, ethnic)
 
 p2b <- h2b %>%
   mutate(y = recode(y,
-                    `POST_2` = "DV: Item 2",
-                    `POST_3` = "DV: Item 3",
-                    `POST_4` = "DV: Item 4"),
+                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow \n the will of the people",
+                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people"),
          ethnic = recode(ethnic,
                          `1` = "Ethnic Conception",
                          `0` = "Civic Conception")) %>%

### 2021-11-10 src/analysis/h1.R
add data analysis

@@ -18,15 +18,19 @@ p1 <- d %>%
                        `POST_3` = "DV: MPs should follow \n the will of the people",
                        `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
   select(name, p_value, t_value, means_difference, lower, higher) %>%
-  ggplot(aes(x = means_difference, y = name,
-         xmin = lower, xmax = higher)) +
-  geom_point(color = fig_cols[1]) + 
-  geom_errorbar(width = 0, color = fig_cols[1]) +
+  ggplot(aes(x = means_difference, 
+             y = name,
+             xmin = lower, 
+             xmax = higher,
+             color = name)) +
+  geom_point() + 
+  geom_errorbar(width = 0) +
   theme_bw() +
   labs(y="", x= "Means Differences Test \n t statistic",
        title = "Ethnic Conception hypothesis") +
   theme(plot.title = element_text(hjust = 0.5),
         legend.position="none") +
+  scale_color_manual(values = fig_cols) +
   geom_vline(xintercept = 0.0, linetype = "dashed", size = .5, color = "gray80")
   
   

### 2021-11-10 src/analysis/h2b.R
add data analysis

@@ -29,3 +29,31 @@ p2b <- h2b %>%
   scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
   coord_flip()
+
+p2c <- h2b %>%
+  mutate(y = recode(y,
+                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow \n the will of the people",
+                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people"),
+         ethnic = recode(ethnic,
+                         `1` = "Ethnic Conception",
+                         `0` = "Civic Conception")) %>%
+  filter(ethnic == "Ethnic Conception") %>%
+  ggplot(aes(x = y, 
+             y = AME,
+             color = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  theme_minimal() +
+  labs(x = "", y = "Average Marginal Effects of \n Voting for a Far Right Party",
+       title = "Far Right Party ID Hypothesis") +
+  facet_grid(.~ethnic) +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank()) +
+  scale_color_manual(values = fig_cols) +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
+  coord_flip()

### 2021-11-10 report/draft.Rmd
add draft

---
title: "Responsive or Responsible? The Reputational Cost of Political Compromises"
date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
author:
  - Maurits Meijers, Radboud University Nijmegen
  - Mariken A.C.G. van der Velden, Vrije Universiteit Amsterdam
output: 
  pdf_document:
   number_sections: false
   includes:
      in_header: header.tex
editor_options: 
  chunk_output_type: console
bibliography: references.bib
urlcolor: blue
linkcolor: blue
abstract: "_ADD Abstract_"
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
---

```{r setup, include=FALSE}
## include this at top of your RMarkdown file for pretty output
## make sure to have the printr package installed: install.packages('printr')
library(knitr)
opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
options(kableExtra.latex.load_packages = FALSE)
here::i_am("report/draft.Rmd")
source(here::here("src/lib/functions.R"))
load(here("data/intermediate/cleaned_experiment.RData"))
source(here("src/analysis/data-for-analyses.R"))
```

# Introduction

# Ethnic or Civic Conception of _the People_

**Ethnic Conception hypothesis** (_H1_):  All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is lower for an ethnic conception of the 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger).e.

**Exclusive National Identity hypothesis** (_H2a_):  All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is higher for an ethnic conception of 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger) when the respondent adheres to an exclusive national identity.

**Far Right Party ID hypothesis** (_H2b_): All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is higher for an ethnic conception of 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger) when the respondent votes for a far right party.

# Data, Measurement & Method

## Data
The survey experiment is conducted in Germany between the 13th of October 2021 and the 11th of November 2021.
The sample, recruited through [Respondi](https://www.respondi.com/EN/), consists of 8,000 participants (based on the power analysis presented in Figure \ref{fig:power}) of 18 years and older.
Respondi works with opt-in respondents, so we have implemented quota on age, gender, and education.
Moreover, we measure some more demographic background variables (see the [Measurement Section](#control-variables)).
Balance checks are conducted to demonstrate whether certain categories are over represented in a certain experimental group (see [the Methods Section](#method), Figure \ref{fig:balance}).
The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the \textit{Vrije Universiteit Amsterdam} (see the approval [here](../docs/RERC_VU_wording-experiment.pdf)).
To ensure good quality of our data, two attention checks are included.
Each respondent failing the attention check will be excluded and replaced with another 'good' response.

## Measurement

**_Dependent Variables_**
Measuring populist attitudes, three of the six items mention _the people_.
We rely on those three items in the populism scale. See Table \ref{tab:dv} in the [Appendix](# Appendix A. Wording of the questionaire) for the exact phrasing of the question.
Each item is used on a 5-point likert scale: from `very much disagree` (value of `0`) till `very much agree` (value of `5`).
The average for each of the items lies between 3 and 4 (with a standard deviation around 1), meaning that people are neutral till positive about these statements.

```{r descriptive-table, echo = FALSE, eval = FALSE}
descr <- d %>%
  select(matches("POST_[234]")) %>%
  pivot_longer(cols = everything()) %>%
  mutate(Variable = recode(name,
                       `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
                       `POST_3` = "DV: MPs should follow \n the will of the people",
                       `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
  group_by(Variable) %>%
  summarise(`Mean Value` = round(mean(value, na.rm = T),2),
            `St.dev` = round(sd(value, na.rm = T), 2),
            `Min. Value` = min(value),
            `Max. Value` = max(value))

kbl(descr, booktabs =T, caption = "\\label{tab:descr-dv}Descriptive Information of Dependent Variables",
    digits = 2) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center")  %>%
   column_spec(1, width = "5.5cm") %>%
   column_spec(2, width = "2cm") %>%
   column_spec(3, width = "1.5cm") %>%
   column_spec(4, width = "2cm") %>%
   column_spec(5, width = "2cm")
rm(descr)  
```

**_Experimental Condition_**
Given the historical context of Germany, we randomize whether _the people_ is translated into German using either the civic conception (i.e. _Bürger_) or the ethnic conception (i.e. _Volk_).
`50.2\%` of the respondents (3347 in total) got the civic conception treatment, and `49.8\%` of the respondents (3317 in total) was randomized into the ethnics conception treatment.

**_Covariates_**
Because Respondi works with an opt-in sample, we have background information on age, gender, educational level, geographical region, vote recall, emplyment, and income.
In our [online compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes), we demonstrate all the descriptive information.
As detailed in our pre-analysis plan, we only include variables as covariates that are unbalanced. 
As Figure \ref{balance} shows, only the income covariate is unbalanced accross the experimental groups. 
We therefore add this covariate to the regression analyses (H2a and H2b).

```{r balance, fig.align = 'center', out.width = "95%", fig.cap = "\\label{fig:balance}Balance Checks"}
include_graphics(here("report/figures", "balance-checks-1.png"))
```

## Method
To test the _Ethnic Conception hypothesis_ (H1), we conducted a difference in means for the group who received the ethnic and the civic question wording, for all populist items containing a reference to _the people_.
To test whether H1 is conditional upon having an exclusive national identity (_H2a_) and/or voting for a far right party (_H2b_) we use linear multivariate regressions, with an interaction between the treatment conditions and the variable of interest in the heterogenous treatment (i.e. respectively having a exclusive national identity and voting for a far right party).

# Framing Effects of Ethnic or Civic Conception of _the People_

## Pre-Registered Hypotheses

```{r results-h1, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-h1h2}Results: H1"}
include_graphics(here("report/figures", "h1-1.png"))
```

```{r results-h2, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-h2}Results: H2"}
include_graphics(here("report/figures", "h2-1.png"))
```

## Explorations

# Discussion

\newpage
# References

\newpage

# Appendix A. Wording of the questionaire

```{r dv, topcaption=TRUE}
d <- tibble(Variable = c("Item 2 (DV1)",
                         "Item 3 (DV2)",
                         "Item 4 (DV3)"), 
            `Wording ENG` = c("The people, not politicians, should make the most important political decisions","he politicians in the German Bundestag need to follow the will of the people", "The political differences between elites and the people are greater than the differences among citizens"),
            `Wording DE` = c("[Die Bürger/Das Volk], und nicht die Politiker, sollte(n) die wichtigsten politischen Entscheidungen treffen", "Die Abgeordneten des Deutschen Bundestags müssen dem Willen [der Bürger/des Volkes] Folge leisten", "Die politischen Unterschiede zwischen den Eliten und [den Bürgern/dem Volk] sind größer als die Unterschiede (zwischen Bürgern)"))

kbl(d, booktabs =T, caption = "\\label{tab:dv}Survey Questions - DV") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "7cm") %>%
  column_spec(3, width = "7cm")

```

### 2021-11-10 report/figures/table_descriptives.tex
add draft

@@
    <td style="text-align:left;"> DV: Item 2 </td>
-   <td style="text-align:right;"> 4.32 </td>
+   <td style="text-align:right;"> 3.32 </td>
    <td style="text-align:right;"> 1.17 </td>
-   <td style="text-align:right;"> 1 </td>
-   <td style="text-align:right;"> 6 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
   </tr>
@@
    <td style="text-align:left;"> DV: Item 3 </td>
-   <td style="text-align:right;"> 4.84 </td>
+   <td style="text-align:right;"> 3.84 </td>
    <td style="text-align:right;"> 0.97 </td>
-   <td style="text-align:right;"> 1 </td>
-   <td style="text-align:right;"> 6 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
   </tr>
@@
    <td style="text-align:left;"> DV: Item 4 </td>
-   <td style="text-align:right;"> 4.55 </td>
+   <td style="text-align:right;"> 3.55 </td>
    <td style="text-align:right;"> 0.99 </td>
-   <td style="text-align:right;"> 1 </td>
-   <td style="text-align:right;"> 6 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
   </tr>

### 2021-11-10 src/analysis/data-for-analyses.R

@@ -60,9 +60,15 @@ d <- d %>%
         PT7 =  na_if(PT7, 7),
         ethnic = if_else(populism=="Volk", 1, 0),
         POST_1 = as_numeric(POST_1),
+        POST_1 = POST_1 - 1,
         POST_2 = as_numeric(POST_2),
+        POST_2 = POST_2 - 1,
         POST_3 = as_numeric(POST_3),
+        POST_3 = POST_3 - 1,
         POST_4 = as_numeric(POST_4),
+        POST_4 = POST_4 - 1,
         POST_5 = as_numeric(POST_5),
-        POST_6 = as_numeric(POST_6)) %>%
+        POST_5 = POST_5 - 1,
+        POST_6 = as_numeric(POST_6),
+        POST_6 = POST_6 - 1,) %>%
   select(id, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_6)

### 2021-11-12 report/draft.Rmd
add draft

@@
 ---
-title: "Responsive or Responsible? The Reputational Cost of Political Compromises"
-date: "`r format(Sys.time(), '%d %B, %Y - %X (%Z)')`"
-author:
-  - Maurits Meijers, Radboud University Nijmegen
-  - Mariken A.C.G. van der Velden, Vrije Universiteit Amsterdam
 output: 
-  pdf_document:
-   number_sections: false
-   includes:
-      in_header: header.tex
-editor_options: 
-  chunk_output_type: console
+  stevetemplates::article:
+    fig_caption: true
 bibliography: references.bib
-urlcolor: blue
-linkcolor: blue
-abstract: "_ADD Abstract_"
+urlcolor: black
+linkcolor: black
 header-includes:
@@
    - \usepackage{tabu}
-   - \usepackage{threeparttable}
+   - \usepackage[para,online,flushleft]{threeparttable}
    - \usepackage{threeparttablex}
@@
    - \usepackage{xcolor}
+   - \usepackage{hyperref}
+   - \usepackage{array}   
+   - \usepackage{caption}
+   - \usepackage{graphicx}
+   - \usepackage{epstopdf}
+   - \usepackage{siunitx}
+   - \usepackage{multirow}
+   - \usepackage{hhline}
+   - \usepackage{calc}
+   - \usepackage{tabularx}
+   - \usepackage{fontawesome}
+   - \usepackage{amsthm}
+   - \newtheorem{hypo}{Hypothesis}
+biblio-style: apsr
+title: "The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
+thanks: "Replication files are available on the author's Github account (http://github.com/MariikenvdVelden/wording-experiment-populist-attitudes).
+**Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: "
+author:
+- name: Mariken A.C.G. van der Velden
+  affiliation: Vrije Universiteit Amsterdam
+- name: Maurits Meijers
+  affiliation: Radboud University Nijmegen
+anonymous: FALSE
+abstract: "ADD ABSTRACT"
+keywords: "Experiment, Populist Attitudes"
+date: "`r format(Sys.time(), '%B %d, %Y')`"
+geometry: margin=1in
+mainfont: cochineal
+#sansfont: Linux Biolinum O
+fontsize: 11pt
+twocol: FALSE
+appendix: TRUE
+# doublespacing: TRUE
+endnote: no
+# pandocparas: TRUE
+sansitup: FALSE
 ---
@@
 ```{r setup, include=FALSE}
-## include this at top of your RMarkdown file for pretty output
-## make sure to have the printr package installed: install.packages('printr')
-library(knitr)
-opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
+knitr::opts_chunk$set(echo = FALSE,
+                      message=FALSE, warning=FALSE)
 options(kableExtra.latex.load_packages = FALSE)
-here::i_am("report/draft.Rmd")
-source(here::here("src/lib/functions.R"))
-load(here("data/intermediate/cleaned_experiment.RData"))
-source(here("src/analysis/data-for-analyses.R"))
+
+# Uncomment below if you want code captions
+# oldSource <- knitr::knit_hooks$get("source")
+# knitr::knit_hooks$set(source = function(x, options) {
+#   x <- oldSource(x, options)
+#   x <- ifelse(!is.null(options$code.cap), paste0(x, "\\captionof{chunk}{", options$code.cap,"}"), x)
+#   ifelse(!is.null(options$ref), paste0(x, "\\label{", options$ref,"}"), x)
+# })
+# Add `chunkcaption: TRUE` to YAML as well.
 ```
@@
 
-**Ethnic Conception hypothesis** (_H1_):  All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is lower for an ethnic conception of the 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger).e.
+<!-- hypothesis 1 -->
+> **H1** (**Ethnic Conception**):  _All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to the people is lower for an ethnic conception of the the people (i.e., das Volk) than for a civic conception of the people (i.e., Bürger)_.
 
-**Exclusive National Identity hypothesis** (_H2a_):  All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is higher for an ethnic conception of 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger) when the respondent adheres to an exclusive national identity.
+<!-- hypothesis 2a -->
+> **H2a** (**Exclusive National Identity**):  _All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to the people is lower for an ethnic conception of the the people (i.e., das Volk) than for a civic conception of the people (i.e., Bürger) when the respondent adheres to an exclusive national identity_.
 
-**Far Right Party ID hypothesis** (_H2b_): All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to 'the people' is higher for an ethnic conception of 'the people' (i.e., das Volk) than for a civic conception of 'the people' (i.e., Bürger) when the respondent votes for a far right party.
+<!-- hypothesis 2b -->
+> **H2b** (**Far Right Party ID**):  _All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to the people is lower for an ethnic conception of the the people (i.e., das Volk) than for a civic conception of the people (i.e., Bürger) when the respondent votes for a far right party_.
 
@@
 
-## Data
-The survey experiment is conducted in Germany between the 13th of October 2021 and the 11th of November 2021.
-The sample, recruited through [Respondi](https://www.respondi.com/EN/), consists of 8,000 participants (based on the power analysis presented in Figure \ref{fig:power}) of 18 years and older.
+To investigate whether a civic or ethnic conception of the people influences the populist attitude constructs, we conducted a survey experiment in Germany between the 13th of October 2021 and the 11th of November 2021.
+The sample, recruited through [Respondi](https://www.respondi.com/EN/), consists of 8,000 participants of 18 years and older.
 Respondi works with opt-in respondents, so we have implemented quota on age, gender, and education.
-Moreover, we measure some more demographic background variables (see the [Measurement Section](#control-variables)).
+Moreover, we measured some more demographic background variables.
 Balance checks are conducted to demonstrate whether certain categories are over represented in a certain experimental group (see [the Methods Section](#method), Figure \ref{fig:balance}).
-The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the \textit{Vrije Universiteit Amsterdam} (see the approval [here](../docs/RERC_VU_wording-experiment.pdf)).
+The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the \textit{Vrije Universiteit Amsterdam} (see the approval [here](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes/blob/master/docs/pap/pap.pdf)).
 To ensure good quality of our data, two attention checks are included.
-Each respondent failing the attention check will be excluded and replaced with another 'good' response.
+All variables and their operationalization have been described in our [pre-analysis plan](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes/blob/master/docs/pap/pap.pdf).
 
-## Measurement
+The dependent variables under study are the three of the six items measuring populist attitudes that mention _the people_: 1) _The people, not politicians, should make the most important political decisions_; 2) _The politicians in the German Bundestag need to follow the will of the people_; and 3) _The political differences between elites and the people are greater than the differences among citizens_.
+We rely on those three items in the populism scale, see Table \ref{tab:dv} in the [Appendix](# Appendix A. Wording of the questionaire) for the exact phrasing of the question.
+Each item is measured on a 5-point likert scale: from `very much disagree` (value of `0`) till `very much agree` (value of `5`).
+The average for each of the items lies between 3 and 4 (with a standard deviation around 1, as shown in Table \ref{tab:descr-dv}), meaning that people are neutral till positive about these statements.
 
-**_Dependent Variables_**
-Measuring populist attitudes, three of the six items mention _the people_.
-We rely on those three items in the populism scale. See Table \ref{tab:dv} in the [Appendix](# Appendix A. Wording of the questionaire) for the exact phrasing of the question.
-Each item is used on a 5-point likert scale: from `very much disagree` (value of `0`) till `very much agree` (value of `5`).
-The average for each of the items lies between 3 and 4 (with a standard deviation around 1), meaning that people are neutral till positive about these statements.
+```{r descriptive-table, echo = FALSE}
+rm(list=ls())
+here::i_am("report/draft.Rmd")
+source(here::here("src/lib/functions_draft.R"))
+load(here("data/intermediate/cleaned_experiment.RData"))
+source(here("src/analysis/data-for-analyses.R"))
 
-```{r descriptive-table, echo = FALSE, eval = FALSE}
 descr <- d %>%
@@
 
-**_Experimental Condition_**
 Given the historical context of Germany, we randomize whether _the people_ is translated into German using either the civic conception (i.e. _Bürger_) or the ethnic conception (i.e. _Volk_).
@@
 
-**_Covariates_**
-Because Respondi works with an opt-in sample, we have background information on age, gender, educational level, geographical region, vote recall, emplyment, and income.
+To measure the heterogenous treatment effects, we measure _Exclusive national identity_ with four statements (_being born in Germany_, _having German ancestors_, _being able to speak German_, _adhering to German traditions and customs_) on a 5-point Likert-scale from `very much disagree` (score of `1`) to `very much agree` (score of `5`).
+Becasue $Cronbach's \alpha \geq 0.8$, we have constructed an additive scale for this measure.
+The constructed scale has a mean of 3.61 (with a standard deviation of .89), meaning that people are neutral till agreeing with a exclusive view on national identity. 
+We measured voting for a far right party by asking whether people had voted for the _Alternative für Deutschland_ (AfD) in the recent elections.
+About `10\%` of the respondents recalled to have voted for the AfD.
+
+We have also measured background information on age, gender, educational level, geographical region, vote recall, emplyment, and income.
 In our [online compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes), we demonstrate all the descriptive information.
 As detailed in our pre-analysis plan, we only include variables as covariates that are unbalanced. 
-As Figure \ref{balance} shows, only the income covariate is unbalanced accross the experimental groups. 
+As Figure \ref{fig:balance} shows, only the income covariate is unbalanced accross the experimental groups.
 We therefore add this covariate to the regression analyses (H2a and H2b).
+Income is measured based on respondents' monthly income in bins of 500 Euro, ranging from $\leq$ `500` to $\geq$ `7501`.
 
-```{r balance, fig.align = 'center', out.width = "95%", fig.cap = "\\label{fig:balance}Balance Checks"}
-include_graphics(here("report/figures", "balance-checks-1.png"))
+```{r balance, fig.align = 'center', out.width = "70%", fig.cap = "\\label{fig:balance}Balance Checks"}
+knitr::include_graphics(here::here("report/figures", "balance-checks-1.png"))
 ```
 
-## Method
-To test the _Ethnic Conception hypothesis_ (H1), we conducted a difference in means for the group who received the ethnic and the civic question wording, for all populist items containing a reference to _the people_.
-To test whether H1 is conditional upon having an exclusive national identity (_H2a_) and/or voting for a far right party (_H2b_) we use linear multivariate regressions, with an interaction between the treatment conditions and the variable of interest in the heterogenous treatment (i.e.
-respectively having a exclusive national identity and voting for a far right party).
+# Wording Effects of Ethnic or Civic Conception of _the People_
 
-# Framing Effects of Ethnic or Civic Conception of _the People_
+To test whether the historical context of Germany affects citizens' populists attitudes when use the civic conception or the ethnic conception (H1), we first conducted a difference in means for the group who received the ethnic and the civic question wording, for all populist items containing a reference to _the people_.
+Figure \ref{fig:results-h1} demonstrates the differences between the scores on the three items of the populist attitudes scale that use the word _the people_.
+Negative values indicate that respondents who saw the ethnic conception of the people on average scored higher on the item compared to respondents in the civic conception condition.
+Positive values indicate the reverse. 
+Our pre-registered hypothesis stated that respondents in the ethnic conception condition would agree less (i.e. lower scores) than those in the civic condition.
+Figure \ref{fig:results-h1} demonstrates that only four the item ``The political differences between elites and the people are greater than the differences among citizens'' we find support for this hypothesis.
+For the other two items -- a) The people, not politicians, should make the most important political decisions, and b) The politicians in the German Bundestag need to follow the will of the people -- we find statstically significant results in the opposite direction.
+For these two items, we find that people who saw the ethnic conception of the people scored higher than the other group.
+This could mean either that the historical notion of the ethnic conception is fading in the German context, or that nativism is a strong element of German populism.
+[WE THEREFORE HAVE RUN TWO ANALYSIS TO EXPLORE THIS.
+FIRST, WE CHECK WHETHER THE DIFFERENCES BETWEEN THE CIVIC AND ETHNIC CONCEPTION ARE AGE DEPENDENT.
+SECONDLY, WE EXAMINE IF THE EFFECT IS CONDITIONAL ON GEOGRAPHICAL REGIONS].
 
-## Pre-Registered Hypotheses
-
-```{r results-h1, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-h1h2}Results: H1"}
-include_graphics(here("report/figures", "h1-1.png"))
+```{r results-h1, out.width = "70%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Results: H1"}
+knitr::include_graphics(here::here("report/figures", "h1-1.png"))
 ```
 
+Our second set of pre-registered hypotheses (H2a and H2b), are directed at the heterogeneous treatment effects: Are the diifferences between the civic and ethnic conception of the people conditional upon having an exclusive national identity (_H2a_) and/or voting for a far right party (_H2b_).
+To test this, we use linear multivariate regressions, with an interaction between the treatment conditions and the variable of interest in the heterogenous treatment (i.e.
+respectively having a exclusive national identity and voting for a far right party).
+First, we hypothesized that the more one adheres to an exclusive national identity, they likely score higher on the items when they are in the ethnic conception condition.
+The left-panel of Figure \ref{fig:results-h2} demonstrates that this only holds for the item ``The people, not politicians, should make the most important political decisions''.
+For this item, Figure \ref{fig:results-h2} shows a positive and statistically significant effect as the adherence to an exclusive national identity increases.
+Compared to not adhering to an exclusive national identity, the average score of fully adhering to an exclusive national identity is 0.2 higher on a 5-point scale.
+Compared the standard deviation of this item (1.17, see Table \ref{tab:descr-dv}), this is a small effect.
+For the other two items, the lines are almost flat over the various levels of adherence to an exclusive national identity and not statistically significant.
+Testing whether voting for a far right party conditions the scores on the populist attitude items, the right-panel of \ref{fig:results-h2} shows that the average score on all the items is higher for an ethnic conception of the people than for the civic conception.
+Hence, this indicates support for H2b. 
+As the right panel of \ref{fig:results-h2} demonstrates, the effect for the item The people, not politicians, should make the most important political decisions is the largest: Compared to voting for all other parties, when voting for the AfD and being in the ethnic conception of the people condition, one scores on average a full point higher on a 5-point scale (i.e.
+about a full standard deviation).
+For the items a) MPs should follow the will of the people and b) Differences between elites and the people are bigger than differences between the people the average effect is half a point on a 5-point scale (i.e.
+about half a standard deviation).
+
 ```{r results-h2, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-h2}Results: H2"}
-include_graphics(here("report/figures", "h2-1.png"))
+knitr::include_graphics(here::here("report/figures", "h2-1.png"))
 ```
 
-## Explorations
+[EXPLORATIVE: PCA]
 
@@
 ```{r dv, topcaption=TRUE}
+library(tidyverse)
+library(kableExtra)
 d <- tibble(Variable = c("Item 2 (DV1)",

### 2021-11-12 src/analysis/analyses.Rmd
add draft

--- 2021-10-20 src/analysis/analyses.Rmd
@@
 ## Ethnic Conception Hypothesis 
-```{r "h1", fig.align="center", fig.height=8, fig.width=8}
+```{r "h1", fig.align="center", fig.height=5, fig.width=6}
 source(here("src/analysis/h1.R"))
 p1
+# negative values: Ethnic conception > Civic conception 
+# positive values: Ethnic conception < Civic conception 
 ```
@@
 
+```{r "h2", fig.align="center", fig.height=6, fig.width=12, echo = FALSE, fig.show = "hide"}
+p2a + p2c + 
+  plot_layout(widths = c(2, 1))
+```
+
 # Exploration

### 2021-11-12 src/lib/functions.R

@@ -30,8 +30,8 @@ render_j2 = function(template, output, data, auto_unbox=TRUE, na="string") {
 regression <- function(df, a, ethnic){
   
   depVarList <- df %>% select(matches("POST_[234]"))
-  indepVarList <- df %>% select(a, ethnic) 
-  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic,
+  indepVarList <- df %>% select(a, ethnic, D8) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
                                                  data= indepVarList))
   depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
   
@@ -60,8 +60,8 @@ regression <- function(df, a, ethnic){
 regression2 <- function(df, a, ethnic){
   
   depVarList <- df %>% select(matches("POST_[234]"))
-  indepVarList <- df %>% select(a, ethnic) 
-  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic,
+  indepVarList <- df %>% select(a, ethnic, D8) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
                                                  data= indepVarList))
   depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
   

### 2021-11-12 src/lib/functions_draft.R

@@ -1,0 +1,4 @@
+library(here)
+library(kableExtra)
+library(tidyverse)
+library(sjlabelled)

### 2021-11-16 report/draft.Rmd
add explorative regression analyses

@@
 keywords: "Experiment, Populist Attitudes"
-date: "`r format(Sys.time(), '%B %d, %Y')`"
 geometry: margin=1in
@@
 fontsize: 11pt
+params:
+  anonymous: ""
+  doublespacing: ""
 twocol: FALSE
@@
 
+[EXPLORATIVE: regressions]
+
+```{r results-explorative, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-explorative}Results: Explorative"}
+knitr::include_graphics(here::here("report/figures", "explorative-1.png"))
+```
+
 [EXPLORATIVE: PCA]

### 2021-11-16 src/analysis/analyses.Rmd
add explorative regression analyses

@@
             stdev = sd(value, na.rm=T)) %>%
-  mutate(lower = means - (1.56 * stdev),
-         upper = means + (1.56 * stdev),
+  mutate(lower = means - (1.96 * stdev),
+         upper = means + (1.96 * stdev),
          type = if_else(means <= 5, "below", "above")) %>%
@@
 
+## Alternative specifications + Interactions
+
+```{r "explorative", fig.align="center", fig.height=10, fig.width=15}
+source(here("src/analysis/explorative_analysis.R"))
+pe1 / (pe3 + pe4) #add pe2 (age)
+```
+
 ## Scaling fit

### 2021-11-16 src/analysis/explorative_analysis.R

@@ -1,0 +1,93 @@
+# Alternative specification
+df <- d 
+exp1 <- regression4(df, ethnic) 
+
+pe1 <- exp1 %>%
+  mutate(y = recode(y,
+                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow \n the will of the people",
+                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
+  ggplot(aes(x = y, 
+             y = estimate,
+             color = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  theme_minimal() +
+  labs(x = "", y = "Effect of Ethnic Conception of the People",
+       title = "Alternative Specification: Ethnic Conception hypothesis") +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank()) +
+  scale_color_manual(values = fig_cols) +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
+  coord_flip()
+
+# Interaction with Age (pe2)
+
+
+#Interaction with Region
+df <- d %>%
+  mutate(a = D9)
+exp3 <- regression5(df, a, ethnic) 
+
+pe3 <- exp3 %>%
+  mutate(y = recode(y,
+                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow \n the will of the people",
+                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
+  ggplot(aes(x = factor, 
+             y = AME,
+             color = y,
+             fill = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  theme_minimal() +
+  labs(x = "", 
+       y = "Average Marginal Effects for Ethnic Conception of the People",
+       title = "Exploration: Region") +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
[…]

### 2021-11-16 src/analysis/explorative_cfa.R

@@ -3,13 +3,24 @@ pa_model <- 'pa_scale = ~ POST_1 + POST_2 + POST_3 + POST_4 + POST_5 + POST_6'
 de <- d %>%
   filter(ethnic == 1)
 cfa_ethnic <- cfa(model = pa_model, data = de)
-#summary(cfa_ethnic, fit.measures = TRUE, standardized = TRUE)
+#summary(cfa_ethnic, fit.measures = TRUE, standardized = TRUE))
 
 dc <- d %>%
   filter(ethnic == 0)
 cfa_civic <- cfa(model = pa_model, data = dc)
 #summary(cfa_civic, fit.measures = TRUE, standardized = TRUE)
 
-d <- d %>%
-  mutate(cfa_pa = ifelse(ethnic == 1, predict(cfa_ethnic), predict(cfa_civic)))
-
+tmp <- d %>%
+  mutate(cfa_pa = ifelse(ethnic == 1, predict(cfa_ethnic), predict(cfa_civic))) %>%
+  select(cfa_pa, ethnic) %>%
+  mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
+  group_by(ethnic) %>%
+  summarise(cfa_pa = list(cfa_pa)) %>%
+  spread(ethnic, cfa_pa) %>%
+  mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
+         t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
+         means_civic = t.test(unlist(`Civic Conception`))$estimate,
+         means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
+         means_difference = means_civic - means_ethnic,
+         lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
+         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2])

### 2021-11-16 src/lib/functions.R

@@ -7,7 +7,7 @@ library(scales)
 library(cobalt)
 library(margins)
 library(lme4)
-library(ggstatsplot)
+#library(ggstatsplot)
 library(ggrepel)
 library(haven)
 library(sjlabelled)
@@ -81,6 +81,118 @@ regression2 <- function(df, a, ethnic){
         select(AME, upper, lower, y, a)
       m <- m %>%
         add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+regression3 <- function(df, a, ethnic){
+  
+  depVarList <- df %>% select(matches("POST_[234]"))
+  indepVarList <- df %>% select(a, ethnic, D8) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
+                                                 data= indepVarList))
+  depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "ethnic", at = list(a = 0:10))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.96 * SE),
+               upper = AME + (1.96 * SE)) %>%
+        select(AME, upper, lower, y, a)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "ethnic", at = list(a = 0:10))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.96 * SE),
+               upper = AME + (1.96 * SE)) %>%
+        select(AME, upper, lower, y, a)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+regression4 <- function(df, ethnic){
+  
+  depVarList <- df %>% select(matches("POST_[234]"))
+  indepVarList <- df %>% select(ethnic, D8, matches("POST_[156]")) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ ethnic + 
+                                                   POST_1 + POST_5 + 
+                                                   POST_6 + D8,
+                                                 data= indepVarList))
+  depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- tidy(allModels[[i]]) %>%
+        mutate(y = depVarList[i],
+               lower = estimate - (1.96 * std.error),
[…]

### 2021-11-16 report/draft.Rmd
add scaling analyses

@@
 anonymous: FALSE
-abstract: "ADD ABSTRACT"
+abstract: "Populists believe in the sovereignty of the people.
+Yet, the people can be construed in ethnic terms or in civic terms.
+Using a novel wording experiment in Germany (N=8000), we examine ethnic or civic conceptions of `the people' affect respondents' adherence agreement to key populist attitude items.
+We find that there are statistically significant differences between items framed in an ethnic and a civic manner -- and that this differs per item.
+This relationship is significantly moderated by respondents' degree of exclusive national identity and voting behaviour for the radical right.
+Our findings suggest that the way in which `the people' is conceptualized has important implications for the measurement of populist attitudes."
 keywords: "Experiment, Populist Attitudes"
@@
 # Ethnic or Civic Conception of _the People_
+
+Verschil tussen civic and ethnic
+- kloof elite-burgers hogere score kloof elite-volk: waarom, volk primes homogeneity of both elite and people
+- daar waar ethnisch hoger scoren: volk meet populism beter dan burger
 

### 2021-11-16 report/figures/table_descriptives.tex
add scaling analyses

@@
    <td style="text-align:left;"> Far Right Party ID </td>
-   <td style="text-align:right;"> 0.10 </td>
+   <td style="text-align:right;"> 0.1 </td>
    <td style="text-align:right;"> 0.30 </td>
@@
    <td style="text-align:left;"> Employment </td>
-   <td style="text-align:right;"> 4.18 </td>
-   <td style="text-align:right;"> 3.85 </td>
+   <td style="text-align:right;"> 4.2 </td>
+   <td style="text-align:right;"> 3.86 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Income </td>
-   <td style="text-align:right;"> 6.94 </td>
+   <td style="text-align:right;"> 6.9 </td>
    <td style="text-align:right;"> 2.64 </td>
@@
    <td style="text-align:left;"> Treatment: Ethnic Conception </td>
-   <td style="text-align:right;"> 0.50 </td>
+   <td style="text-align:right;"> 0.5 </td>
    <td style="text-align:right;"> 0.50 </td>
@@
    <td style="text-align:left;"> National Identity </td>
-   <td style="text-align:right;"> 3.63 </td>
+   <td style="text-align:right;"> 3.6 </td>
    <td style="text-align:right;"> 0.90 </td>
@@
    <td style="text-align:left;"> Political Knowledge </td>
-   <td style="text-align:right;"> 1.47 </td>
+   <td style="text-align:right;"> 1.5 </td>
    <td style="text-align:right;"> 0.82 </td>
@@
   <tr>
-   <td style="text-align:left;"> DV: Item 2 </td>
-   <td style="text-align:right;"> 3.32 </td>
-   <td style="text-align:right;"> 1.17 </td>
+   <td style="text-align:left;"> DV: People, not politicians, 
+ should make the most 
+ important political decisions </td>
+   <td style="text-align:right;"> 3.3 </td>
+   <td style="text-align:right;"> 1.18 </td>
    <td style="text-align:right;"> 0 </td>
@@
   <tr>
-   <td style="text-align:left;"> DV: Item 3 </td>
-   <td style="text-align:right;"> 3.84 </td>
-   <td style="text-align:right;"> 0.97 </td>
+   <td style="text-align:left;"> DV: MPs should follow 
+ the will of the people </td>
+   <td style="text-align:right;"> 3.8 </td>
+   <td style="text-align:right;"> 0.98 </td>
    <td style="text-align:right;"> 0 </td>
@@
   <tr>
-   <td style="text-align:left;"> DV: Item 4 </td>
-   <td style="text-align:right;"> 3.55 </td>
-   <td style="text-align:right;"> 0.99 </td>
+   <td style="text-align:left;"> DV: Differences between elites and 
+ the people are bigger than 
+ differences between the people </td>
+   <td style="text-align:right;"> 3.5 </td>
+   <td style="text-align:right;"> 1.00 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
+   <td style="text-align:left;"> Attitude towards Pluralism </td>
+   <td style="text-align:right;"> 4.2 </td>
+   <td style="text-align:right;"> 0.83 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:left;"> Political Interest </td>
-   <td style="text-align:right;"> 2.93 </td>
-   <td style="text-align:right;"> 1.09 </td>
+   <td style="text-align:right;"> 2.9 </td>
+   <td style="text-align:right;"> 1.10 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> Ideology </td>
-   <td style="text-align:right;"> 4.75 </td>
+   <td style="text-align:right;"> 4.8 </td>
    <td style="text-align:right;"> 1.79 </td>

### 2021-11-16 src/analysis/analyses.Rmd
add scaling analyses

--- 2021-11-12 src/analysis/analyses.Rmd
@@
                       fig.path=('../../report/figures/'))
+options(scipen = 1, digits = 2)
 library(rmarkdown)
@@
   mutate(dvs = recode(dvs,
-                      `POST_2` = "DV: Item 2",
-                      `POST_3` = "DV: Item 3",
-                      `POST_4` = "DV: Item 4"),
+                      `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                       `POST_3` = "DV: MPs should follow \n the will of the people",
+                       `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people"),
          ethnic = if_else(ethnic==0, "Civic Conception", "Ethnic Conception")) %>%
@@
 
+## Alternative specifications + Interactions
+
+```{r "explorative", fig.align="center", fig.height=15, fig.width=15}
+source(here("src/analysis/explorative_analysis.R"))
+pe1
+
+pe3/ (pe4 + pe5) #add pe2 (age)
+```
+
 ## Scaling fit
@@
 
+kbl(cfa1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "10cm") %>%
+  column_spec(2, width = "3cm") 
 ```
+
+## IRT Analyse
+```{r "irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
+source(here("src/analysis/IRT.R"))
+
+```
+```{r "irt", fig.align="center", fig.height=8, fig.width=12}
+irt1 + irt2 + 
+  plot_layout(widths = c(1, 2))
+```

### 2021-11-16 src/data-processing/prep_data.Rmd
add scaling analyses

@@
 source(here::here("src/lib/functions.R"))
-renv::snapshot()
 ```

### 2021-11-16 src/analysis/IRT.R

@@ -1,0 +1,188 @@
+packages <- c( "ltm", "GPArotation", "Hmisc", "mirt",
+              "lattice","lordif", "semPlot",
+              "semTools", "nFactors", "corrr")
+for (p in packages) {
+  if (p %in% installed.packages()[,1]) require(p, character.only=T)
+  else {
+    install.packages(p)
+    library(p, character.only=T)
+  }
+}
+
+#Subset for all populist items
+pop_e <- d %>%
+  dplyr::filter(ethnic == 1) %>%
+  dplyr::select(matches("POST_[123456]"))
+  
+pop_c <- d  %>%
+  dplyr::filter(ethnic == 0) %>%
+  dplyr::select(matches("POST_[123456]"))
+
+#Descriptive Statistics for all populism items
+stats_e <- psych::describe(pop_e)
+stats_c <- psych::describe(pop_c)
+
+#polychoric correlations of all items
+#psych::polychoric(pop_e)
+#psych::polychoric(pop_c)
+
+##Correlation Matrix, Screeplot, Bifactor Model
+#cor(pop_e)
+#cor(pop_c)
+
+#psych::omega(pop_e)
+#psych::omega(pop_c)
+
+#psych::alpha(pop_e)
+#psych::alpha(pop_c)
+
+# Screeplot 
+ev_e <- eigen(cor(pop_e)) # get eigenvalues
+ev_c <- eigen(cor(pop_c)) # get eigenvalues
+
+ap_e <- parallel(subject=nrow(pop_e),var=ncol(pop_e),
+                rep=100,cent=.05)
+ap_c <- parallel(subject=nrow(pop_c),var=ncol(pop_c),
+                 rep=100,cent=.05)
+
+nS_e <- nScree(x=ev_e$values, aparallel=ap_e$eigen$qevpea)
+nS_c <- nScree(x=ev_c$values, aparallel=ap_c$eigen$qevpea)
+
+#plotnScree(nS_e, main="", xlab="Factors")
+#plotnScree(nS_c, main="", xlab="Factors")
+
+# Further tests for dimensionality:
+#nfactors(pop_e)
+#nfactors(pop_c)
+
+# Exploratory Factor Analysis 
+pop_e_EFA <- factanal(pop_e, 1, rotation="varimax", covmat = NULL)
+pop_c_EFA <- factanal(pop_c, 1, rotation="varimax", covmat = NULL)
+
[…]

### 2021-11-16 src/analysis/data-for-analyses.R

@@ -70,5 +70,7 @@ d <- d %>%
         POST_5 = as_numeric(POST_5),
         POST_5 = POST_5 - 1,
         POST_6 = as_numeric(POST_6),
-        POST_6 = POST_6 - 1,) %>%
-  select(id, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_6)
+        POST_6 = POST_6 - 1,
+        POST_8 = as_numeric(POST_8),
+        POST_8 = POST_8 - 1,) %>%
+  select(id, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_8)

### 2021-11-16 src/analysis/descriptive-information-overview.R

@@ -1,6 +1,6 @@
 descr <- d %>%
-  select(D7:D8, pol_know:POST_4, -POST_1) %>%
-  pivot_longer(cols = D7:POST_4,
+  select(D7:D8, pol_know:POST_4, POST_8, -POST_1) %>%
+  pivot_longer(cols = D7:POST_8,
                names_to = "Variables") %>%
   group_by(Variables) %>%
   summarise(`Mean Value` = mean(value, na.rm = T),
@@ -14,14 +14,18 @@ descr <- d %>%
                             `pol_know`  = "Political Knowledge",
                             `PT7`  = "Political Interest",
                             `PT8`  = "Ideology",
-                            `POST_2`  = "DV: Item 2",
-                            `POST_3`  = "DV: Item 3",
-                            `POST_4`  = "DV: Item 4",
+                            `POST_2`  = "DV: People, not politicians, \n should make the most \n important political decisions",
+                            `POST_3` = "DV: MPs should follow \n the will of the people",
+                            `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people",
+                            `POST_8` = "Attitude towards Pluralism",
                             `HT4`  = "National Identity",
                             `Afd_vote` = "Far Right Party ID",
                             `ethnic` = "Treatment: Ethnic Conception"),
          Variables = factor(Variables,
-                            levels = c("DV: Item 2","DV: Item 3", "DV: Item 4",
+                            levels = c("DV: People, not politicians, \n should make the most \n important political decisions",
+                                       "DV: MPs should follow \n the will of the people",
+                                       "DV: Differences between elites and \n the people are bigger than \n differences between the people",
+                                       "Attitude towards Pluralism",
                                        "Treatment: Ethnic Conception",
                                        "National Identity",
                                        "Far Right Party ID",

### 2021-11-16 src/analysis/explorative_analysis.R

@@ -14,7 +14,7 @@ pe1 <- exp1 %>%
              ymax = upper)) +
   geom_point(position = position_dodge(.5)) + 
   geom_errorbar(position = position_dodge(.5), width = 0) +
-  theme_minimal() +
+  theme_ipsum() +
   labs(x = "", y = "Effect of Ethnic Conception of the People",
        title = "Alternative Specification: Ethnic Conception hypothesis") +
   theme(plot.title = element_text(hjust = 0.5),
@@ -46,7 +46,7 @@ pe3 <- exp3 %>%
              ymax = upper)) +
   geom_point(position = position_dodge(.5)) + 
   geom_errorbar(position = position_dodge(.5), width = 0) +
-  theme_minimal() +
+  theme_ipsum() +
   labs(x = "", 
        y = "Average Marginal Effects for Ethnic Conception of the People",
        title = "Exploration: Region") +
@@ -79,10 +79,42 @@ pe4 <- exp4 %>%
   geom_line() + 
   geom_ribbon(alpha = .2) +
   #geom_errorbar(position = position_dodge(.5), width = 0) +
-  theme_minimal() +
+  theme_ipsum() +
   labs(x = "Ideological Left-Right Placement \n (0 = Left, 10 = Right)", 
        y = "Average Marginal Effects for Ethnic Conception of the People",
        title = "Exploration: Ideology") +
+  facet_grid(.~y) +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank()) +
+  scale_color_manual(values = fig_cols) +
+  scale_fill_manual(values = fig_cols) +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed")
+
+#Interaction with POST_8
+df <- d %>%
+  mutate(a = POST_8)
+exp5 <- regression6(df, a, ethnic) 
+
+pe5 <- exp5 %>%
+  mutate(y = recode(y,
+                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow \n the will of the people",
+                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
+  ggplot(aes(x = a, 
+             y = AME,
+             color = y,
+             fill = y,
+             ymin = lower,
+             ymax = upper)) +
[…]

### 2021-11-16 src/analysis/explorative_cfa.R

@@ -1,16 +1,19 @@
-pa_model <- 'pa_scale = ~ POST_1 + POST_2 + POST_3 + POST_4 + POST_5 + POST_6'
+pa_model <- 'pa_scale = ~ POST_1 + POST_2 + POST_3 + POST_4 + POST_5 + POST_6
+  POST_3 ~~ POST_2
+  POST_2 ~~ POST_6
+'
 
 de <- d %>%
   filter(ethnic == 1)
 cfa_ethnic <- cfa(model = pa_model, data = de)
-#summary(cfa_ethnic, fit.measures = TRUE, standardized = TRUE))
+#summary(cfa_ethnic, fit.measures = TRUE, standardized = TRUE)
 
 dc <- d %>%
   filter(ethnic == 0)
 cfa_civic <- cfa(model = pa_model, data = dc)
 #summary(cfa_civic, fit.measures = TRUE, standardized = TRUE)
 
-tmp <- d %>%
+cfa1 <- d %>%
   mutate(cfa_pa = ifelse(ethnic == 1, predict(cfa_ethnic), predict(cfa_civic))) %>%
   select(cfa_pa, ethnic) %>%
   mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
@@ -23,4 +26,17 @@ tmp <- d %>%
          means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
          means_difference = means_civic - means_ethnic,
          lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
-         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2])
+         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
+         name = "Differences in Means") %>%
+  select(means_civic, means_ethnic, means_difference, p_value) %>%
+  pivot_longer(cols = means_civic:p_value,
+               values_to = "Values",
+               names_to = "Variables") %>%
+  mutate(Variables = recode(Variables,
+                            `means_civic` = "Average of PCA Constructed Scale for Civic Conception of the People",
+                            `means_ethnic` = "Average of PCA Constructed Scale for Ethnic Conception of the People",
+                            `means_difference` = "Average of Civic Conception - Average of Ethnic Conception",
+                            `p_value` = "p-Value for Differences in Means"))
+
+
+         

### 2021-11-16 src/analysis/h1.R

@@ -25,7 +25,7 @@ p1 <- d %>%
              color = name)) +
   geom_point() + 
   geom_errorbar(width = 0) +
-  theme_bw() +
+  theme_ipsum() +
   labs(y="", x= "Means Differences Test \n t statistic",
        title = "Ethnic Conception hypothesis") +
   theme(plot.title = element_text(hjust = 0.5),

### 2021-11-16 src/analysis/h2a.R

@@ -16,7 +16,7 @@ p2a <- h2a %>%
   geom_line() + 
   geom_ribbon(alpha = .2) +
   #geom_errorbar(position = position_dodge(.5), width = 0) +
-  theme_minimal() +
+  theme_ipsum() +
   labs(x = "Exclusive National Identity \n (1 = Low, 5 = High)", 
        y = "Average Marginal Effects of Levels of Ethnic Conception of the People",
        title = "National Identity Hypothesis") +

### 2021-11-16 src/analysis/h2b.R

@@ -18,7 +18,7 @@ p2b <- h2b %>%
              ymax = upper)) +
   geom_point(position = position_dodge(.5)) + 
   geom_errorbar(position = position_dodge(.5), width = 0) +
-  theme_minimal() +
+  theme_ipsum() +
   labs(x = "", y = "Average Marginal Effects of Voting for a Far Right Party",
        title = "Far Right Party ID Hypothesis") +
   facet_grid(.~ethnic) +

### 2021-11-16 src/data-processing/clean_data.R

@@ -8,8 +8,9 @@ dem <- d %>%
          tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
   select(matches("D\\d"), id = tic) %>%
   select(-matches("D6_7_TEXT")) %>%
-  select(id, D4:D10)%>%
+  select(id, D4:D10) %>%
   drop_na()
+
 
 pret <- d %>%
   filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
@@ -18,8 +19,10 @@ pret <- d %>%
          tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
   select(matches("PT\\d"), matches("HT4_\\d+"), id = tic) %>%
   select(-matches("PT8_NPS_GROUP"), -matches("PT[13]"), -matches("PT[13]_\\d+")) %>%
-  select(id, PT4, PT5 = PT5_1, PT6:HT4_4)%>%
+  select(id, PT4, PT5 = PT5_1, PT6:HT4_4) %>%
   drop_na()
+
+
 
 treat <- d %>%
   filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
@@ -29,18 +32,20 @@ treat <- d %>%
   select(id = tic, populism) %>%
   drop_na()
 
+
 post <- d %>%
   filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
          tic != "359766d9041e7d8c345c0c2838781095", 
          tic != "daabba41247f457b637205e066bbe39b",
          tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
-  select(id = tic, matches("POST1[ab]_[123456]")) %>%
+  select(id = tic, matches("POST1[ab]_[1234568]")) %>%
   unite(POST_1, matches("POST1[ab]_1"), na.rm = TRUE) %>%
   unite(POST_2, matches("POST1[ab]_2"), na.rm = TRUE) %>%
   unite(POST_3, matches("POST1[ab]_3"), na.rm = TRUE) %>%
   unite(POST_4, matches("POST1[ab]_4"), na.rm = TRUE) %>%
   unite(POST_5, matches("POST1[ab]_5"), na.rm = TRUE) %>%
   unite(POST_6, matches("POST1[ab]_6"), na.rm = TRUE) %>%
+  unite(POST_8, matches("POST1[ab]_8"), na.rm = TRUE) %>%
   drop_na()
 
 d <- left_join(dem, pret, by = "id")

### 2021-11-16 src/lib/functions.R

@@ -6,8 +6,7 @@ library(ggpubr)
 library(scales)
 library(cobalt)
 library(margins)
-library(lme4)
-#library(ggstatsplot)
+library(ggstatsplot)
 library(ggrepel)
 library(haven)
 library(sjlabelled)
@@ -197,4 +196,135 @@ regression5 <- function(df, a, ethnic){
     }
   }
   return(m)
+}
+
+regression6 <- function(df, a, ethnic){
+  
+  depVarList <- df %>% select(matches("POST_[234]"))
+  indepVarList <- df %>% select(a, ethnic, D8) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
+                                                 data= indepVarList))
+  depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- summary(margins(allModels[[i]], variables = "ethnic", at = list(a = 0:5))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, a)
+    }
+    else{
+      tmp <- summary(margins(allModels[[i]], variables = "ethnic", at = list(a = 0:5))) %>%
+        mutate(y = depVarList[i],
+               lower = AME - (1.56 * SE),
+               upper = AME + (1.56 * SE)) %>%
+        select(AME, upper, lower, y, a)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+theme_ipsum <- function(base_family="Arial Narrow", base_size = 11.5,
+                        plot_title_family=base_family, plot_title_size = 18,
+                        plot_title_face="bold", plot_title_margin = 10,
+                        subtitle_family=base_family, subtitle_size = 12,
+                        subtitle_face = "plain", subtitle_margin = 15,
+                        strip_text_family = base_family, strip_text_size = 12,
+                        strip_text_face = "plain",
+                        caption_family = base_family, caption_size = 9,
+                        caption_face = "italic", caption_margin = 10,
+                        axis_text_size = base_size,
+                        axis_title_family = subtitle_family, axis_title_size = 9,
+                        axis_title_face = "plain", axis_title_just = "rt",
[…]

### 2021-11-16 report/draft.Rmd
add scaling analyses

@@
 author:
+- name: Maurits Meijers
+  affiliation: Radboud University Nijmegen
 - name: Mariken A.C.G. van der Velden
   affiliation: Vrije Universiteit Amsterdam
-- name: Maurits Meijers
-  affiliation: Radboud University Nijmegen
 anonymous: FALSE
@@
 This relationship is significantly moderated by respondents' degree of exclusive national identity and voting behaviour for the radical right.
-Our findings suggest that the way in which `the people' is conceptualized has important implications for the measurement of populist attitudes."
+Our findings suggest that the way in which 'the people' is conceptualized has important implications for the measurement of populist attitudes."
 keywords: "Experiment, Populist Attitudes"

### 2021-11-19 src/analysis/analyses.Rmd
add new analysis

@@
 
+kbl(m_cfa, booktabs =T, caption = "Confirmatory Factor Analysis - Fit Statistics") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "4cm") %>%
+  column_spec(2, width = "4cm")  %>%
+  column_spec(2, width = "4cm") %>%
+  column_spec(2, width = "4cm")
+
 kbl(cfa1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
@@
   column_spec(2, width = "3cm")
+
+cfa2
 ```

### 2021-11-19 src/analysis/IRT.R

@@ -12,11 +12,11 @@ for (p in packages) {
 #Subset for all populist items
 pop_e <- d %>%
   dplyr::filter(ethnic == 1) %>%
-  dplyr::select(matches("POST_[123456]"))
+  dplyr::select(matches("POST_[12356]"))
   
 pop_c <- d  %>%
   dplyr::filter(ethnic == 0) %>%
-  dplyr::select(matches("POST_[123456]"))
+  dplyr::select(matches("POST_[12356]"))
 
 #Descriptive Statistics for all populism items
 stats_e <- psych::describe(pop_e)
@@ -107,12 +107,12 @@ pattern_c<-factor.scores(fit_c, resp.pattern=pop_c)
 
 # Plot Figure 1
 #https://www.dropbox.com/s/xacryjt5kakm6fn/IRT%20measurement%20populism%20%5BPolitics%5D%20replication%20materials.zip?dl=0&file_subpath=%2FVanHauwaertEtAl.2019_R_Script_Replication.R
-vals_e <- plot(fit_e, type = "IIC", items = 0, plot = FALSE, zrange = c(-6,6)) %>%
+vals_e <- plot(fit_e, type = "IIC", items = 0, plot = FALSE, zrange = c(-5,5)) %>%
   as_tibble() %>%
   mutate(id = "Ethnic Conception",
          se = z / sqrt(test.info))
   
-vals_c <- plot(fit_e, type = "IIC", items = 0, plot = FALSE, zrange = c(-6,6))  %>%
+vals_c <- plot(fit_e, type = "IIC", items = 0, plot = FALSE, zrange = c(-5,5))  %>%
   as_tibble() %>%
   mutate(id = "Civic Conception",
          se = z / sqrt(test.info))
@@ -139,39 +139,35 @@ irt1 <- vals_e %>% add_case(vals_c) %>%
 ## Figure 2 
 #Extract IIC for each of the 6 items & convert them into dataframe:
 df_e <- tibble(
-  z = plot(fit_e, type = "IIC", items = 1, plot = T, zrange = c(-6,6))[,1],
-  item1 = plot(fit_e, type = "IIC", items = 1, plot = T, zrange = c(-6,6))[,2],
-  item2 = plot(fit_e, type = "IIC", items = 2, plot = T, zrange = c(-6,6))[,2],
-  item3 = plot(fit_e, type = "IIC", items = 3, plot = T, zrange = c(-6,6))[,2],
[…]

### 2021-11-19 src/analysis/explorative_cfa.R

@@ -1,4 +1,4 @@
-pa_model <- 'pa_scale = ~ POST_1 + POST_2 + POST_3 + POST_4 + POST_5 + POST_6
+pa_model <- 'pa_scale = ~ POST_1 + POST_2 + POST_3 + POST_5 + POST_6
   POST_3 ~~ POST_2
   POST_2 ~~ POST_6
 '
@@ -6,13 +6,33 @@ pa_model <- 'pa_scale = ~ POST_1 + POST_2 + POST_3 + POST_4 + POST_5 + POST_6
 de <- d %>%
   filter(ethnic == 1)
 cfa_ethnic <- cfa(model = pa_model, data = de)
-#summary(cfa_ethnic, fit.measures = TRUE, standardized = TRUE)
+#summary(cfa_ethnic, fit.measures = TRUE, standardized = TRUE)[[1]]
 
 dc <- d %>%
   filter(ethnic == 0)
 cfa_civic <- cfa(model = pa_model, data = dc)
 #summary(cfa_civic, fit.measures = TRUE, standardized = TRUE)
 
+pa_model <- 'pa_scale = ~ POST_1 + POST_2 + POST_3 + POST_4 + POST_5 + POST_6
+  POST_3 ~~ POST_2
+  POST_2 ~~ POST_6
+'
+dc <- d %>%
+  filter(ethnic == 0)
+cfa_civic6 <- cfa(model = pa_model, data = dc)
+
+m_cfa <- tibble(
+  `Fit Statistics` = c("CFI", "AIC", "BIC", "RMSEA", "p-value RMSEA", "SRMR"),
+  `Ethnic Conception` = c(fitMeasures(cfa_ethnic)[9], AIC(cfa_ethnic), BIC(cfa_ethnic),
+                          fitMeasures(cfa_ethnic)[23], fitMeasures(cfa_ethnic)[26],
+                          fitMeasures(cfa_ethnic)[29]),
+  `Civic Conception` = c(fitMeasures(cfa_civic)[9], AIC(cfa_civic), BIC(cfa_civic),
+                         fitMeasures(cfa_civic)[23], fitMeasures(cfa_civic)[26],
+                         fitMeasures(cfa_civic)[29]),
+  `Civic Conception (6 Items)` = c(fitMeasures(cfa_civic6)[9], AIC(cfa_civic6), BIC(cfa_civic6),
+                         fitMeasures(cfa_civic6)[23], fitMeasures(cfa_civic6)[26],
[…]

### 2021-11-19 src/analysis/h1.R

@@ -1,7 +1,7 @@
 p1 <- d %>% 
   mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
-  select(POST_2, POST_3, POST_4, ethnic) %>%
-  pivot_longer(cols = POST_2:POST_4) %>%
+  select(POST_2, POST_3, ethnic) %>%
+  pivot_longer(cols = POST_2:POST_3) %>%
   group_by(ethnic, name) %>%
   summarise(value = list(value)) %>%
   spread(ethnic, value) %>%
@@ -15,8 +15,7 @@ p1 <- d %>%
          higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
          name = recode(name,
                        `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
-                       `POST_3` = "DV: MPs should follow \n the will of the people",
-                       `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
+                       `POST_3` = "DV: MPs should follow \n the will of the people")) %>%
   select(name, p_value, t_value, means_difference, lower, higher) %>%
   ggplot(aes(x = means_difference, 
              y = name,

### 2021-11-19 src/lib/functions.R

@@ -28,11 +28,11 @@ render_j2 = function(template, output, data, auto_unbox=TRUE, na="string") {
 
 regression <- function(df, a, ethnic){
   
-  depVarList <- df %>% select(matches("POST_[234]"))
+  depVarList <- df %>% select(matches("POST_[23]"))
   indepVarList <- df %>% select(a, ethnic, D8) 
   allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
                                                  data= indepVarList))
-  depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
+  depVarList <- df %>% select(matches("POST_[23]")) %>% colnames()
   
   for(i in 1:length(depVarList)){
     if(i==1){
@@ -58,11 +58,11 @@ regression <- function(df, a, ethnic){
 
 regression2 <- function(df, a, ethnic){
   
-  depVarList <- df %>% select(matches("POST_[234]"))
+  depVarList <- df %>% select(matches("POST_[23]"))
   indepVarList <- df %>% select(a, ethnic, D8) 
   allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
                                                  data= indepVarList))
-  depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
+  depVarList <- df %>% select(matches("POST_[23]")) %>% colnames()
   
   for(i in 1:length(depVarList)){
     if(i==1){
@@ -88,11 +88,11 @@ regression2 <- function(df, a, ethnic){
 
 regression3 <- function(df, a, ethnic){
   
-  depVarList <- df %>% select(matches("POST_[234]"))
+  depVarList <- df %>% select(matches("POST_[23]"))
   indepVarList <- df %>% select(a, ethnic, D8) 
   allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
                                                  data= indepVarList))
-  depVarList <- df %>% select(matches("POST_[234]")) %>% colnames()
+  depVarList <- df %>% select(matches("POST_[23]")) %>% colnames()
   
   for(i in 1:length(depVarList)){
     if(i==1){
@@ -118,13 +118,13 @@ regression3 <- function(df, a, ethnic){
 
 regression4 <- function(df, ethnic){
   
-  depVarList <- df %>% select(matches("POST_[234]"))
+  depVarList <- df %>% select(matches("POST_[24]"))
   indepVarList <- df %>% select(ethnic, D8, matches("POST_[156]")) 
[…]

### 2021-11-19 src/analysis/analyses.Rmd
add analyses'

@@
 
+### CFA
 ```{r "scale", fig.align="center", fig.height=8, fig.width=8}
@@
 
-## IRT Analyse
+### Additive scale
+```{r "addative", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
+source(here("src/analysis/additive-scale.R"))
+
+kbl(add1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "10cm") %>%
+  column_spec(2, width = "3cm")
+
+add2
+```
+
+### Wüttke et al. Approach
+```{r "wuttke", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
+source(here("src/analysis/wuttke-approach.R"))
+
+kbl(wa1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "10cm") %>%
+  column_spec(2, width = "3cm")
+
+wa2
+```
+
+### IRT Analyse
 ```{r "irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
@@
 ```
+
+## Explanatory Power: Predicting Populist Vote
+```{r "predict-vote-1", fig.align="center", fig.height=8, fig.width=8}
+source(here("src/analysis/predict-pop-vote-scales.R"))
+exp
+```
+
+```{r "predict-vote-2", fig.align="center", fig.height=8, fig.width=8}
+source(here("src/analysis/predict-pop-vote-items.R"))
+exp
+```

### 2021-11-19 src/analysis/IRT.R

@@ -102,9 +102,6 @@ fit_c <- grm(pop_c)
 #fit_c
 pattern_c<-factor.scores(fit_c, resp.pattern=pop_c)
 
-#d <- d %>% 
-#  dplyr::mutate(IRT_SCORE = dplyr::if_else(ethnic == 1, pattern_e$score.dat$z1, pattern_c$score.dat$z1))
-
 # Plot Figure 1
 #https://www.dropbox.com/s/xacryjt5kakm6fn/IRT%20measurement%20populism%20%5BPolitics%5D%20replication%20materials.zip?dl=0&file_subpath=%2FVanHauwaertEtAl.2019_R_Script_Replication.R
 vals_e <- plot(fit_e, type = "IIC", items = 0, plot = FALSE, zrange = c(-5,5)) %>%
@@ -184,3 +181,12 @@ irt2 <- df_e %>%
         legend.title = element_blank()) +
   guides(color=guide_legend(nrow=2,byrow=TRUE))
 
+irt_e <- pattern_e$score.dat$z1
+irt_c <- pattern_c$score.dat$z1
+
+tmp <- d %>%
+  dplyr::mutate(irt_pa = ifelse(ethnic == 1, irt_e,irt_c)) %>%
+  dplyr::select(irt_pa)
+
+d <- d %>%
+  add_column(tmp)

### 2021-11-19 src/analysis/additive-scale.R

@@ -1,0 +1,59 @@
+as_e <- d %>%
+  filter(ethnic == 1) %>%
+  mutate(scale = round((POST_1 + POST_2 + POST_3 + 
+                          POST_5 + POST_6)/5,0)) 
+as_e <- as_e$scale
+  
+as_c <- d %>%
+  filter(ethnic == 0) %>%
+  mutate(scale = round((POST_1 + POST_2 + POST_3 + 
+                          POST_5 + POST_6)/5,0)) 
+as_c <- as_c$scale
+
+add1 <- d %>%
+  mutate(scale = ifelse(ethnic == 1, as_e, as_c)) %>%
+  select(scale, ethnic) %>%
+  mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
+  group_by(ethnic) %>%
+  summarise(scale = list(scale)) %>%
+  spread(ethnic, scale) %>%
+  mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
+         t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
+         means_civic = t.test(unlist(`Civic Conception`))$estimate,
+         means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
+         means_difference = means_civic - means_ethnic,
+         lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
+         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
+         name = "Differences in Means") %>%
+  select(means_civic, means_ethnic, means_difference, p_value) %>%
+  pivot_longer(cols = means_civic:p_value,
+               values_to = "Values",
+               names_to = "Variables") %>%
+  mutate(Variables = recode(Variables,
+                            `means_civic` = "Average of PCA Constructed Scale for Civic Conception of the People",
+                            `means_ethnic` = "Average of PCA Constructed Scale for Ethnic Conception of the People",
+                            `means_difference` = "Average of Civic Conception - Average of Ethnic Conception",
+                            `p_value` = "p-Value for Differences in Means"))
+
+
+add2 <- d %>%
+  mutate(scale = ifelse(ethnic == 1, as_e, as_c),
+         ethnic = recode(ethnic,
[…]

### 2021-11-19 src/analysis/explorative_cfa.R

@@ -74,4 +74,11 @@ cfa2 <- d %>%
   scale_fill_manual(values = fig_cols) +
   theme(legend.position="none",
         legend.title = element_blank())
+
+tmp <- d %>%
+  mutate(cfa_pa = ifelse(ethnic == 1, predict(cfa_ethnic), predict(cfa_civic))) %>%
+  select(cfa_pa)
+
+d <- d %>%
+  add_column(tmp)
   

### 2021-11-19 src/analysis/predict-pop-vote-items.R

@@ -1,0 +1,137 @@
+Ethnic <- c(0,1) 
+
+for(i in 1:length(Ethnic)){
+  df <- d %>%
+    dplyr::filter(ethnic == Ethnic[i]) %>%
+    mutate(pop_vote = ifelse(D6 == "AfD", 1,
+                             ifelse(D6 == "Left", 1, 0)),
+           Linke_vote = ifelse(D6 == "Left", 1,0),
+           scale = POST_1)
+  if(i==1){
+    exp <- regression7(df, scale) %>%
+      mutate(id = "POST_1",
+             ethnic = Ethnic[i])}
+  else{
+    tmp <- regression7(df, scale) %>%
+      mutate(id = "POST_1",
+             ethnic = Ethnic[i])
+    exp <- exp %>%
+      add_case(tmp)}
+}
+
+for(i in 1:length(Ethnic)){
+  df <- d %>%
+    dplyr::filter(ethnic == Ethnic[i]) %>%
+    mutate(pop_vote = ifelse(D6 == "AfD", 1,
+                             ifelse(D6 == "Left", 1, 0)),
+           Linke_vote = ifelse(D6 == "Left", 1,0),
+           scale = POST_2)
+  if(i==1){
+    tmp <- regression7(df, scale) %>%
+      mutate(id = "POST_2",
+             ethnic = Ethnic[i])}
+  else{
+    tmpp <- regression7(df, scale) %>%
+      mutate(id = "POST_2",
+             ethnic = Ethnic[i])
+    tmp <- tmp %>%
+      add_case(tmpp)}
+}
+exp <- exp %>%
+  add_case(tmp)
+
+for(i in 1:length(Ethnic)){
+  df <- d %>%
+    dplyr::filter(ethnic == Ethnic[i]) %>%
+    mutate(pop_vote = ifelse(D6 == "AfD", 1,
+                             ifelse(D6 == "Left", 1, 0)),
+           Linke_vote = ifelse(D6 == "Left", 1,0),
+           scale = POST_3)
+  if(i==1){
+    tmp <- regression7(df, scale) %>%
+      mutate(id = "POST_3",
+             ethnic = Ethnic[i])}
+  else{
+    tmpp <- regression7(df, scale) %>%
+      mutate(id = "POST_3",
+             ethnic = Ethnic[i])
+    tmp <- tmp %>%
+      add_case(tmpp)}
+}
+exp <- exp %>%
[…]

### 2021-11-19 src/analysis/predict-pop-vote-scales.R

@@ -1,0 +1,114 @@
+Ethnic <- c(0,1) 
+
+for(i in 1:length(Ethnic)){
+df <- d %>%
+    dplyr::filter(ethnic == Ethnic[i]) %>%
+    mutate(pop_vote = ifelse(D6 == "AfD", 1,
+                             ifelse(D6 == "Left", 1, 0)),
+           Linke_vote = ifelse(D6 == "Left", 1,0),
+           scale = cfa_pa)
+if(i==1){
+  exp <- regression7(df, scale) %>%
+    mutate(id = "cfa_pa",
+           ethnic = Ethnic[i])}
+else{
+  tmp <- regression7(df, scale) %>%
+    mutate(id = "cfa_pa",
+           ethnic = Ethnic[i])
+  exp <- exp %>%
+    add_case(tmp)}
+}
+
+for(i in 1:length(Ethnic)){
+  df <- d %>%
+    dplyr::filter(ethnic == Ethnic[i]) %>%
+    mutate(pop_vote = ifelse(D6 == "AfD", 1,
+                             ifelse(D6 == "Left", 1, 0)),
+           Linke_vote = ifelse(D6 == "Left", 1,0),
+           scale = add_pa)
+  if(i==1){
+    tmp <- regression7(df, scale) %>%
+      mutate(id = "add_pa",
+             ethnic = Ethnic[i])}
+  else{
+    tmpp <- regression7(df, scale) %>%
+      mutate(id = "add_pa",
+             ethnic = Ethnic[i])
+    tmp <- tmp %>%
+      add_case(tmpp)}
+}
+exp <- exp %>%
+  add_case(tmp)
+
+for(i in 1:length(Ethnic)){
+  df <- d %>%
+    dplyr::filter(ethnic == Ethnic[i]) %>%
+    mutate(pop_vote = ifelse(D6 == "AfD", 1,
+                             ifelse(D6 == "Left", 1, 0)),
+           Linke_vote = ifelse(D6 == "Left", 1,0),
+           scale = wuttke_pa)
+  if(i==1){
+    tmp <- regression7(df, scale) %>%
+      mutate(id = "wuttke_pa",
+             ethnic = Ethnic[i])}
+  else{
+    tmpp <- regression7(df, scale) %>%
+      mutate(id = "wuttke_pa",
+             ethnic = Ethnic[i])
+    tmp <- tmp %>%
+      add_case(tmpp)}
[…]

### 2021-11-19 src/analysis/wuttke-approach.R

@@ -1,0 +1,64 @@
+w_e <- d %>%
+  filter(ethnic == 1) %>%
+  select(matches("POST_[12356]")) %>%
+  rowwise() %>% 
+  mutate(scale = min(POST_1, POST_2, POST_3,
+                     POST_5, POST_6))
+w_e <- w_e$scale
+
+w_c <- d %>%
+  filter(ethnic == 0) %>%
+  select(matches("POST_[12356]")) %>%
+  rowwise() %>% 
+  mutate(scale = min(POST_1, POST_2, POST_3,
+                     POST_5, POST_6))
+w_c <- w_c$scale
+
+wa1 <- d %>%
+  mutate(scale = ifelse(ethnic == 1, w_e, w_c)) %>%
+  select(scale, ethnic) %>%
+  mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
+  group_by(ethnic) %>%
+  summarise(scale = list(scale)) %>%
+  spread(ethnic, scale) %>%
+  mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
+         t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
+         means_civic = t.test(unlist(`Civic Conception`))$estimate,
+         means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
+         means_difference = means_civic - means_ethnic,
+         lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
+         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
+         name = "Differences in Means") %>%
+  select(means_civic, means_ethnic, means_difference, p_value) %>%
+  pivot_longer(cols = means_civic:p_value,
+               values_to = "Values",
+               names_to = "Variables") %>%
+  mutate(Variables = recode(Variables,
+                            `means_civic` = "Average of PCA Constructed Scale for Civic Conception of the People",
+                            `means_ethnic` = "Average of PCA Constructed Scale for Ethnic Conception of the People",
+                            `means_difference` = "Average of Civic Conception - Average of Ethnic Conception",
+                            `p_value` = "p-Value for Differences in Means"))
+
+
+wa2 <- d %>%
[…]

### 2021-11-19 src/lib/functions.R

@@ -118,7 +118,7 @@ regression3 <- function(df, a, ethnic){
 
 regression4 <- function(df, ethnic){
   
-  depVarList <- df %>% select(matches("POST_[24]"))
+  depVarList <- df %>% select(matches("POST_[23]"))
   indepVarList <- df %>% select(ethnic, D8, matches("POST_[156]")) 
   allModels <- apply(depVarList,2,function(xl)lm(xl ~ ethnic + 
                                                    POST_1 + POST_5 + 
@@ -220,6 +220,39 @@ regression6 <- function(df, a, ethnic){
                lower = AME - (1.56 * SE),
                upper = AME + (1.56 * SE)) %>%
         select(AME, upper, lower, y, a)
+      m <- m %>%
+        add_case(tmp)
+      
+    }
+  }
+  return(m)
+}
+
+regression7 <- function(df, scale){
+  
+  depVarList <- df %>% dplyr::select(pop_vote, Afd_vote, Linke_vote)
+  indepVarList <- df %>% dplyr::select(scale, D8)
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ scale + D8,
+                                                 data= indepVarList))
+  depVarList <- df %>% dplyr::select(pop_vote, Afd_vote, Linke_vote) %>%
+    colnames()
+  
+  for(i in 1:length(depVarList)){
+    if(i==1){
+      m <- tidy(allModels[[i]]) %>%
+        filter(term == "scale") %>%
+        mutate(y = depVarList[i],
+               lower = estimate - (1.96 * std.error),
+               upper = estimate + (1.96 * std.error)) %>%
+        dplyr::select(estimate, upper, lower, y)
+    }
+    else{
+      tmp <- tidy(allModels[[i]]) %>%
+        filter(term == "scale") %>%
+        mutate(y = depVarList[i],
+               lower = estimate - (1.96 * std.error),
+               upper = estimate + (1.96 * std.error)) %>%
+        dplyr::select(estimate, upper, lower, y)
       m <- m %>%
         add_case(tmp)
       

### 2021-11-20 report/draft.Rmd
add files for rough draft

--- 2021-11-16 report/draft.Rmd
@@
 title: "The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
-thanks: "Replication files are available on the author's Github account (http://github.com/MariikenvdVelden/wording-experiment-populist-attitudes).
-**Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: "
+thanks: "Replication files are available on the author's Github account (http://github.com/MarikenvdVelden/wording-experiment-populist-attitudes).
+**Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: Maurits Meijers"
 author:
+- name: Maurits Meijers
+  affiliation: Radboud University Nijmegen
 - name: Mariken A.C.G. van der Velden
   affiliation: Vrije Universiteit Amsterdam
-- name: Maurits Meijers
-  affiliation: Radboud University Nijmegen
 anonymous: FALSE
-abstract: "ADD ABSTRACT"
+abstract: "Populists believe in the sovereignty of the people.
+Yet, the people can be construed in ethnic terms or in civic terms.
+Using a novel wording experiment in Germany (N=6,713), we examine ethnic or civic conceptions of `the people' affect respondents' adherence agreement to key populist attitude items.
+We find that there are small, but statistically significant differences between items framed in an ethnic and a civic manner -- and that this differs per item.
+This relationship is significantly moderated by respondents' degree of exclusive national identity and voting behaviour for the radical right.
+Our findings suggest that the way in which the people is conceptualized has important implications for the measurement of populist attitudes."
 keywords: "Experiment, Populist Attitudes"
@@
 appendix: TRUE
-# doublespacing: TRUE
+doublespacing: TRUE
 endnote: no
@@
 # Introduction
+Populism puts 'the people' central in political decision-making. 
+It's central claim is that political power should reside with the people, as opposed to the elites [@canovan1999trust, @mudde2004].
+To study populist beliefs at the individual level, scholars recently developed the populist attitude scale [@akkerman2014, @hawkins2012, @castanho2020]. 
+Research on both the individual and the party level has found that populism is a diverse phenomenon, applicable to inclusive left-wing ideologies and exclusionary right-wing ideologies [@meijers2021, @vanhauwaert2018].
+Indeed, populism is thought to be a thin-centred ideology that is usually attached to 'full' ideologies, such as socialism or nationalism [@mudde2004]. 
+As a result, the concept of populism remains agnostic about who constitutes the people.
 
-# Ethnic or Civic Conception of _the People_
+In civic terms, we can think of the people as 'citizens' [e.g., @almond1963]. In ethnic terms, 'the people'can refer to a more cultural understanding of _folk_. 
+While in some  cultural contexts, there is no strong semantic difference between 'the people' and 'citizens' (e.g.
+in the English-speaking world), in other contexts, such as the Germanic one, 'the people' (i.e., _das Volk_) has a strong ethnic connotation.
+In the 1800s, the term _Volk_ and _völkisch_ became strongly associated with an ethnic and racial conception of 'Germanness'. 
+After World War I, the terms _Volk_ and _Volksdeutsche_ were used to describe a ethnically and culturally homogeneous German diaspora, who were citizens of different states after the Versailles Treaty of 1919 [@gosewinkel2003].
 
-<!-- hypothesis 1 -->
-> **H1** (**Ethnic Conception**):  _All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to the people is lower for an ethnic conception of the the people (i.e., das Volk) than for a civic conception of the people (i.e., Bürger)_.
+Scales of populist attitudes have mostly relied on ethnic conceptions of the people [@akkerman2014,@hawkins2012, @castanho2020, @vanhauwaert2020, @schulz2018]. 
+At the same time, populist attitude scales have often been inconsistent in juxtaposing the elites with 'the people' or with 'citizens'. 
+For instance, the scale proposed by @akkerman2014 primarily refers to 'the people'. 
+Yet one item in the @akkerman2014 scale contrasts 'the citizen' with 'politicians' (`POP4`) - an item that nonetheless contributes significantly to the latent construct of populism [@vanhauwaert2020].
+What is more, 'the people' has been translated differently in different translations of the populist attitude scale. 
+For instance, in the French context 'the people' has been translated as _le peuple_ in some items, but as _les citoyens_ in other items [@ivaldi2018]. 
+Yet another study of French citizens refrains from using either _le peuple_ or _les citoyens_, choosing the more neutral _les gens_ instead [@castanho2020]. 
+In Italian, 'the people' is sometimes referred to as _il popolo_, and sometimes as _le persone_ [@castanho2020].
 
-<!-- hypothesis 2a -->
-> **H2a** (**Exclusive National Identity**):  _All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to the people is lower for an ethnic conception of the the people (i.e., das Volk) than for a civic conception of the people (i.e., Bürger) when the respondent adheres to an exclusive national identity_.
+This begs the question whether a civic or ethnic conception of the people matters for the measurement of populist attitudes. 
+On the (far) right, 'the people' is often construed in ethnic, cultural, or even racial terms. On the left, 'the people' is often conceived of in more civic or economic terms. 
+Ideally, however, populist attitude scale capture populist ideation across different ideological predispositions (see the critique of @castanho2020 of populist item scales including nativist items). 
+Using a wording experiment in Germany (`N=6,713`), we examine whether an ethnic or a civic conception of the people affects respondents' agreement with the two items of the populist attitude scale that directly juxtapose 'the people' with the elites.
+We further examine whether far right voters and respondents with a exclusive national identity respond differently to ethnic conceptions of the people.
+In addition, we examine whether the differences found affect the overall latent construct of populist attitudes (EXPAND/SPECIFY LATER).
+Given the more pronounced ethnic connotation with the concept of 'people' or _Volk_ in the German language, the German case is particularly suitable to tease out differences between ethnic and civic conceptions of the people in key populist attitude items.
 
-<!-- hypothesis 2b -->
-> **H2b** (**Far Right Party ID**):  _All things equal, agreement with the constitutive items of the populist attitude construct containing a reference to the people is lower for an ethnic conception of the the people (i.e., das Volk) than for a civic conception of the people (i.e., Bürger) when the respondent votes for a far right party_.
+# Empirical Analysis
+To test whether an ethnic or civic framing of the people affects respondents' agreement with key populist items we conduct a wording experiment. 
+Wording experiments have been used in political science to assess how different question phrasing affects respondents' perceptions of concepts such as issue ownership [@walgrave2016], climate change [@schuldt2011], and party identity [@sanders2002].
+We rely on a nationally representative sample of German citizens over 18 years old (`N=6,713`). 
+The sample is from an online panel provided by the survey company Respondi. 
+Quotas for age, gender, and education were included to ensure the representativeness of the sample. 
+We have 3,348 respondents in the group that received the ethnic phrasing and 3,365 respondents in the group with the civic phrasing. 
+This large sample size allows us to detect also small effects of question wording differences.
 
-# Data, Measurement & Method
+```{r dv, topcaption=TRUE}
+library(tidyverse)
+library(kableExtra)
+df <- tibble(Variable = c("POP1","POP2","POP3",
+                         "POP4","POP5","POP6"), 
+            `Wording ENG` = c("The politicians in the German Bundestag need to follow the will of the [people/citizens].",
+               "The [people/citizens], not politicians, should make the most important political decisions",
+               "I would rather be represented by an ordinary citizen than by a professional politician.", 
+               "The political differences between elites and the people are greater than the differences among citizens",
+               "Elected officials talk too much and take too little action",
+               "What people call ‘compromise’ in politics is really just selling out on one’s principles"),
+            `Wording DE` = c("Die Abgeordneten des Deutschen Bundestags müssen dem Willen [der Bürger/des Volkes] Folge leisten", 
+                             "[Die Bürger/Das Volk], und nicht die Politiker, sollte(n) die wichtigsten politischen Entscheidungen treffen",
+                             "Ein Bürger würde besser meine Interessen vertreten als ein Berufspolitiker",
+                             "Die politischen Unterschiede zwischen den Eliten und [den Bürgern/dem Volk] sind größer als die Unterschiede (zwischen Bürgern)",
+                             "Die Politiker reden zu viel und machen zu wenig",
+                             "Was in der Politik Kompromiss genannt wird, ist in Wirklichkeit nur ein Verrat von Prinzipien"))
 
-To investigate whether a civic or ethnic conception of the people influences the populist attitude constructs, we conducted a survey experiment in Germany between the 13th of October 2021 and the 11th of November 2021.
-The sample, recruited through [Respondi](https://www.respondi.com/EN/), consists of 8,000 participants of 18 years and older.
-Respondi works with opt-in respondents, so we have implemented quota on age, gender, and education.
-Moreover, we measured some more demographic background variables.
-Balance checks are conducted to demonstrate whether certain categories are over represented in a certain experimental group (see [the Methods Section](#method), Figure \ref{fig:balance}).
-The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the \textit{Vrije Universiteit Amsterdam} (see the approval [here](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes/blob/master/docs/pap/pap.pdf)).
-To ensure good quality of our data, two attention checks are included.
-All variables and their operationalization have been described in our [pre-analysis plan](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes/blob/master/docs/pap/pap.pdf).
-
-The dependent variables under study are the three of the six items measuring populist attitudes that mention _the people_: 1) _The people, not politicians, should make the most important political decisions_; 2) _The politicians in the German Bundestag need to follow the will of the people_; and 3) _The political differences between elites and the people are greater than the differences among citizens_.
-We rely on those three items in the populism scale, see Table \ref{tab:dv} in the [Appendix](# Appendix A. Wording of the questionaire) for the exact phrasing of the question.
-Each item is measured on a 5-point likert scale: from `very much disagree` (value of `0`) till `very much agree` (value of `5`).
-The average for each of the items lies between 3 and 4 (with a standard deviation around 1, as shown in Table \ref{tab:descr-dv}), meaning that people are neutral till positive about these statements.
-
-```{r descriptive-table, echo = FALSE}
-rm(list=ls())
-here::i_am("report/draft.Rmd")
-source(here::here("src/lib/functions_draft.R"))
-load(here("data/intermediate/cleaned_experiment.RData"))
-source(here("src/analysis/data-for-analyses.R"))
-
-descr <- d %>%
-  select(matches("POST_[234]")) %>%
-  pivot_longer(cols = everything()) %>%
-  mutate(Variable = recode(name,
-                       `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
-                       `POST_3` = "DV: MPs should follow \n the will of the people",
-                       `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
-  group_by(Variable) %>%
-  summarise(`Mean Value` = round(mean(value, na.rm = T),2),
-            `St.dev` = round(sd(value, na.rm = T), 2),
-            `Min. Value` = min(value),
-            `Max. Value` = max(value))
-
-kbl(descr, booktabs =T, caption = "\\label{tab:descr-dv}Descriptive Information of Dependent Variables",
-    digits = 2) %>%
+kbl(df, booktabs =T, caption = "\\label{tab:popatt}Akkerman et al Populist Attitudes Scale") %>%
   kable_styling(latex_options = c("striped", "hold_position"),
                 full_width = F, fixed_thead = T, position = "center") %>%
-   column_spec(1, width = "5.5cm") %>%
-   column_spec(2, width = "2cm") %>%
-   column_spec(3, width = "1.5cm") %>%
-   column_spec(4, width = "2cm") %>%
-   column_spec(5, width = "2cm")
-rm(descr)  
+   column_spec(1, width = "1.5cm") %>%
+   column_spec(2, width = "6cm") %>%
+   column_spec(3, width = "6cm")
+
 ```
-
-Given the historical context of Germany, we randomize whether _the people_ is translated into German using either the civic conception (i.e. _Bürger_) or the ethnic conception (i.e. _Volk_).
-`50.2\%` of the respondents (3347 in total) got the civic conception treatment, and `49.8\%` of the respondents (3317 in total) was randomized into the ethnics conception treatment.
-
-To measure the heterogenous treatment effects, we measure _Exclusive national identity_ with four statements (_being born in Germany_, _having German ancestors_, _being able to speak German_, _adhering to German traditions and customs_) on a 5-point Likert-scale from `very much disagree` (score of `1`) to `very much agree` (score of `5`).
-Becasue $Cronbach's \alpha \geq 0.8$, we have constructed an additive scale for this measure.
-The constructed scale has a mean of 3.61 (with a standard deviation of .89), meaning that people are neutral till agreeing with a exclusive view on national identity. 
-We measured voting for a far right party by asking whether people had voted for the _Alternative für Deutschland_ (AfD) in the recent elections.
-About `10\%` of the respondents recalled to have voted for the AfD.
-
-We have also measured background information on age, gender, educational level, geographical region, vote recall, emplyment, and income.
-In our [online compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes), we demonstrate all the descriptive information.
-As detailed in our pre-analysis plan, we only include variables as covariates that are unbalanced. 
-As Figure \ref{fig:balance} shows, only the income covariate is unbalanced accross the experimental groups.
-We therefore add this covariate to the regression analyses (H2a and H2b).
-Income is measured based on respondents' monthly income in bins of 500 Euro, ranging from $\leq$ `500` to $\geq$ `7501`.
-
-```{r balance, fig.align = 'center', out.width = "70%", fig.cap = "\\label{fig:balance}Balance Checks"}
-knitr::include_graphics(here::here("report/figures", "balance-checks-1.png"))
-```
-
-# Wording Effects of Ethnic or Civic Conception of _the People_
-
-To test whether the historical context of Germany affects citizens' populists attitudes when use the civic conception or the ethnic conception (H1), we first conducted a difference in means for the group who received the ethnic and the civic question wording, for all populist items containing a reference to _the people_.
-Figure \ref{fig:results-h1} demonstrates the differences between the scores on the three items of the populist attitudes scale that use the word _the people_.
-Negative values indicate that respondents who saw the ethnic conception of the people on average scored higher on the item compared to respondents in the civic conception condition.
-Positive values indicate the reverse. 
-Our pre-registered hypothesis stated that respondents in the ethnic conception condition would agree less (i.e. lower scores) than those in the civic condition.
-Figure \ref{fig:results-h1} demonstrates that only four the item ``The political differences between elites and the people are greater than the differences among citizens'' we find support for this hypothesis.
-For the other two items -- a) The people, not politicians, should make the most important political decisions, and b) The politicians in the German Bundestag need to follow the will of the people -- we find statstically significant results in the opposite direction.
-For these two items, we find that people who saw the ethnic conception of the people scored higher than the other group.
-This could mean either that the historical notion of the ethnic conception is fading in the German context, or that nativism is a strong element of German populism.
-[WE THEREFORE HAVE RUN TWO ANALYSIS TO EXPLORE THIS.
-FIRST, WE CHECK WHETHER THE DIFFERENCES BETWEEN THE CIVIC AND ETHNIC CONCEPTION ARE AGE DEPENDENT.
-SECONDLY, WE EXAMINE IF THE EFFECT IS CONDITIONAL ON GEOGRAPHICAL REGIONS].
-
 ```{r results-h1, out.width = "70%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Results: H1"}
@@
 ```
+To examine whether civic conceptions of the people elicit different responses than ethnic concepts, we experimentally vary the wording of two of the six items in the scale proposed by @akkerman2014, see Table \ref{tab:popatt}.
+In the original Akkerman et al. scale deployed in the Netherlands, the items `POP1` and `POP2` were phrased in ethnic terms (i,e., with reference to _het volk_). 
+We randomize whether respondents received a ethnic framing (i.e., with reference to 'the people; or _das Volk_) or a civic framing (i.e., with reference to 'citizens', or _Bürger_). 
+The upper two items in Table \ref{tab:popatt} shows the differences in wording for the two items `POP1` and `POP2` in English and German. 
+All the other items were kept constant.[^1].
 
-Our second set of pre-registered hypotheses (H2a and H2b), are directed at the heterogeneous treatment effects: Are the diifferences between the civic and ethnic conception of the people conditional upon having an exclusive national identity (_H2a_) and/or voting for a far right party (_H2b_).
-To test this, we use linear multivariate regressions, with an interaction between the treatment conditions and the variable of interest in the heterogenous treatment (i.e.
-respectively having a exclusive national identity and voting for a far right party).
-First, we hypothesized that the more one adheres to an exclusive national identity, they likely score higher on the items when they are in the ethnic conception condition.
-The left-panel of Figure \ref{fig:results-h2} demonstrates that this only holds for the item ``The people, not politicians, should make the most important political decisions''.
-For this item, Figure \ref{fig:results-h2} shows a positive and statistically significant effect as the adherence to an exclusive national identity increases.
-Compared to not adhering to an exclusive national identity, the average score of fully adhering to an exclusive national identity is 0.2 higher on a 5-point scale.
-Compared the standard deviation of this item (1.17, see Table \ref{tab:descr-dv}), this is a small effect.
-For the other two items, the lines are almost flat over the various levels of adherence to an exclusive national identity and not statistically significant.
-Testing whether voting for a far right party conditions the scores on the populist attitude items, the right-panel of \ref{fig:results-h2} shows that the average score on all the items is higher for an ethnic conception of the people than for the civic conception.
-Hence, this indicates support for H2b. 
-As the right panel of \ref{fig:results-h2} demonstrates, the effect for the item The people, not politicians, should make the most important political decisions is the largest: Compared to voting for all other parties, when voting for the AfD and being in the ethnic conception of the people condition, one scores on average a full point higher on a 5-point scale (i.e.
-about a full standard deviation).
-For the items a) MPs should follow the will of the people and b) Differences between elites and the people are bigger than differences between the people the average effect is half a point on a 5-point scale (i.e.
-about half a standard deviation).
+[^1]:Our intention was to also vary the wording of the item `POP4`.
+Yet, due to an unfortunate translation error in Qualtrics, we cannot use the item `POP4` in our analysis.
+However, robustness checks in the Appendix XXX shows that removal of the item does not strongly affect the overall latent construct.
+
+Figure \ref{fig:results-h1} shows the results of a difference of means test for the two treatment groups (ethnic vs. civic wording) for both items. 
+There is a statistically significant difference in respondent agreement with the ethnic and civic conception of the people. 
+When 'the people' is conceived as _das Volk_ respondents are more likely to agree with the item's statement compared to the civic wording of _Bürger_. 
+Yet, as the results show, the difference is small in substantive terms.
+
+How does the effect of an ethnic conception of the people vis-à-vis a civic conception vary across respondents? 
+The left-hand panel of Figure \ref{fig:results-h2} shows the results of an OLS regression analysis with the an interaction between the treatment and a variable measuring whether or not the respondent voted for the far right party _Alternative für Deutschland_.
+We see that far right voters show much more agreement to items `POP1` and `POP2` when it is phrased in an ethnic way. 
+These effects are substantial and statistically significant. 
+[ADD ONE SENTENCE ABOUT THIS].
+
+In a next step, we examine whether respondents with lower and higher levels of exclusive national identity are affected differently by the treatment. 
+Inspired by @mader2021, we measure exclusive national identity using a four-item additive scale on a 5-point Likert scale, which asks respondents to rate how important the following aspects are to be considered German: being born in Germany (a), having German ancestors (b), being able to speak German (c), and sharing share German manners and norms (d).
+The right-hand panel of Figure \ref{fig:results-h2} shows the interaction between the treatment and the exclusive national identity variable on the two items. 
+Overall, we see that the difference between an ethnic and civic wording is only statistically significant for respondents with higher levels of exclusive national identity (ca.
+`>2.5` on the exclusive national identity scale).
+Both the analyses from the left and right-hand panel of \ref{fig:results-h2} suggest that far right voters and respondents with an exclusive national identity interpret `the people' (_das Volk_) in an ethno-cultural way.
+
+So how does an ethnic and civic framing of the items `POP1` and `POP2` affect the latent construct of populism? 
+A graded Item Response Theory (IRT) analysis [see also @vanhauwaert2020] moreover shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see Figure XX and XX in the Appendix).
+Overall, however, the overall level of information yielded by the two latent constructs of populism are similar. 
+This is not surprising, given that we varied the wording of `the people' only in two items of the full \@akkerman2014 item battery.
+
+Therefore, also overall difference between a latent construct of populism with two ethnically framed items and a latent construct with two civically framed items is small.
+We find no statistically significant difference between the two constructs estimated using Confirmatory Factor Analysis (see Figure XX and Table XX in the Appendix). 
+In terms of model fit, both constructs show very similar goodness-of-fit statistics (i.e., CFI, BIC, RMSEA, and SRMR).
+Interestingly, however, both the 'ethnic' and the 'civic' scale show a satisfactory model fit (`CFI > 0.9`; `RMSEA < 0.08`; and `SRMR < 0.02`).
 
@@
 
-[EXPLORATIVE: regressions]
+```{r "scale", fig.align="center", fig.height=8, fig.width=8, eval = FALSE}
+source(here::here("src/lib/functions.R"))
+load(here("data/intermediate/cleaned_experiment.RData"))
+source(here("src/analysis/data-for-analyses.R"))
+source(here("src/analysis/explorative_cfa.R"))
 
-```{r results-explorative, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-explorative}Results: Explorative"}
-knitr::include_graphics(here::here("report/figures", "explorative-1.png"))
+kbl(m_cfa, booktabs =T, caption = "\\label{tab:CFA}Confirmatory Factor Analysis - Fit Statistics") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "4cm") %>%
+  column_spec(2, width = "4cm")  %>%
+  column_spec(2, width = "4cm") %>%
+  column_spec(2, width = "4cm") 
 ```
 
-[EXPLORATIVE: PCA]
+# Conclusion
+Existing populist attitudes scales have been inconsistent in using 'ethnic' or 'civic' conceptions of the people. 
+Using a wording experiment we examined whether German respondents presented with an ethnic framing of 'the people' (_das Volk_) answered key populist attitude items differently than respondents who recevied an ethnic framing of `the people' as citizens (_Bürger_).
 
-# Discussion
+We find that there are statistically significant differences between the two wordings. 
+An ethnic conception of the people, overall, yielded more agreement with the items in question. 
+This is effect is particularly pronounced for voters of the far right. 
+The difference between an ethnic and a civic conception of the people was also only significant for respondents who adhered a moderate to high level of exclusive national identity. 
+This finding is highly suggestive of the 'ethnic' interpretation of `the people' -- at least in the German language.
+
+Nevertheless, we found that a civic or an ethnic wording of items referring to 'the people' makes little difference in a latent construct that also comprises other items that were kept constant. 
+Yet, while this might make little difference in a latent construct that also comprises items that do not solely rely on items that juxtapose 'the people' with the elite, it is likely to be more consequential in survey batteries that predominantly include items contrast 'the people' with elites to measure populist attitudes [for an overview of different batteries, see @castanho2020].
+The populist attitude scales proposed by @schulz2018 and @stanley2011, for instance, contain references to 'the people' in 7/9 and 7/8 of the items, respectively.
+
+Importantly, the degree to which 'the people' is understood in denoting a specific ethno-cultural group likely differs across countries.
+This type of differential item interpretation might therefore lead to measurement invariance when used in cross-national research [@castanho2020]. 
+In other words, if the ethno-cultural connotation of the the people varies across countries, this may hamper cross-national application of populist attitude scales that include multiple items referring to 'the people'.
+In fact, in a comparison of different populist attitudes scales @castanho2020 find that the scales by  @schulz2018 and @stanley2011 perform worse than the scale proposed by @akkerman2014. 
+To empirically establish whether differential interpretations of `the people' matters for measurement invariance, it would be worthwhile replicating this study for different countries.
+In addition, it would be worthwhile in replicating this analysis for different scales than the @akkerman2014 scale.
+
+One can argue theoretically that 'the people' captures the meaning of the concept of populism better than 'citizens'. 
+After all, it populism assumes the people to be a homogeneous entity. 
+Yet, our findings suggest that also a civic framing of the concept yields a satisfactory model fit when estimating a Confirmatory Factor Analysis. 
+In addition, our results suggest that an ethnic framing of the citizens runs the, albeit small, risk overestimating the degree of populist attitudes among more nativist citizens. 
+To avoid priming respondents with an ethnic conception of the people, future studies should consider using a civic conception of ''citizens vs. the elite" when measuring populist attitudes.
 
@@
 # References
-
-\newpage
-
-# Appendix A. Wording of the questionaire
-
-```{r dv, topcaption=TRUE}
-library(tidyverse)
-library(kableExtra)
-d <- tibble(Variable = c("Item 2 (DV1)",
-                         "Item 3 (DV2)",
-                         "Item 4 (DV3)"), 
-            `Wording ENG` = c("The people, not politicians, should make the most important political decisions","he politicians in the German Bundestag need to follow the will of the people", "The political differences between elites and the people are greater than the differences among citizens"),
-            `Wording DE` = c("[Die Bürger/Das Volk], und nicht die Politiker, sollte(n) die wichtigsten politischen Entscheidungen treffen", "Die Abgeordneten des Deutschen Bundestags müssen dem Willen [der Bürger/des Volkes] Folge leisten", "Die politischen Unterschiede zwischen den Eliten und [den Bürgern/dem Volk] sind größer als die Unterschiede (zwischen Bürgern)"))
-
-kbl(d, booktabs =T, caption = "\\label{tab:dv}Survey Questions - DV") %>%
-  kable_styling(latex_options = c("striped", "hold_position"),
-                full_width = F, fixed_thead = T, position = "center") %>%
-  column_spec(1, width = "3cm") %>%
-  column_spec(2, width = "7cm") %>%
-  column_spec(3, width = "7cm")
-
-```

### 2021-11-20 report/old_text.R

@@ -1,0 +1,105 @@
+# Data, Measurement & Method
+To investigate whether a civic or ethnic conception of the people influences the populist attitude constructs, we conducted a survey experiment in Germany between the 13th of October 2021 and the 11th of November 2021.
+The sample, recruited through [Respondi](https://www.respondi.com/EN/), consists of 8,000 participants of 18 years and older.
+Respondi works with opt-in respondents, so we have implemented quota on age, gender, and education.
+Moreover, we measured some more demographic background variables.
+Balance checks are conducted to demonstrate whether certain categories are over represented in a certain experimental group (see [the Methods Section](#method), Figure \ref{fig:balance}).
+  The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the \textit{Vrije Universiteit Amsterdam} (see the approval [here](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes/blob/master/docs/pap/pap.pdf)).
+  To ensure good quality of our data, two attention checks are included.
+  All variables and their operationalization have been described in our [pre-analysis plan](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes/blob/master/docs/pap/pap.pdf).
+  
+  The dependent variables under study are the three of the six items measuring populist attitudes that mention _the people_: 1) _The people, not politicians, should make the most important political decisions_; 2) _The politicians in the German Bundestag need to follow the will of the people_; and 3) _The political differences between elites and the people are greater than the differences among citizens_.
+We rely on those three items in the populism scale, see Table \ref{tab:dv} in the [Appendix](# Appendix A. Wording of the questionaire) for the exact phrasing of the question.
+  Each item is measured on a 5-point likert scale: from `very much disagree` (value of `0`) till `very much agree` (value of `5`).
+  The average for each of the items lies between 3 and 4 (with a standard deviation around 1, as shown in Table \ref{tab:descr-dv}), meaning that people are neutral till positive about these statements. 
+  
+  ```{r descriptive-table, echo = FALSE}
+  rm(list=ls())
+  here::i_am("report/draft.Rmd")
+  source(here::here("src/lib/functions_draft.R"))
+  load(here("data/intermediate/cleaned_experiment.RData"))
+  source(here("src/analysis/data-for-analyses.R"))
+  
+  descr <- d %>%
+    select(matches("POST_[234]")) %>%
+    pivot_longer(cols = everything()) %>%
+    mutate(Variable = recode(name,
[…]

### 2021-11-20 src/analysis/h1.R

@@ -25,8 +25,7 @@ p1 <- d %>%
   geom_point() + 
   geom_errorbar(width = 0) +
   theme_ipsum() +
-  labs(y="", x= "Means Differences Test \n t statistic",
-       title = "Ethnic Conception hypothesis") +
+  labs(y="", x= "Means Differences Test \n t statistic") +
   theme(plot.title = element_text(hjust = 0.5),
         legend.position="none") +
   scale_color_manual(values = fig_cols) +

### 2021-11-20 src/analysis/h2a.R

@@ -18,8 +18,7 @@ p2a <- h2a %>%
   #geom_errorbar(position = position_dodge(.5), width = 0) +
   theme_ipsum() +
   labs(x = "Exclusive National Identity \n (1 = Low, 5 = High)", 
-       y = "Average Marginal Effects of Levels of Ethnic Conception of the People",
-       title = "National Identity Hypothesis") +
+       y = "Average Marginal Effects of Levels of Ethnic Conception of the People") +
   facet_grid(.~y) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),

### 2021-11-20 src/analysis/h2b.R

@@ -19,8 +19,7 @@ p2b <- h2b %>%
   geom_point(position = position_dodge(.5)) + 
   geom_errorbar(position = position_dodge(.5), width = 0) +
   theme_ipsum() +
-  labs(x = "", y = "Average Marginal Effects of Voting for a Far Right Party",
-       title = "Far Right Party ID Hypothesis") +
+  labs(x = "", y = "Average Marginal Effects of Voting for a Far Right Party") +
   facet_grid(.~ethnic) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
@@ -46,10 +45,9 @@ p2c <- h2b %>%
              ymax = upper)) +
   geom_point(position = position_dodge(.5)) + 
   geom_errorbar(position = position_dodge(.5), width = 0) +
-  theme_minimal() +
-  labs(x = "", y = "Average Marginal Effects of \n Voting for a Far Right Party",
-       title = "Far Right Party ID Hypothesis") +
-  facet_grid(.~ethnic) +
+  theme_ipsum() +
+  labs(x = "", y = "Average Marginal Effects of Voting for a Far Right Party \n for Ethnic Conception of the People") +
+  #facet_grid(.~ethnic) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",

### 2021-11-23 report/appendix.Rmd
add Online Appendix

---
output: 
  stevetemplates::article:
    number_sections: TRUE
    toc: yes
title: "ONLINE APPENDIX:The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
bibliography: references.bib
biblio-style: apsr
geometry: margin=1in
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
endnotes: FALSE
mainfont: cochineal
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
appendix: TRUE
appendixletter: "A"
pandocparas: FALSE
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
linkcolor: black
#nocite: |
#  @cartersmith2020fml, @andersetal2020bbgb
header-includes: 
   - \usepackage{array}
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
   - \floatsetup[table]{capposition=top}
   - \usepackage{booktabs}
   - \usepackage{longtable}
   - \usepackage{array}
   - \usepackage{multirow}
   - \usepackage{wrapfig}
   - \usepackage{float}
   - \usepackage{colortbl}
   - \usepackage{pdflscape}
   - \usepackage{tabu}
   - \usepackage[para,online,flushleft]{threeparttable}
   - \usepackage{threeparttablex}
   - \usepackage[normalem]{ulem}
   - \usepackage{makecell}
   - \usepackage{xcolor}
   - \usepackage{caption}
   - \usepackage{graphicx}
   - \usepackage{epstopdf}
   - \usepackage{siunitx}
   - \usepackage{multirow}
   - \usepackage{hhline}
   - \usepackage{calc}
   - \usepackage{tabularx}
   - \usepackage{fontawesome}
   - \usepackage{amsthm}
   - \usepackage{csquotes}
   - \LTcapwidth=.95\textwidth
   - \linespread{1.05}
   - \usepackage{hyperref}
   - \usepackage{setspace}
   - \renewcommand{\thepage}{A-\arabic{page}}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, warning=FALSE)
options(kableExtra.latex.load_packages = FALSE)
options(tinytex.verbose = TRUE)
options(scipen = 1, digits = 2)
# Uncomment below if you want code captions
# oldSource <- knitr::knit_hooks$get("source")
# knitr::knit_hooks$set(source = function(x, options) {
#   x <- oldSource(x, options)
#   x <- ifelse(!is.null(options$code.cap), paste0(x, "\\captionof{chunk}{", options$code.cap,"}"), x)
#   ifelse(!is.null(options$ref), paste0(x, "\\label{", options$ref,"}"), x)
# })
# Add `chunkcaption: TRUE` to YAML as well.
```

```{r "env", message=FALSE, warning=F}
rm(list=ls())
here::i_am("report/appendix.Rmd")
source(here::here("src/lib/functions.R"))
load(here("data/intermediate/cleaned_experiment.RData"))
source(here("src/analysis/data-for-analyses.R"))
```
\newpage
# Questionnaire and Descriptive Information
## Dependent Variables
We rely on the two items in the populism scale that mention the people: a) ''The people, not politicians, should make the most important political decisions''; and b) ''The politicians in the German Bundestag need to follow the will of the people''. All items are measured on a 5-point Likert-scale: `very much disagree`, `disagree`, `neutral`, `agree`, `very much agree`. See Table \ref{tab:dv} for the exact phrasing of the question.

```{r dv, topcaption=TRUE}
df <- tibble(Variable = c("Item 2 (DV1)",
                         "Item 3 (DV2)"), 
            `Wording ENG` = c("The people, not politicians, should make the most important political decisions","he politicians in the German Bundestag need to follow the will of the people"),
            `Wording DE` = c("[Die Bürger/Das Volk], und nicht die Politiker, sollte(n) die wichtigsten politischen Entscheidungen treffen", "Die Abgeordneten des Deutschen Bundestags müssen dem Willen [der Bürger/des Volkes] Folge leisten"))

kbl(df, booktabs =T, caption = "\\label{tab:dv}Survey Questions - DV") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "7cm") %>%
  column_spec(3, width = "7cm")

```

## Treatment
Respondents are randomly assigned to the populism items translated into German using either the civic conception (i.e. _Bürger_) or the ethnic conception (i.e. _Volk_).

&nbsp;

## Control Variables

As control variables, the following _demographics_ are measured (see Table \ref{tab:demographics} for the exact phrasing of the question):

- _Gender_ is measured as `sex`. The answer categories are `Male` (value of `1`), `Female` (value of `0`), and `No answer` (value of `999`).

- _Age_ is measured using 6 categories: `17 or younger`, `18--29`, `30--39`, `40--49`, `50--59`, `60--74`.

- _Education_ is measured as the highest successfully completed level of education, recoded into four categories: `low`, `middle`, `high`, and `none`.
I create dummy variables for each level of education with the lowest category as base category.

- _Urbanness_ Respondents are asked for what the type of location they live: `big city`, `suburb of a large city`, `middle-szed or small city`, `rural village`, `detached house in the countryside` -- as well as giving them the options of `will not  say` and `do not know`.

- _Vote Recall_ Respondents were asked which party they voted for in the last election with their second vote. Answering categories were: `CDU/CSU`, `SPD`, `AfD`, `FDP`, `DIE LINKE`, `BÜNDNIS 90/DIE GRÜNEN`, `Other party:`, `I did not vote/was not eligble to vote`-- as well as giving them the options of `will not  say` and `do not know`.

- _Employment_ Respondents were asked which category of employment -- `Full-time employed`, `Part-time employed`, `Entrepreneur`, `Unemployed and searching for a job`, `Unemployed and not searching for a job or incapacitated`, `Housewife/Househusband or else`, `Retired`, `Student or full-time education` -- applied most to them.

- _Income_ Respondents were questioned on their monthly income in bins of 500 Euro -- `500 or less`, `501-1000`, `1001-1500`, `1501-2000`, `2001-2500`, `2501-3000`, `3001-3500`, `3501-4000`, `4501-7500`, `7501 or more` -- as well as giving them the options of `will not  say` and `do not know`.

- _Geographical region_ is measured using the same questions as the [German Longitudinal Election Study](https://www.gesis.org/wahlen/gles), asking respondents where they are born and currently live, differentiating between the different German provinces (_Bundesl{\"a}nder_): Baden-W{\"u}rtemberg, Bavaria, Berlin, Brandenburg, Bremen, Hamburg, Hessen, Lower Saxony, Mecklenburg-Western Pomerania, North Rhine-
Westphalia, Rhineland-Palatinate, Saarland, Saxony, Saxony-Anholt, Schleswig-Holstein, and Thuringia.

```{r demographics, topcaption=TRUE}
df <- tibble(Variable = c("gender (D1)", "age (D2)", "education (D3)",
                         "geographical-region (D4)", "vote-recall2 (D6)", "employment (D7)",
                         "income (D8)", "living-place (D9)", "birth-place (D10)"), 
            `Wording ENG` = c("Which gender do you feel you belong to?", "To which of the following age groups do you belong?",
                              "What is your highest educational qualification?", 
                             "Which of the following categories best describes where you live?",
                             "Which party did you vote for with your second vote in the last federal election in September 2021?",
                             "Now we would like to ask you something about your employment. Which of this list applies to you?",
                              "What is the total monthly net income of your household? This refers to the sum that remains after deducting taxes and social security contributions.",
                             "In which federal state or on the territory of which present federal state do you currently live?",
                              "And in which federal state or on the territory of which present federal state were you born?"),
            `Wording DE` = c("Welchem Geschlecht fühlen Sie sich zugehörig?", 
                             "Zu welcher der nachfolgenden Altersgruppen gehören Sie?",
                             "Was ist Ihr höchster Bildungsabschluss?",
                             "Welche der folgenden Kategorien beschreibt am besten, wo Sie wohnen?",
                             "Welche Partei haben Sie bei der letzten Bundestagswahl im September 2021 mit Ihrer Zweitstimme gewählt?",
                             "Nun möchten wir Sie gerne etwas zu Ihrer Erwerbstätigkeit fragen. Was von dieser Liste trifft auf Sie zu?",
                             "Wie hoch ist das monatliche Netto-Einkommen Ihres Haushaltes insgesamt? Gemeint ist die Summe, die nach Abzug von Steuern und Sozialversicherungsbeiträgen übrig bleibt.",
                             "Im welchen Bundesland bzw. auf dem Gebiet welches heutigen Bundeslandes wohnen Sie derzeit?",
                             "Und in welchem Bundesland bzw. auf dem Gebiet welches heutigen Bundeslandes wurden Sie geboren?"))

kbl(df, booktabs =T, caption = "\\label{tab:demographics}Survey Questions - Demographics") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "7cm") %>%
  column_spec(3, width = "7cm")

```

In addition, pre-treatment, we ask respondents the following questions (see Table \ref{tab:pret}for the exact phrasing of the question):

- _Ideological position_ is measured using an 11-point scale ranging from left (`0`) to right (`10`).

- _Exclusive national identity_ is measured with four statements ("being born in Germany", "having German ancestors", "being able to speak German", "adhering to German traditions and customs") on a 5-point Likert-scale: `very much disagree`, `disagree`, `neutral`, `agree`, `very much agree`.

```{r pret, topcaption=TRUE}
df <- tibble(Variable = c("political-knowledge1 (PT4)", "political-knowledge2 (PT5)", "political-knowledge3 (PT6)", "political-interest (PT7)","RILE (PT8)", "Exclusive national identity (HT4)", "Exclusive national identity (HT4-1)", "Exclusive national identity (HT4-2)", "Exclusive national identity (HT4-3)", "Exclusive national identity (HT4-4)" ), 
            `Wording ENG` = c("In the federal election, you have two votes, a first vote and a second vote. How is that actually, which of the two votes is decisive for the distribution of seats in the Bundestag?",
                             "Now we would like to know from you, from what percentage of the second votes a party can send deputies in any case in the Bundestag?",
                             "And can you say approximately what the current unemployment rate is in Germany? Is it lower or higher than 10 percent?", 
                             "Once speaking in general terms: How interested are you in politics - very strongly, strongly, moderately, less strongly, or not at all?",
                            "In politics, people often talk about 'left' and 'right.' Where would you classify yourself?",
                            "Some people think that the following points are important to be truly German. Others do not think they are important. How important do you think the following points are to being German?", "being born in Germany", "having German ancestors", "being able to speak German", "adhering to German traditions and customs"),
            `Wording DE` = c("Bei der Bundestagswahl haben Sie ja zwei Stimmen, eine Erststimme und eine Zweitstimme. Wie ist das eigentlich, welche der beiden Stimmen ist ausschlaggebend für die Sitzverteilung im Bundestag?",
                             "Jetzt möchten wir gerne von Ihnen wissen, ab wie viel Prozent der Zweitstimmen eine Partei auf jeden Fall Abgeordnete in den Bundestag entsenden kann? ",
                             "Und können Sie ungefähr sagen, wie hoch die derzeitige Arbeitslosenquote in Deutschland ist? Ist sie niedriger oder höher als 10 Prozent?", 
                             "Einmal ganz allgemein gesprochen: Wie stark interessieren Sie sich für Politik – sehr stark, stark, mittelmäßig, weniger stark oder überhaupt nicht?",
                            "In der Politik reden die Leute häufig von 'links' und 'rechts'. Wo würden Sie sich selbst einordnen?",
                            "Manche Leute meinen, dass die folgenden Punkte wichtig sind, um wirklich deutsch zu sein. Andere halten diese nicht für wichtig. Für wie wichtig halten Sie die folgenden Punkte, um deutsch zu sein?", "in Deutschland geboren sein", "deutsche Vorfahren haben", "deutsch sprechen können", "sich an deutsche Traditionen und Gepflogenheiten halten"))

kbl(df, booktabs =T, caption = "\\label{tab:pret}Survey Questions - PreTreatment Questions") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "3cm") %>%
  column_spec(2, width = "7cm") %>%
  column_spec(3, width = "7cm")
```

- _Political knowledge_ is measured with three items. First, respondents are asked which of the two votes is determinative for the seat distribution in parliament: `first vote`, `second vote`, `both`, `do not know`. Secondly, respondents are asked about the electoral threshold. Last, respondents are asked whether or not the unemployment rate is over ten procent.

- _Political interest_ is measured by asking people how strongly they are interested in politics using a 5-point Likert-scale (`very strong`, `strong`, `medium`, `less strong`, `not at all`) -- as well as giving them the options of `will not  say` and `do not know`.

## Attention Checks
We include two attention checks in the survey.
The first one is after the demographic covariates, the second one is asked just before respondents enter the round of the experimental treatments.
The attention checks are taken from @berinsky2014separating and adapted to the German context by the authors.
If a respondents fails the first attention check, a warning appears and the respondent can only continue with the survey once the respondent has correctly answered the question correctly.
The second attention check also has a warning -- meaning that respondents have to select two options -- but if they fail to correctly pass the check, they are excluded.
Each excluded respondent due to failing an attention check is replaced with another ``good respondent".

**Attention Check 1**  When a big news story breaks people often go online to get up-to-the-minute details on what is going on.
We want to know which websites people trust to get this information.
We also want to know if people are paying attention to the question.
To show that you have read this much, please ignore the question and select BILD-Zeitung and Süddeutsche Zeitung as your two answers.
When there is a big news story, which is the one news website you would visit first? (Please only choose one).
Eight (German) news outlets are provided to choose from.
Respondents pass the attention check if they select _BILD-Zeitung_ and _Süddeutsche Zeitung_.

**Attention Check 2**:
We would like to get a sense of your general preferences.
Most  modern  theories  of  decision  making  recognize  that  decisions  do  not take  place  in  a  vacuum.
Individual  preferences  and  knowledge,  along  with  situational variables can greatly impact the decision process.
To demonstrate that you've read this much,  just  go  ahead  and  select  both  red  and  green  among  the  alternatives  below,  no matter what your favourite color is.  Yes, ignore the question below and select both of those options.
What is your favourite color?
Six colors are provided to choose from, respondents pass the attention check if they select red and green.

## Descritive Information
Table \ref{tab:descr} gives an overview of the descriptive information of the variables under study.

```{r "Table with Descriptives"}
source(here("src/analysis/descriptive-information-overview.R"))
kbl(descr, booktabs =T, caption = "\\label{tab:descr}Descriptive Information") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "2cm")  %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm") 
```

\newpage
# Balance Checks
As detailed in our pre-analysis plan, we only include variables as covariates that are unbalanced. 
As Figure \ref{fig:balance} shows, only the income covariate is unbalanced accross the experimental groups.
We therefore add this covariate to the regression analyses.

```{r oa-balance, fig.align = 'center', out.width = "70%", fig.cap = "\\label{fig:balance}Balance Checks"}
  knitr::include_graphics(here::here("report/figures", "balance-checks-1.png"))
```

\newpage
# Pre-Registered and Explorative Analysis
Table \ref{tab:h1} demonstrates the results as visualized in Figure 1 in the paper.
```{r "h1", fig.align="center", fig.height=5, fig.width=6}
p1 <- d %>% 
  mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
  select(POST_2, POST_3, ethnic) %>%
  pivot_longer(cols = POST_2:POST_3) %>%
  group_by(ethnic, name) %>%
  summarise(value = list(value)) %>%
  spread(ethnic, value) %>%
  group_by(name) %>%
  mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
         t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
         means_civic = t.test(unlist(`Civic Conception`))$estimate,
         means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
         means_difference = means_civic - means_ethnic,
         lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
         name = recode(name,
                       `POST_2` = "DV: People, not politicians, should make the most  important political decisions",
                       `POST_3` = "DV: MPs should follow the will of the people")) %>%
  select(var = name, p_value, t_value, means_difference, lower, higher) %>%
  pivot_longer(cols = p_value:higher) %>%
  mutate(name = recode(name,
                       `p_value` = "p-value",
                       `t_value` = "t-value",
                       `means_difference` = "Differences in Means",
                       `lower` = "CI: Lower Bound",
                       `higher` = "CI: Upper Bound")) %>%
  ungroup()

tmp <- p1 %>%
  filter(var == "DV: People, not politicians, should make the most  important political decisions") %>%
  select(`Statistical Values` = name, `DV: People, not politicians, should make the most  important political decisions` = value)

tmpp <- p1 %>%
  filter(var == "DV: MPs should follow the will of the people") %>%
  select(`DV: MPs should follow the will of the people` = value)

p1 <- tmp %>%
  add_column(tmpp)

kbl(p1, booktabs =T, caption = "\\label{tab:h1}Table Results H1") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm")  %>%
  column_spec(3, width = "4cm")

```
\newpage

Table \ref{tab:h2a} and \ref{tab:h2b} demonstrate the results as visualized in Figure 2 in the paper.
```{r "h2a", fig.align="center", fig.height=5, fig.width=6}
df <- d %>%
  mutate(a = HT4)
h2a <- regression2(df, a, ethnic) %>%
  pivot_longer(cols = AME) %>%
  mutate(a = recode(a, 
                    `1` = "1 (Low)", `2` = "2", `3` = "3", `4` = "4",
                    `5` = "5 (High"),
         y = recode(y,
                    `POST_2` = "DV: People, not politicians, should make the most  important political decisions",
                    `POST_3` = "DV: MPs should follow the will of the people")) %>%
  select(`Dependent Variable` = y, `Levels of National Exclusivity` = a,
         AME = value, `CI: Lower Bound` = lower, `CI: Upper Bound` = upper)

kbl(h2a, booktabs =T, caption = "\\label{tab:h2a}Table Results H2a") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")
```

```{r "h2b", fig.align="center", fig.height=5, fig.width=6}
df <- d %>%
  mutate(a = Afd_vote)
h2b <- regression(df, a, ethnic) %>%
  mutate(ethnic = recode(ethnic, 
                    `0` = "Civic Conception", 
                    `1` = "Ethnic Conception"),
         y = recode(y,
                    `POST_2` = "DV: People, not politicians, should make the most  important political decisions",
                    `POST_3` = "DV: MPs should follow the will of the people")) %>%
  select(`Dependent Variable` = y, Treatment = ethnic,
         AME, `CI: Lower Bound` = lower, `CI: Upper Bound` = upper)

kbl(h2b, booktabs =T, caption = "\\label{tab:h2b}Table Results H2b") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")
```

\newpage
# Scaling

## CFA
```{r "oa-cfa", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/explorative_cfa.R"))

kbl(m_cfa, booktabs =T, caption = "Confirmatory Factor Analysis - Fit Statistics") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm")  %>%
  column_spec(3, width = "4cm") %>%
  column_spec(4, width = "5cm") 
```
```{r "oa-cfa1", fig.align="center", fig.height=8, fig.width=8}
kbl(cfa1, booktabs =T, caption = "Confirmatory Factor Analysis") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "8cm") %>%
  column_spec(2, width = "3cm") 
```

```{r oa-cfa2, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:cfa}CFA Distribution"}
knitr::include_graphics(here::here("report/figures", "scale-1.png"))
```
## Additive scale
```{r "oa-addative", fig.align="center", fig.height=8, fig.width=12}
source(here("src/analysis/additive-scale.R"))

kbl(add1, booktabs =T, caption = "Addative Scaling Analysis") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "3cm")

```

```{r oa-add, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:add}Addative Scale Distribution"}
knitr::include_graphics(here::here("report/figures", "addative-1.png"))
```

## Wüttke et al. Approach
```{r "oa-wuttke", fig.align="center", fig.height=8, fig.width=12}
source(here("src/analysis/wuttke-approach.R"))

kbl(wa1, booktabs =T, caption = "Wüttke et al. Approach") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "3cm")  
```

```{r oa-wuttke-2, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:wuttke}Wuttke et al. Approach Distribution"}
knitr::include_graphics(here::here("report/figures", "wuttke-1.png"))
```

## IRT Analyse
```{r "oa-irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
source(here("src/analysis/IRT.R"))
```
```{r oa-irt1, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:irt1}IRT Distribution (1)"}
knitr::include_graphics(here::here("report/figures", "irt-1.png"))
```

```{r "oa-irt2", fig.align="center", fig.height=8, fig.width=12}
kbl(irt3, booktabs =T, caption = "IRT Analysis") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "3cm")  
```

```{r oa-irt3, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:irt1}IRT Distribution (1)"}
knitr::include_graphics(here::here("report/figures", "irt-2.png"))
```

\newpage
# Explanatory Power: Predicting Populist Vote
```{r "oa-predict-vote-1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/predict-pop-vote-scales.R"))
dv1 <- exp2 %>%
  filter(y == "Voted: Populist Party") %>%
  dplyr::select(`Regression Coefficient` = estimate,
         `CI: Lower Bound` = lower, 
         `CI: Upper Bound` = upper, 
         `Scaling Technique` = id,
         `Treatment` = ethnic)
kbl(dv1, booktabs =T, caption = "Table Results DV: Populist Vote") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")

dv2<- exp2 %>%
  filter(y == "Voted: AfD") %>%
  dplyr::select(`Regression Coefficient` = estimate,
         `CI: Lower Bound` = lower, 
         `CI: Upper Bound` = upper, 
         `Scaling Technique` = id,
         `Treatment` = ethnic)
kbl(dv2, booktabs =T, caption = "Table Results DV: AfD Vote") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")

dv3 <- exp2 %>%
  filter(y == "Voted: Left") %>%
  dplyr::select(`Regression Coefficient` = estimate,
         `CI: Lower Bound` = lower, 
         `CI: Upper Bound` = upper, 
         `Scaling Technique` = id,
         `Treatment` = ethnic)
kbl(dv3, booktabs =T, caption = "Table Results DV: Left Vote") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")
```

```{r "oa-predict-vote-2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/predict-pop-vote-items.R"))
dv1 <- exp2 %>%
  filter(y == "Voted: Populist Party") %>%
  dplyr::select(`Regression Coefficient` = estimate,
         `CI: Lower Bound` = lower, 
         `CI: Upper Bound` = upper, 
         `Items` = id,
         `Treatment` = ethnic)
kbl(dv1, booktabs =T, caption = "Table Results DV: Populist Vote") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")

dv2<- exp2 %>%
  filter(y == "Voted: AfD") %>%
  dplyr::select(`Regression Coefficient` = estimate,
         `CI: Lower Bound` = lower, 
         `CI: Upper Bound` = upper, 
         `Scaling Technique` = id,
         `Treatment` = ethnic)
kbl(dv2, booktabs =T, caption = "Table Results DV: AfD Vote") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")

dv3 <- exp2 %>%
  filter(y == "Voted: Left") %>%
  dplyr::select(`Regression Coefficient` = estimate,
         `CI: Lower Bound` = lower, 
         `CI: Upper Bound` = upper, 
         `Scaling Technique` = id,
         `Treatment` = ethnic)
kbl(dv3, booktabs =T, caption = "Table Results DV: Left Vote") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")
```

### 2021-11-23 report/draft.Rmd
add Online Appendix

@@
 mainfont: cochineal
-#sansfont: Linux Biolinum O
 fontsize: 11pt
@@
   doublespacing: ""
-twocol: FALSE
-appendix: TRUE
 doublespacing: TRUE
 endnote: no
-# pandocparas: TRUE
+pandocparas: TRUE
 sansitup: FALSE
@@
 We rely on a nationally representative sample of German citizens over 18 years old (`N=6,713`). 
-The sample is from an online panel provided by the survey company Respondi. 
+The sample is from an online panel provided by the survey company Respondi -- for an overview of all variables in the study, as well as the descriptive information, see Online Appendix (OA pp.
+A2-A6).
 Quotas for age, gender, and education were included to ensure the representativeness of the sample. 
@@
 Yet, due to an unfortunate translation error in Qualtrics, we cannot use the item `POP4` in our analysis.
-However, robustness checks in the Appendix XXX shows that removal of the item does not strongly affect the overall latent construct.
+However, robustness checks in the Online Appendix (OA) Table A.8 shows that removal of the item does not strongly affect the overall latent construct.
 
-Figure \ref{fig:results-h1} shows the results of a difference of means test for the two treatment groups (ethnic vs. civic wording) for both items. 
+Figure \ref{fig:results-h1} shows the results of a difference of means test for the two treatment groups (ethnic vs. civic wording) for both items -- Table A.5 in the OA shows the coefficients. 
 There is a statistically significant difference in respondent agreement with the ethnic and civic conception of the people. 
@@
 How does the effect of an ethnic conception of the people vis-à-vis a civic conception vary across respondents? 
-The left-hand panel of Figure \ref{fig:results-h2} shows the results of an OLS regression analysis with the an interaction between the treatment and a variable measuring whether or not the respondent voted for the far right party _Alternative für Deutschland_.
+The left-hand panel of Figure \ref{fig:results-h2} shows the results of an OLS regression analysis[^2] with the an interaction between the treatment and a variable measuring whether or not the respondent voted for the far right party _Alternative für Deutschland_ -- for more details see Table A.6 in the OA).
 We see that far right voters show much more agreement to items `POP1` and `POP2` when it is phrased in an ethnic way. 
 These effects are substantial and statistically significant. 
-[ADD ONE SENTENCE ABOUT THIS].
+For the item `POP2` (''the people, not politicians, should make the most important political decisions''), when voting for the AfD and being in the ethnic conception of the people condition, one scores on average a full point higher on a 5-point scale, which is about a full standard deviation.
+For the item `POP1` (''The politicians need to follow the will of the people''), the effect size is about half a point (i.e. half a standard deviation).
+
+[^2]: As specified in the Pre-Analysis Plan, we only include unbalanced covariates.
+OA p.
+A-7 demonstrates the balance checks, demonstrating that only income is unbalanced, and therefore included as a covariate.
 
@@
 Inspired by @mader2021, we measure exclusive national identity using a four-item additive scale on a 5-point Likert scale, which asks respondents to rate how important the following aspects are to be considered German: being born in Germany (a), having German ancestors (b), being able to speak German (c), and sharing share German manners and norms (d).
-The right-hand panel of Figure \ref{fig:results-h2} shows the interaction between the treatment and the exclusive national identity variable on the two items. 
+The right-hand panel of Figure \ref{fig:results-h2} shows the interaction between the treatment and the exclusive national identity variable on the two items -- for more details see Table A.7 in the OA).
+Compared to not adhering to an exclusive national identity, the average score of fully adhering to an exclusive national identity is 0.2 higher on a 5-point scale for the item `POP2` (''the people, not politicians, should make the most important political decisions'').
+Compared the standard deviation of this item (1.17, see Table A.4 in the OA), this is a small effect.
+For the other item, the line is much less steep over the various levels of adherence to an exclusive national identity.
 Overall, we see that the difference between an ethnic and civic wording is only statistically significant for respondents with higher levels of exclusive national identity (ca.
@@
 Therefore, also overall difference between a latent construct of populism with two ethnically framed items and a latent construct with two civically framed items is small.
-We find no statistically significant difference between the two constructs estimated using Confirmatory Factor Analysis (see Figure XX and Table XX in the Appendix). 
+We find no statistically significant difference between the two constructs estimated using Confirmatory Factor Analysis (see Table A.9 in the OA). 
 In terms of model fit, both constructs show very similar goodness-of-fit statistics (i.e., CFI, BIC, RMSEA, and SRMR).
-Interestingly, however, both the 'ethnic' and the 'civic' scale show a satisfactory model fit (`CFI > 0.9`; `RMSEA < 0.08`; and `SRMR < 0.02`).
+Interestingly, however, both the 'ethnic' and the 'civic' scale show a satisfactory model fit (`CFI > 0.9`; `RMSEA < 0.08`; and `SRMR < 0.02`) -- for more information see OA Table A.8.
 

### 2021-11-23 report/figures/table_descriptives.tex
add Online Appendix

--- 2021-11-10 report/figures/table_descriptives.tex
@@
   <tr>
-   <td style="text-align:left;"> DV: Item 4 </td>
-   <td style="text-align:right;"> 3.55 </td>
+   <td style="text-align:left;"> Differences between elites and 
+ the people are bigger than 
+ differences between the people </td>
+   <td style="text-align:right;"> 3.5 </td>
+   <td style="text-align:right;"> 1.00 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
+   <td style="text-align:left;"> Too much talk, no action </td>
+   <td style="text-align:right;"> 4.0 </td>
    <td style="text-align:right;"> 0.99 </td>
@@
   <tr>
+   <td style="text-align:left;"> Compromise is selling out </td>
+   <td style="text-align:right;"> 3.2 </td>
+   <td style="text-align:right;"> 1.14 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
+   <td style="text-align:left;"> Attitude towards Pluralism </td>
+   <td style="text-align:right;"> 4.2 </td>
+   <td style="text-align:right;"> 0.83 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
    <td style="text-align:left;"> Political Interest </td>
-   <td style="text-align:right;"> 2.93 </td>
-   <td style="text-align:right;"> 1.09 </td>
+   <td style="text-align:right;"> 2.9 </td>
+   <td style="text-align:right;"> 1.10 </td>
    <td style="text-align:right;"> 1 </td>

### 2021-11-23 src/analysis/analyses.Rmd
add files for rough draft
add Online Appendix

--- 2021-11-19 src/analysis/analyses.Rmd
@@
 ```{r "h2", fig.align="center", fig.height=6, fig.width=12, echo = FALSE, fig.show = "hide"}
-p2a + p2c + 
-  plot_layout(widths = c(2, 1))
+p2c + p2a + 
+  plot_layout(widths = c(1, 2))
 ```
@@
   column_spec(2, width = "4cm")  %>%
-  column_spec(2, width = "4cm") %>%
-  column_spec(2, width = "4cm")
+  column_spec(3, width = "4cm") %>%
+  column_spec(4, width = "4cm")
 
@@
 
-## IRT Analyse
+### Additive scale
+```{r "addative", fig.align="center", fig.height=8, fig.width=12}
+source(here("src/analysis/additive-scale.R"))
+
+kbl(add1, booktabs =T, caption = "Addative Scaling Analysis") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "10cm") %>%
+  column_spec(2, width = "3cm")
+
+add2
+```
+
+### Wüttke et al. Approach
+```{r "wuttke", fig.align="center", fig.height=8, fig.width=12}
+source(here("src/analysis/wuttke-approach.R"))
+
+kbl(wa1, booktabs =T, caption = "Wüttke et al. Approach") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "10cm") %>%
+  column_spec(2, width = "3cm")
+
+wa2
+```
+
+### IRT Analyse
 ```{r "irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
 source(here("src/analysis/IRT.R"))
-
 ```
@@
   plot_layout(widths = c(1, 2))
+
+kbl(irt3, booktabs =T, caption = "IRT Analysis") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "10cm") %>%
+  column_spec(2, width = "3cm")
+
+irt4
 ```
+
+## Explanatory Power: Predicting Populist Vote
+```{r "predict-vote-1", fig.align="center", fig.height=8, fig.width=8}
+source(here("src/analysis/predict-pop-vote-scales.R"))
+exp1
+```
+
+```{r "predict-vote-2", fig.align="center", fig.height=8, fig.width=8}
+source(here("src/analysis/predict-pop-vote-items.R"))
+exp1
+```
+
+## Save Data with Scales
+```{r "save data"}
+save(d, file = here("data/intermediate/cleaned_experiment_scales.RData"))
+```

### 2021-11-23 src/analysis/IRT.R

@@ -190,3 +190,44 @@ tmp <- d %>%
 
 d <- d %>%
   add_column(tmp)
+
+irt3 <- d %>%
+  dplyr::select(irt_pa, ethnic) %>%
+  dplyr::mutate(ethnic = dplyr::recode(ethnic, 
+                                `1` = "Ethnic Conception", 
+                                `0` = "Civic Conception")) %>%
+  dplyr::group_by(ethnic) %>%
+  dplyr::summarise(irt_pa = list(irt_pa)) %>%
+  spread(ethnic, irt_pa) %>%
+  dplyr::mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
+         t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
+         means_civic = t.test(unlist(`Civic Conception`))$estimate,
+         means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
+         means_difference = means_civic - means_ethnic,
+         lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
+         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
+         name = "Differences in Means") %>%
+  dplyr::select(means_civic, means_ethnic, means_difference, p_value) %>%
+  pivot_longer(cols = means_civic:p_value,
+               values_to = "Values",
+               names_to = "Variables") %>%
+  dplyr::mutate(Variables = dplyr::recode(Variables,
+                            `means_civic` = "Average of IRT Constructed Scale for Civic Conception of the People",
+                            `means_ethnic` = "Average of IRT Constructed Scale for Ethnic Conception of the People",
+                            `means_difference` = "Average of Civic Conception - Average of Ethnic Conception",
+                            `p_value` = "p-Value for Differences in Means"))
+
+
+irt4 <- d %>%
+  dplyr::mutate(ethnic = dplyr::recode(ethnic,
+                         `0` = "Civic Conception",
+                         `1` = "Ethnic Conception")) %>%
+  ggplot(aes(x = irt_pa, color = ethnic, fill = ethnic)) +
+  labs(y= "Density", x = "Distribution IRT Construct") +
+  geom_histogram(binwidth=1) +
+  facet_grid(.~ethnic) +
+  theme_ipsum()  +
+  scale_color_manual(values = fig_cols) +
[…]

### 2021-11-23 src/analysis/additive-scale.R

@@ -1,13 +1,13 @@
 as_e <- d %>%
   filter(ethnic == 1) %>%
   mutate(scale = round((POST_1 + POST_2 + POST_3 + 
-                          POST_5 + POST_6)/5,0)) 
+                          POST_5 + POST_6)/5,2)) 
 as_e <- as_e$scale
   
 as_c <- d %>%
   filter(ethnic == 0) %>%
   mutate(scale = round((POST_1 + POST_2 + POST_3 + 
-                          POST_5 + POST_6)/5,0)) 
+                          POST_5 + POST_6)/5,2)) 
 as_c <- as_c$scale
 
 add1 <- d %>%

### 2021-11-23 src/analysis/descriptive-information-overview.R

@@ -1,5 +1,5 @@
 descr <- d %>%
-  select(D7:D8, pol_know:POST_4, POST_8, -POST_1) %>%
+  select(D7:D8, pol_know:POST_6, POST_8, -POST_1) %>%
   pivot_longer(cols = D7:POST_8,
                names_to = "Variables") %>%
   group_by(Variables) %>%
@@ -14,9 +14,12 @@ descr <- d %>%
                             `pol_know`  = "Political Knowledge",
                             `PT7`  = "Political Interest",
                             `PT8`  = "Ideology",
+                            `POST_1` = "Rep. by ordinary citizen",
                             `POST_2`  = "DV: People, not politicians, \n should make the most \n important political decisions",
                             `POST_3` = "DV: MPs should follow \n the will of the people",
-                            `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people",
+                            `POST_4` = "Differences between elites and \n the people are bigger than \n differences between the people",
+                            `POST_5` = "Too much talk, no action",
+                            `POST_6` = "Compromise is selling out",
                             `POST_8` = "Attitude towards Pluralism",
                             `HT4`  = "National Identity",
                             `Afd_vote` = "Far Right Party ID",
@@ -24,7 +27,9 @@ descr <- d %>%
          Variables = factor(Variables,
                             levels = c("DV: People, not politicians, \n should make the most \n important political decisions",
                                        "DV: MPs should follow \n the will of the people",
-                                       "DV: Differences between elites and \n the people are bigger than \n differences between the people",
+                                       "Rep. by ordinary citizen",
+                                       "Differences between elites and \n the people are bigger than \n differences between the people",
+                                       "Too much talk, no action","Compromise is selling out",
                                        "Attitude towards Pluralism",
                                        "Treatment: Ethnic Conception",
                                        "National Identity",

### 2021-11-23 src/analysis/explorative_cfa.R

@@ -67,11 +67,10 @@ cfa2 <- d %>%
   ggplot(aes(x = cfa_pa, color = ethnic, fill = ethnic)) +
   labs(y= "Density", x = "Distribution CFA Construct") +
   geom_histogram(binwidth=.5) +
-  stat_density(alpha=.2) +
   facet_grid(.~ethnic) +
-  theme_ipsum()  +
   scale_color_manual(values = fig_cols) +
   scale_fill_manual(values = fig_cols) +
+  theme_ipsum()  +
   theme(legend.position="none",
         legend.title = element_blank())
 

### 2021-11-23 src/analysis/h2a.R

@@ -4,9 +4,9 @@ h2a <- regression2(df, a, ethnic)
   
 p2a <- h2a %>%
   mutate(y = recode(y,
-                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
-                    `POST_3` = "DV: MPs should follow \n the will of the people",
-                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
+                    `POST_2` = "DV: People, not politicians, should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow the will of the \n people",
+                    `POST_4` = "DV: Differences between elites an the people are bigger than \n differences between the people")) %>%
   ggplot(aes(x = a, 
              y = AME,
              color = y,
@@ -18,7 +18,7 @@ p2a <- h2a %>%
   #geom_errorbar(position = position_dodge(.5), width = 0) +
   theme_ipsum() +
   labs(x = "Exclusive National Identity \n (1 = Low, 5 = High)", 
-       y = "Average Marginal Effects of Levels of Ethnic Conception of the People") +
+       y = "Average Marginal Effects for\n Ethnic Conception of the People") +
   facet_grid(.~y) +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),

### 2021-11-23 src/analysis/h2b.R

@@ -8,9 +8,9 @@ p2b <- h2b %>%
                     `POST_3` = "DV: MPs should follow \n the will of the people",
                     `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people"),
          ethnic = recode(ethnic,
-                         `1` = "Ethnic Conception",
+                         `1` = "Ethnic Conception of the People",
                          `0` = "Civic Conception")) %>%
-  filter(ethnic == "Ethnic Conception") %>%
+  filter(ethnic == "Ethnic Conception of the People") %>%
   ggplot(aes(x = y, 
              y = AME,
              color = y,
@@ -35,9 +35,9 @@ p2c <- h2b %>%
                     `POST_3` = "DV: MPs should follow \n the will of the people",
                     `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people"),
          ethnic = recode(ethnic,
-                         `1` = "Ethnic Conception",
+                         `1` = "Ethnic Conception of the People",
                          `0` = "Civic Conception")) %>%
-  filter(ethnic == "Ethnic Conception") %>%
+  filter(ethnic == "Ethnic Conception of the People") %>%
   ggplot(aes(x = y, 
              y = AME,
              color = y,

### 2021-11-23 src/analysis/predict-pop-vote-items.R

@@ -101,7 +101,7 @@ for(i in 1:length(Ethnic)){
     tmp <- tmp %>%
       add_case(tmpp)}
 }
-exp <- exp %>%
+exp1 <- exp %>%
   add_case(tmp) %>%
   dplyr::mutate(y = dplyr::recode(y,
                                   `Afd_vote` = "Voted: AfD",
@@ -135,3 +135,19 @@ exp <- exp %>%
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
   coord_flip() +
   guides(color=guide_legend(nrow=2,byrow=TRUE))
+
+exp2 <- exp %>%
+  add_case(tmp) %>%
+  dplyr::mutate(y = dplyr::recode(y,
+                                  `Afd_vote` = "Voted: AfD",
+                                  `Linke_vote` = "Voted: Left",
+                                  `pop_vote` = "Voted: Populist Party"),
+                id = dplyr::recode(id,
+                                   `POST_1` = "Item 1 - Compromise is selling out",
+                                   `POST_2` = "Item 2 - The people must decide",
+                                   `POST_3` = "Item 3 - Follow will of the peopl",
+                                   `POST_5` = "Item 5 - Too much talk, no action",
+                                   `POST_6` = "Item 6 - Rep. by ordinary citizen"),
+                ethnic = dplyr::recode(ethnic,
+                                       `1` = "Ethnic Conception",
+                                       `0` = "Civic Conception"))

### 2021-11-23 src/analysis/predict-pop-vote-scales.R

@@ -4,7 +4,7 @@ for(i in 1:length(Ethnic)){
 df <- d %>%
     dplyr::filter(ethnic == Ethnic[i]) %>%
     mutate(pop_vote = ifelse(D6 == "AfD", 1,
-                             ifelse(D6 == "Left", 1, 0)),
+                      ifelse(D6 == "Left", 1, 0)),
            Linke_vote = ifelse(D6 == "Left", 1,0),
            scale = cfa_pa)
 if(i==1){
@@ -23,7 +23,7 @@ for(i in 1:length(Ethnic)){
   df <- d %>%
     dplyr::filter(ethnic == Ethnic[i]) %>%
     mutate(pop_vote = ifelse(D6 == "AfD", 1,
-                             ifelse(D6 == "Left", 1, 0)),
+                      ifelse(D6 == "Left", 1, 0)),
            Linke_vote = ifelse(D6 == "Left", 1,0),
            scale = add_pa)
   if(i==1){
@@ -80,7 +80,7 @@ for(i in 1:length(Ethnic)){
       add_case(tmpp)}
 }
 
-exp <- exp %>%
+exp1 <- exp %>%
   add_case(tmp) %>%
   dplyr::mutate(y = dplyr::recode(y,
                     `Afd_vote` = "Voted: AfD",
@@ -112,3 +112,18 @@ exp <- exp %>%
   scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
   coord_flip()
+
+exp2 <- exp %>%
+  add_case(tmp) %>%
+  dplyr::mutate(y = dplyr::recode(y,
+                                  `Afd_vote` = "Voted: AfD",
+                                  `Linke_vote` = "Voted: Left",
+                                  `pop_vote` = "Voted: Populist Party"),
+                id = dplyr::recode(id,
+                                   `add_pa` = "Addative Scale",
+                                   `cfa_pa` = "CFA Scaling",
+                                   `irt_pa` = "IRT Scaling",
+                                   `wuttke_pa` = "Wüttke et al. Approach"),
+                ethnic = dplyr::recode(ethnic,
+                                       `1` = "Ethnic Conception",
+                                       `0` = "Civic Conception"))

### 2021-11-23 src/lib/functions.R

@@ -231,8 +231,8 @@ regression6 <- function(df, a, ethnic){
 regression7 <- function(df, scale){
   
   depVarList <- df %>% dplyr::select(pop_vote, Afd_vote, Linke_vote)
-  indepVarList <- df %>% dplyr::select(scale, D8)
-  allModels <- apply(depVarList,2,function(xl)lm(xl ~ scale + D8,
+  indepVarList <- df %>% dplyr::select(scale, D8, PT8)
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ scale + D8 + PT8,
                                                  data= indepVarList))
   depVarList <- df %>% dplyr::select(pop_vote, Afd_vote, Linke_vote) %>%
     colnames()

### 2021-12-08 report/figures/table_descriptives.tex
add analyses

--- 2021-11-10 report/figures/table_descriptives.tex
@@
    <td style="text-align:left;"> Employment </td>
-   <td style="text-align:right;"> 4.18 </td>
-   <td style="text-align:right;"> 3.85 </td>
+   <td style="text-align:right;"> 4.2 </td>
+   <td style="text-align:right;"> 3.87 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:left;"> National Identity </td>
-   <td style="text-align:right;"> 3.63 </td>
-   <td style="text-align:right;"> 0.90 </td>
+   <td style="text-align:right;"> 3.6 </td>
+   <td style="text-align:right;"> 0.89 </td>
    <td style="text-align:right;"> 1 </td>
@@
   <tr>
-   <td style="text-align:left;"> DV: Item 2 </td>
-   <td style="text-align:right;"> 3.32 </td>
-   <td style="text-align:right;"> 1.17 </td>
+   <td style="text-align:left;"> DV: People, not politicians, 
+ should make the most 
+ important political decisions </td>
+   <td style="text-align:right;"> 3.3 </td>
+   <td style="text-align:right;"> 1.19 </td>
    <td style="text-align:right;"> 0 </td>
@@
   <tr>
-   <td style="text-align:left;"> DV: Item 3 </td>
-   <td style="text-align:right;"> 3.84 </td>
-   <td style="text-align:right;"> 0.97 </td>
-   <td style="text-align:right;"> 0 </td>
-   <td style="text-align:right;"> 5 </td>
-  </tr>
-  <tr>
-   <td style="text-align:left;"> DV: Item 4 </td>
-   <td style="text-align:right;"> 3.55 </td>
+   <td style="text-align:left;"> DV: MPs should follow 
+ the will of the people </td>
+   <td style="text-align:right;"> 3.8 </td>
    <td style="text-align:right;"> 0.99 </td>
@@
   <tr>
+   <td style="text-align:left;"> Differences between elites and 
+ the people are bigger than 
+ differences between the people </td>
+   <td style="text-align:right;"> 3.5 </td>
+   <td style="text-align:right;"> 1.02 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
+   <td style="text-align:left;"> Too much talk, no action </td>
+   <td style="text-align:right;"> 4.0 </td>
+   <td style="text-align:right;"> 1.01 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
+   <td style="text-align:left;"> Compromise is selling out </td>
+   <td style="text-align:right;"> 3.2 </td>
+   <td style="text-align:right;"> 1.15 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
+   <td style="text-align:left;"> Attitude towards Pluralism </td>
+   <td style="text-align:right;"> 4.2 </td>
+   <td style="text-align:right;"> 0.86 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
    <td style="text-align:left;"> Political Interest </td>
-   <td style="text-align:right;"> 2.93 </td>
+   <td style="text-align:right;"> 2.9 </td>
    <td style="text-align:right;"> 1.09 </td>

### 2021-12-08 src/data-processing/prep_data.Rmd
add Online Appendix
add analyses

@@
 source(here("src/data-processing/clean_data.R"))
+
+dem <- read_delim(here("data/raw-private/14651 data matched final.csv"), 
+                  delim = ";") %>%
+  select(id = tic, D2 = age, D1 = gender, D3 = education)
+
+d <- left_join(d, dem)
+rm(dem)
 ```
@@
 ## Save Data for Analysis
-```{r "save data",eval=FALSE}
+```{r "save data"}
 save(d, file = here("data/intermediate/cleaned_experiment.RData"))
@@
   mutate(HT4 = (HT4_1 + HT4_2 + HT4_3 + HT4_4)/4) %>%
-  select(#`Gender` = D1,
-         #`Age` = D2,
-         #`Education` = D3,
+  select(`Gender` = D1,
+         `Age` = D2,
+         `Education` = D3,
          `Region`  = D9,

### 2021-12-08 src/analysis/IRT.R

@@ -185,11 +185,14 @@ irt_e <- pattern_e$score.dat$z1
 irt_c <- pattern_c$score.dat$z1
 
 tmp <- d %>%
-  dplyr::mutate(irt_pa = ifelse(ethnic == 1, irt_e,irt_c)) %>%
-  dplyr::select(irt_pa)
+  filter(ethnic == 1) %>%
+  mutate(irt_pa = irt_e)
 
 d <- d %>%
-  add_column(tmp)
+  dplyr::filter(ethnic == 0) %>%
+  dplyr::mutate(irt_pa = irt_c) %>%
+  add_case(tmp)
+
 
 irt3 <- d %>%
   dplyr::select(irt_pa, ethnic) %>%

### 2021-12-08 src/analysis/additive-scale.R

@@ -1,22 +1,24 @@
 as_e <- d %>%
   filter(ethnic == 1) %>%
-  mutate(scale = round((POST_1 + POST_2 + POST_3 + 
-                          POST_5 + POST_6)/5,2)) 
-as_e <- as_e$scale
-  
-as_c <- d %>%
+  mutate(add_pa = (POST_1 + POST_2 + POST_3 + 
+                          POST_5 + POST_6)/5) %>%
+  select(id, add_pa)
+
+as_df <- d %>%
   filter(ethnic == 0) %>%
-  mutate(scale = round((POST_1 + POST_2 + POST_3 + 
-                          POST_5 + POST_6)/5,2)) 
-as_c <- as_c$scale
+  mutate(add_pa = (POST_1 + POST_2 + POST_3 + 
+                          POST_5 + POST_6)/5) %>%
+  select(id, add_pa) %>% 
+  add_case(as_e)
+  
 
 add1 <- d %>%
-  mutate(scale = ifelse(ethnic == 1, as_e, as_c)) %>%
-  select(scale, ethnic) %>%
+  left_join(as_df) %>%
+  select(add_pa, ethnic) %>%
   mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
   group_by(ethnic) %>%
-  summarise(scale = list(scale)) %>%
-  spread(ethnic, scale) %>%
+  summarise(add_pa = list(add_pa)) %>%
+  spread(ethnic, add_pa) %>%
   mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
          t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
          means_civic = t.test(unlist(`Civic Conception`))$estimate,
@@ -37,11 +39,11 @@ add1 <- d %>%
 
 
 add2 <- d %>%
-  mutate(scale = ifelse(ethnic == 1, as_e, as_c),
-         ethnic = recode(ethnic,
+  left_join(as_df) %>%
+  mutate(ethnic = recode(ethnic,
                          `0` = "Civic Conception",
                          `1` = "Ethnic Conception")) %>%
-  ggplot(aes(x = scale, color = ethnic, fill = ethnic)) +
+  ggplot(aes(x = add_pa, color = ethnic, fill = ethnic)) +
[…]

### 2021-12-08 src/analysis/balance-test.R

@@ -1,17 +1,24 @@
 covs <- d %>%
-  select(ethnic, D4, D7:PT8) %>%
-  filter(D4 != "NA",
+  select(ethnic, D1:D4, D7:PT8) %>%
+  filter(D1 != "NA",
+         D2 != "NA",
+         D3 != "NA",
+         D4 != "NA",
          D7 != "NA",
          D8 != "NA",
          D9 != "NA",
          D10 != "NA")
 
-balanced <-bal.tab(ethnic ~ factor(D4) + D7 + D8 + factor(D9) +
+balanced <-bal.tab(ethnic ~ factor(D1) +  factor(D2) + factor(D3) + 
+                     factor(D4) + D7 + D8 + factor(D9) +
                      factor(D10) + pol_know + PT7 + PT8,
                    data = covs,
                    thresholds = c(m = 0.05))[[1]] 
 df <- balanced %>%
-  mutate(variable = c("Urbanness: Big City", "Urbanness: Countryside", "Urbanness: Middlesized City", 
+  mutate(variable = c("Male", "Age: 18 - 29", "Age: 30 - 39", "Age: 40 - 49",
+                      "Age: 50 - 59", "Age: 60 - 74", "High Levels of Education",
+                      "Low Levels of Education", "Medium Levels of Education",
+                      "Urbanness: Big City", "Urbanness: Countryside", "Urbanness: Middlesized City", 
                           "Urbanness: Rural Village", "Urbanness: Suburb",
                           "Employment", "Income", "Living Place: Badem-Würtemberg",
                           "Living Place: Bavaria", "Living Place: Berlin",
@@ -33,7 +40,10 @@ df <- balanced %>%
                           "Political Knowledge", "Political Interest",
                           "Ideology"),
          variable = factor(variable,
-                           levels = c("Urbanness: Big City", "Urbanness: Countryside", "Urbanness: Middlesized City", 
+                           levels = c("Male", "Age: 18 - 29", "Age: 30 - 39", "Age: 40 - 49",
+                                      "Age: 50 - 59", "Age: 60 - 74", "High Levels of Education",
+                                      "Low Levels of Education", "Medium Levels of Education",
+                                      "Urbanness: Big City", "Urbanness: Countryside", "Urbanness: Middlesized City", 
                                       "Urbanness: Rural Village", "Urbanness: Suburb",
                                       "Employment", "Income", "Living Place: Badem-Würtemberg",
                                       "Living Place: Bavaria", "Living Place: Berlin",

### 2021-12-08 src/analysis/data-for-analyses.R

@@ -1,5 +1,19 @@
 d <- d %>%
-  mutate(D4 = recode(D4, 
+  mutate(D1 = recode(D1, 
+                     `1` = "Female",
+                     `2` = "Male", .default = "NA"),
+         D2 = recode(D2, 
+                     `1` = "17 or younger",
+                     `2` = "18-29",
+                     `3` = "30-39",
+                     `4` = "40-49",
+                     `5` = "50-59",
+                     `6` = "60-74", .default = "NA"),
+         D3 = recode(D3, 
+                     `1` = "Low Levels of Education",
+                     `2` = "Medium Levels of Education",  
+                     `3` =  "High Levels of Education",.default = "NA"),
+         D4 = recode(D4, 
                      `1` = "Big City",
                      `2` = "Suburb",
                      `3` = "Middlesized City",
@@ -73,4 +87,4 @@ d <- d %>%
         POST_6 = POST_6 - 1,
         POST_8 = as_numeric(POST_8),
         POST_8 = POST_8 - 1,) %>%
-  select(id, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_8)
+  select(id, D1, D2, D3, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_8)

### 2021-12-08 src/analysis/explorative_analysis.R

@@ -26,7 +26,40 @@ pe1 <- exp1 %>%
   coord_flip()
 
 # Interaction with Age (pe2)
+df <- d %>%
+  mutate(a = D2)
+exp2 <- regression5(df, a, ethnic) 
 
+pe2 <- exp2 %>%
+  mutate(y = recode(y,
+                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow \n the will of the people",
+                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people"),
+         factor = recode(factor,
+                         `a30-39` = "Age: 30 - 39",
+                         `a40-49` = "Age: 40 - 49",
+                         `a50-59` = "Age: 50 - 59", 
+                         `a60-74` = "Age: 60 - 74")) %>%
+  ggplot(aes(x = factor, 
+             y = AME,
+             color = y,
+             fill = y,
+             ymin = lower,
+             ymax = upper)) +
+  geom_point(position = position_dodge(.5)) + 
+  geom_errorbar(position = position_dodge(.5), width = 0) +
+  theme_ipsum() +
+  labs(x = "", 
+       y = "Average Marginal Effects for Ethnic Conception of the People",
+       title = "Exploration: Age") +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5),
+        legend.position="none",
+        legend.title = element_blank()) +
+  scale_color_manual(values = fig_cols) +
+  scale_fill_manual(values = fig_cols) +
+  geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
+  coord_flip()
 
 #Interaction with Region
 df <- d %>%

### 2021-12-08 src/analysis/explorative_cfa.R

@@ -32,9 +32,20 @@ m_cfa <- tibble(
   `Civic Conception (6 Items)` = c(fitMeasures(cfa_civic6)[9], AIC(cfa_civic6), BIC(cfa_civic6),
                          fitMeasures(cfa_civic6)[23], fitMeasures(cfa_civic6)[26],
                          fitMeasures(cfa_civic6)[29]))
+
+cfa_e <- d %>%
+  filter(ethnic == 1) %>%
+  mutate(cfa_pa = as.numeric(predict(cfa_ethnic))) %>%
+  select(id, cfa_pa)
+
+cfa_df <- d %>%
+  filter(ethnic == 0) %>%
+  mutate(cfa_pa = as.numeric(predict(cfa_civic))) %>%
+  select(id, cfa_pa) %>%
+  add_case(cfa_e)
              
 cfa1 <- d %>%
-  mutate(cfa_pa = ifelse(ethnic == 1, predict(cfa_ethnic), predict(cfa_civic))) %>%
+  left_join(cfa_df, by = "id") %>%
   select(cfa_pa, ethnic) %>%
   mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
   group_by(ethnic) %>%
@@ -60,8 +71,8 @@ cfa1 <- d %>%
 
 
 cfa2 <- d %>%
-  mutate(cfa_pa = ifelse(ethnic == 1, predict(cfa_ethnic), predict(cfa_civic)),
-         ethnic = recode(ethnic,
+  left_join(cfa_df, by = "id")  %>%
+  mutate(ethnic = recode(ethnic,
                          `0` = "Civic Conception",
                          `1` = "Ethnic Conception"))  %>%
   ggplot(aes(x = cfa_pa, color = ethnic, fill = ethnic)) +
@@ -74,10 +85,6 @@ cfa2 <- d %>%
   theme(legend.position="none",
         legend.title = element_blank())
 
-tmp <- d %>%
-  mutate(cfa_pa = ifelse(ethnic == 1, predict(cfa_ethnic), predict(cfa_civic))) %>%
-  select(cfa_pa)
-
-d <- d %>%
-  add_column(tmp)
+d <- full_join(x = d, y = cfa_df, by = "id") %>%
+  distinct()
   

### 2021-12-08 src/analysis/predict-pop-vote-items.R

@@ -2,21 +2,42 @@ Ethnic <- c(0,1)
 
 for(i in 1:length(Ethnic)){
   df <- d %>%
-    dplyr::filter(ethnic == Ethnic[i]) %>%
+    filter(ethnic == Ethnic[i]) %>%
     mutate(pop_vote = ifelse(D6 == "AfD", 1,
                              ifelse(D6 == "Left", 1, 0)),
-           Linke_vote = ifelse(D6 == "Left", 1,0),
-           scale = POST_1)
+           Linke_vote = ifelse(D6 == "Left", 1,0)) %>%
+    rename(scale = POST_1) 
+  
   if(i==1){
-    exp <- regression7(df, scale) %>%
+    exp <- tidy(lm(pop_vote ~ scale + D8 + PT8, df)) %>%
       mutate(id = "POST_1",
-             ethnic = Ethnic[i])}
-  else{
-    tmp <- regression7(df, scale) %>%
+             ethnic = Ethnic[i],
+             y = "pop_vote") 
+    tmp <- tidy(lm(Afd_vote ~ scale + D8 + PT8, df)) %>%
       mutate(id = "POST_1",
-             ethnic = Ethnic[i])
-    exp <- exp %>%
-      add_case(tmp)}
+             ethnic = Ethnic[i],
+             y = "Afd_vote") 
+    exp <- exp %>% add_case(tmp)
+    tmp <- tidy(lm(Linke_vote ~ scale + D8 + PT8, df)) %>%
+      mutate(id = "POST_1",
+             ethnic = Ethnic[i],
+             y = "Linke_vote")
+    exp <- exp %>% add_case(tmp)}
+  else{
+    exp <- tidy(lm(pop_vote ~ scale + D8 + PT8, df)) %>%
+      mutate(id = "POST_1",
+             ethnic = Ethnic[i],
+             y = "pop_vote") 
+    tmp <- tidy(lm(Afd_vote ~ scale + D8 + PT8, df)) %>%
+      mutate(id = "POST_1",
+             ethnic = Ethnic[i],
+             y = "Afd_vote") 
+    exp <- exp %>% add_case(tmp)
+    tmp <- tidy(lm(Linke_vote ~ scale + D8 + PT8, df)) %>%
+      mutate(id = "POST_1",
+             ethnic = Ethnic[i],
+             y = "Linke_vote")
+    exp <- exp %>% add_case(tmp)}
 }
 
[…]

### 2021-12-08 src/analysis/predict-pop-vote-scales.R

@@ -1,22 +1,61 @@
+detach_package <- function(pkg, character.only = FALSE){
+  if(!character.only)
+  {
+    pkg <- deparse(substitute(pkg))
+  }
+  search_item <- paste("package", pkg, sep = ":")
+  while(search_item %in% search())
+  {
+    detach(search_item, unload = TRUE, character.only = TRUE)
+  }
+}
+packages <- c( "ltm", "GPArotation", "Hmisc", "mirt",
+               "lattice","lordif", "semPlot",
+               "semTools", "nFactors", "corrr")
+for(i in length(packages)){
+  detach_package(packages[i], TRUE)
+}
+
 Ethnic <- c(0,1) 
 
 for(i in 1:length(Ethnic)){
-df <- d %>%
-    dplyr::filter(ethnic == Ethnic[i]) %>%
+    df <- d %>%
+    filter(ethnic == Ethnic[i]) %>%
     mutate(pop_vote = ifelse(D6 == "AfD", 1,
                       ifelse(D6 == "Left", 1, 0)),
-           Linke_vote = ifelse(D6 == "Left", 1,0),
-           scale = cfa_pa)
+           Linke_vote = ifelse(D6 == "Left", 1,0)) %>%
+  rename(scale = cfa_pa) 
+
 if(i==1){
-  exp <- regression7(df, scale) %>%
+  exp <- tidy(lm(pop_vote ~ scale + D8 + PT8, df)) %>%
     mutate(id = "cfa_pa",
-           ethnic = Ethnic[i])}
+           ethnic = Ethnic[i],
+           y = "pop_vote") 
+  tmp <- tidy(lm(Afd_vote ~ scale + D8 + PT8, df)) %>%
+                 mutate(id = "cfa_pa",
+                        ethnic = Ethnic[i],
+                        y = "Afd_vote") 
+  exp <- exp %>% add_case(tmp)
+  tmp <- tidy(lm(Linke_vote ~ scale + D8 + PT8, df)) %>%
+               mutate(id = "cfa_pa",
+                      ethnic = Ethnic[i],
+                      y = "Linke_vote")
+  exp <- exp %>% add_case(tmp)}
 else{
-  tmp <- regression7(df, scale) %>%
+  exp <- tidy(lm(pop_vote ~ scale + D8 + PT8, df)) %>%
     mutate(id = "cfa_pa",
-           ethnic = Ethnic[i])
-  exp <- exp %>%
-    add_case(tmp)}
+           ethnic = Ethnic[i],
[…]

### 2021-12-08 src/analysis/wuttke-approach.R

@@ -1,26 +1,28 @@
 w_e <- d %>%
   filter(ethnic == 1) %>%
-  select(matches("POST_[12356]")) %>%
+  select(id, matches("POST_[12356]")) %>%
   rowwise() %>% 
-  mutate(scale = min(POST_1, POST_2, POST_3,
-                     POST_5, POST_6))
-w_e <- w_e$scale
+  mutate(wuttke_pa = min(POST_1, POST_2, POST_3,
+                     POST_5, POST_6)) %>%
+  select(id, wuttke_pa)
 
-w_c <- d %>%
+
+w_df <- d %>%
   filter(ethnic == 0) %>%
-  select(matches("POST_[12356]")) %>%
+  select(id, matches("POST_[12356]")) %>%
   rowwise() %>% 
-  mutate(scale = min(POST_1, POST_2, POST_3,
-                     POST_5, POST_6))
-w_c <- w_c$scale
+  mutate(wuttke_pa = min(POST_1, POST_2, POST_3,
+                     POST_5, POST_6)) %>%
+  select(id, wuttke_pa) %>%
+  add_case(w_e)
 
 wa1 <- d %>%
-  mutate(scale = ifelse(ethnic == 1, w_e, w_c)) %>%
-  select(scale, ethnic) %>%
+  left_join(w_df) %>%
+  select(wuttke_pa, ethnic) %>%
   mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
   group_by(ethnic) %>%
-  summarise(scale = list(scale)) %>%
-  spread(ethnic, scale) %>%
+  summarise(wuttke_pa = list(wuttke_pa)) %>%
+  spread(ethnic, wuttke_pa) %>%
   mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
          t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
          means_civic = t.test(unlist(`Civic Conception`))$estimate,
@@ -41,11 +43,11 @@ wa1 <- d %>%
 
 
 wa2 <- d %>%
-  mutate(scale = ifelse(ethnic == 1, w_e, w_c),
-         ethnic = recode(ethnic,
+  left_join(w_df) %>%
+  mutate(ethnic = recode(ethnic,
                          `0` = "Civic Conception",
[…]

### 2021-12-08 src/lib/functions.R

@@ -232,7 +232,7 @@ regression7 <- function(df, scale){
   
   depVarList <- df %>% dplyr::select(pop_vote, Afd_vote, Linke_vote)
   indepVarList <- df %>% dplyr::select(scale, D8, PT8)
-  allModels <- apply(depVarList,2,function(xl)lm(xl ~ scale + D8 + PT8,
+  allModels <- apply(depVarList,2,function(xl)lm(as.factor(xl) ~ scale + D8 + PT8,
                                                  data= indepVarList))
   depVarList <- df %>% dplyr::select(pop_vote, Afd_vote, Linke_vote) %>%
     colnames()

### 2021-12-08 src/analysis/analyses.Rmd
add analyses

@@
 # positive values: Ethnic conception < Civic conception
+
+kbl(df, booktabs =T, caption = "Ethnic Conception Hypothesis - T-Test") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "8cm") %>%
+  column_spec(2, width = "2cm")  %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "2cm") %>%
+  column_spec(5, width = "2cm") %>%
+  column_spec(6, width = "2cm")
 ```
@@
 p2a
+
+h2a <- h2a %>% 
+  mutate(y = recode(y,
+                    `POST_2` = "DV: People, not politicians, should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow the will of the \n people",
+                    `POST_4` = "DV: Differences between elites an the people are bigger than \n differences between the people")) %>%
+  select(y, AME:lower, a) %>%
+  rename(`Exclusive National Identity` = a)
+
+kbl(h2a, booktabs =T, caption = "National Identity Hypothesis - AME") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "8cm") %>%
+  column_spec(2, width = "2cm")  %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "2cm") %>%
+  column_spec(5, width = "2cm") 
 ```
@@
 p2b
+
+h2b <- h2b %>% 
+  mutate(y = recode(y,
+                    `POST_2` = "DV: People, not politicians, should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow the will of the \n people",
+                    `POST_4` = "DV: Differences between elites an the people are bigger than \n differences between the people"),
+         ethnic = recode(ethnic,
+                         `1` = "Ethnic Conception of the People",
+                         `0` = "Civic Conception")) %>%
+  select(y, AME:lower, treatment = ethnic)
+
+kbl(h2b, booktabs =T, caption = "Far Right Party ID - AME") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "8cm") %>%
+  column_spec(2, width = "2cm")  %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "2cm") %>%
+  column_spec(5, width = "2cm") 
 ```
@@
 
-## Alternative specifications + Interactions
-
 ```{r "explorative", fig.align="center", fig.height=15, fig.width=15}
@@
 
-pe3/ (pe4 + pe5) #add pe2 (age)
+exp1 <- exp1 %>%
+  mutate(y = recode(y,
+                    `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
+                    `POST_3` = "DV: MPs should follow \n the will of the people"))
+kbl(exp1, booktabs =T, caption = "Ethnic Conception Hypothesis - OLS Effect of Ethnic Conception of the People ") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "2cm") %>%
+  column_spec(2, width = "2cm")  %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "8cm")
+
+#(pe2 + pe3)/ (pe4 + pe5)
 ```
@@
 exp1
+
+exp <- exp %>%
+  dplyr::select(estimate, lower, upper, scale = id, treatment = ethnic, y)
+kbl(exp, booktabs =T, caption = "Explanatory Power: Scales Predicting Populist Vote - OLS Regression") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "2cm") %>%
+  column_spec(2, width = "2cm")  %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "4cm") %>%
+  column_spec(5, width = "4cm") %>%
+  column_spec(6, width = "4cm")
 ```
@@
 exp1
+
+exp <- exp %>%
+  dplyr::select(estimate, lower, upper, item = id, treatment = ethnic, y)
+kbl(exp, booktabs =T, caption = "Explanatory Power: Items Predicting Populist Vote - OLS Regression") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "2cm") %>%
+  column_spec(2, width = "2cm")  %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "4cm") %>%
+  column_spec(5, width = "4cm") %>%
+  column_spec(6, width = "4cm")
 ```
-
-## Save Data with Scales
-```{r "save data"}
-save(d, file = here("data/intermediate/cleaned_experiment_scales.RData"))
-```

### 2021-12-08 src/analysis/h1.R

@@ -1,4 +1,4 @@
-p1 <- d %>% 
+df <- d %>% 
   mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
   select(POST_2, POST_3, ethnic) %>%
   pivot_longer(cols = POST_2:POST_3) %>%
@@ -16,7 +16,9 @@ p1 <- d %>%
          name = recode(name,
                        `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
                        `POST_3` = "DV: MPs should follow \n the will of the people")) %>%
-  select(name, p_value, t_value, means_difference, lower, higher) %>%
+  select(name, p_value, t_value, means_difference, lower, higher) 
+
+p1 <- df %>%
   ggplot(aes(x = means_difference, 
              y = name,
              xmin = lower, 

### 2021-12-08 src/analysis/predict-pop-vote-items.R

@@ -208,7 +208,7 @@ for(i in 1:length(Ethnic)){
     exp <- exp %>% add_case(tmp)}
 }
 
-exp1 <- exp %>%
+exp <- exp %>%
   dplyr::mutate(lower = estimate - (1.96 * std.error),
                 upper = estimate + (1.96 * std.error),
                 y = dplyr::recode(y,
@@ -224,7 +224,9 @@ exp1 <- exp %>%
                 ethnic = dplyr::recode(ethnic,
                                        `1` = "Ethnic Conception",
                                        `0` = "Civic Conception")) %>%
-  filter(term == "scale") %>%
+  filter(term == "scale") 
+
+exp1 <- exp %>%
   ggplot(aes(x = y, 
              y = estimate,
              color = id,

### 2021-12-08 src/analysis/predict-pop-vote-scales.R

@@ -42,10 +42,11 @@ if(i==1){
                       y = "Linke_vote")
   exp <- exp %>% add_case(tmp)}
 else{
-  exp <- tidy(lm(pop_vote ~ scale + D8 + PT8, df)) %>%
+  tmp <- tidy(lm(pop_vote ~ scale + D8 + PT8, df)) %>%
     mutate(id = "cfa_pa",
            ethnic = Ethnic[i],
            y = "pop_vote") 
+  exp <- exp %>% add_case(tmp)
   tmp <- tidy(lm(Afd_vote ~ scale + D8 + PT8, df)) %>%
     mutate(id = "cfa_pa",
            ethnic = Ethnic[i],
@@ -184,7 +185,7 @@ else{
   exp <- exp %>% add_case(tmp)}
 }
 
-exp1 <- exp %>%
+exp <- exp %>%
   dplyr::mutate(lower = estimate - (1.96 * std.error),
          upper = estimate + (1.96 * std.error),
          y = dplyr::recode(y,
@@ -199,7 +200,9 @@ exp1 <- exp %>%
          ethnic = dplyr::recode(ethnic,
                                 `1` = "Ethnic Conception",
                                 `0` = "Civic Conception")) %>%
-  filter(term == "scale") %>%
+  filter(term == "scale") 
+
+exp1 <- exp %>%
   ggplot(aes(x = y, 
              y = estimate,
              color = id,

### 2021-12-08 src/analysis/wuttke-approach.R

@@ -1,25 +1,25 @@
 w_e <- d %>%
-  filter(ethnic == 1) %>%
-  select(id, matches("POST_[12356]")) %>%
+  dplyr::filter(ethnic == 1) %>%
+  dplyr::select(id, matches("POST_[12356]")) %>%
   rowwise() %>% 
-  mutate(wuttke_pa = min(POST_1, POST_2, POST_3,
+  dplyr::mutate(wuttke_pa = min(POST_1, POST_2, POST_3,
                      POST_5, POST_6)) %>%
-  select(id, wuttke_pa)
+  dplyr::select(id, wuttke_pa)
 
 
 w_df <- d %>%
-  filter(ethnic == 0) %>%
-  select(id, matches("POST_[12356]")) %>%
+  dplyr::filter(ethnic == 0) %>%
+  dplyr::select(id, matches("POST_[12356]")) %>%
   rowwise() %>% 
-  mutate(wuttke_pa = min(POST_1, POST_2, POST_3,
+  dplyr::mutate(wuttke_pa = min(POST_1, POST_2, POST_3,
                      POST_5, POST_6)) %>%
-  select(id, wuttke_pa) %>%
+  dplyr::select(id, wuttke_pa) %>%
   add_case(w_e)
 
 wa1 <- d %>%
   left_join(w_df) %>%
-  select(wuttke_pa, ethnic) %>%
-  mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
+  dplyr::select(wuttke_pa, ethnic) %>%
+  dplyr::mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
   group_by(ethnic) %>%
   summarise(wuttke_pa = list(wuttke_pa)) %>%
   spread(ethnic, wuttke_pa) %>%
@@ -44,7 +44,7 @@ wa1 <- d %>%
 
 wa2 <- d %>%
   left_join(w_df) %>%
-  mutate(ethnic = recode(ethnic,
+  dplyr::mutate(ethnic = recode(ethnic,
                          `0` = "Civic Conception",
                          `1` = "Ethnic Conception")) %>%
   ggplot(aes(x = wuttke_pa, color = ethnic, fill = ethnic)) +

### 2022-02-01 report/draft.Rmd
add analyses
add full flow

@@
 title: "The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
-thanks: "Replication files are available on the author's Github account (http://github.com/MarikenvdVelden/wording-experiment-populist-attitudes).
+thanks: "Replication files are available on the author's Github account (https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).
 **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: Maurits Meijers"
@@
 Populism puts 'the people' central in political decision-making. 
-It's central claim is that political power should reside with the people, as opposed to the elites [@canovan1999trust, @mudde2004].
-To study populist beliefs at the individual level, scholars recently developed the populist attitude scale [@akkerman2014, @hawkins2012, @castanho2020]. 
-Research on both the individual and the party level has found that populism is a diverse phenomenon, applicable to inclusive left-wing ideologies and exclusionary right-wing ideologies [@meijers2021, @vanhauwaert2018].
+Its central claim is that political power should reside with the people, as opposed to the elites [@canovan1999trust; @mudde2004].
+To study populist beliefs at the individual level, scholars recently developed the populist attitude scale [@akkerman2014; @hawkins2012; @castanho2020]. 
+Research on both the individual and the party level has found that populism is a diverse phenomenon, applicable to inclusive left-wing ideologies and exclusionary right-wing ideologies [@meijers2021; @vanhauwaert2018].
 Indeed, populism is thought to be a thin-centred ideology that is usually attached to 'full' ideologies, such as socialism or nationalism [@mudde2004]. 
-As a result, the concept of populism remains agnostic about who constitutes the people.
+As a result, the concept of populism remains agnostic about _who_ constitutes the people.
 
-In civic terms, we can think of the people as 'citizens' [e.g., @almond1963]. In ethnic terms, 'the people'can refer to a more cultural understanding of _folk_. 
+In civic terms, we can think of the people as 'citizens' [e.g., @almond1963]. 
+In ethnic terms, 'the people' can refer to a more cultural understanding of _folk_. 
 While in some  cultural contexts, there is no strong semantic difference between 'the people' and 'citizens' (e.g.
@@
 
-Scales of populist attitudes have mostly relied on ethnic conceptions of the people [@akkerman2014,@hawkins2012, @castanho2020, @vanhauwaert2020, @schulz2018]. 
+Scales of populist attitudes have mostly relied on ethnic conceptions of the people [@akkerman2014; @hawkins2012; @castanho2020; @vanhauwaert2020; @schulz2018]. 
 At the same time, populist attitude scales have often been inconsistent in juxtaposing the elites with 'the people' or with 'citizens'. 
@@
 
-This begs the question whether a civic or ethnic conception of the people matters for the measurement of populist attitudes. 
-On the (far) right, 'the people' is often construed in ethnic, cultural, or even racial terms. On the left, 'the people' is often conceived of in more civic or economic terms. 
-Ideally, however, populist attitude scale capture populist ideation across different ideological predispositions (see the critique of @castanho2020 of populist item scales including nativist items). 
-Using a wording experiment in Germany (`N=6,713`), we examine whether an ethnic or a civic conception of the people affects respondents' agreement with the two items of the populist attitude scale that directly juxtapose 'the people' with the elites.
+This begs the question whether a civic or ethnic conception of the people elicits differences in measurement of populist attitudes. 
+On the (far) right, 'the people' is often construed in ethnic, cultural, or even racial terms. 
+On the left, 'the people' is often conceived of in more civic or economic terms. 
+Ideally, however, populist attitude scale captures populist ideation across different ideological predispositions (see the critique of @castanho2020 of populist item scales including nativist items). 
+Using a wording experiment in Germany (`N=7,034`), we examine whether an ethnic or a civic conception of the people affects respondents' agreement with the two items of the populist attitude scale that directly juxtapose 'the people' with the elites.[^1]
 We further examine whether far right voters and respondents with a exclusive national identity respond differently to ethnic conceptions of the people.
-In addition, we examine whether the differences found affect the overall latent construct of populist attitudes (EXPAND/SPECIFY LATER).
+In addition, we examine whether the differences found affect the overall latent construct of populist attitudes (**EXPAND/SPECIFY LATER**).
 Given the more pronounced ethnic connotation with the concept of 'people' or _Volk_ in the German language, the German case is particularly suitable to tease out differences between ethnic and civic conceptions of the people in key populist attitude items.
 
-# Empirical Analysis
+[^1]: All analytical material for replication can be found in our online Research Compendium: https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md (anonymized for the review process).
+
+# Civic versus Ethnic Conception of "the People"
 To test whether an ethnic or civic framing of the people affects respondents' agreement with key populist items we conduct a wording experiment. 
-Wording experiments have been used in political science to assess how different question phrasing affects respondents' perceptions of concepts such as issue ownership [@walgrave2016], climate change [@schuldt2011], and party identity [@sanders2002].
-We rely on a nationally representative sample of German citizens over 18 years old (`N=6,713`). 
+Wording experiments have been used in political science to assess how different question phrasing affects respondents' perceptions of concepts, such as issue ownership [@walgrave2016], climate change [@schuldt2011], and party identity [@sanders2002].
+We rely on a nationally representative sample of German citizens over 18 years old (`N=7,034`). 
 The sample is from an online panel provided by the survey company Respondi -- for an overview of all variables in the study, as well as the descriptive information, see Online Appendix (OA pp.
@@
 Quotas for age, gender, and education were included to ensure the representativeness of the sample. 
-We have 3,348 respondents in the group that received the ethnic phrasing and 3,365 respondents in the group with the civic phrasing. 
-This large sample size allows us to detect also small effects of question wording differences.
+We have `3,507` respondents in the group that received the ethnic phrasing and `3,527` respondents in the group with the civic phrasing. 
+This large sample size allows us to detect also small effects of question wording differences.[^2]
+
+[^2]: A power analysis is conducted and reported on our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).
 
@@
 ```
-```{r results-h1, out.width = "70%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Results: H1"}
-knitr::include_graphics(here::here("report/figures", "h1-1.png"))
+```{r results-h1,out.width = "99%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Results: H1"}
+knitr::include_graphics(here::here("report/figures", "h1-extra-1.png"))
 ```
@@
 We randomize whether respondents received a ethnic framing (i.e., with reference to 'the people; or _das Volk_) or a civic framing (i.e., with reference to 'citizens', or _Bürger_). 
+A balance test, reported in our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md), demonstrates that the allocation of the treatment was fully random.
 The upper two items in Table \ref{tab:popatt} shows the differences in wording for the two items `POP1` and `POP2` in English and German. 
-All the other items were kept constant.[^1].
+All the other items were kept constant.[^3].
 
-[^1]:Our intention was to also vary the wording of the item `POP4`.
+[^3]:Our intention was to also vary the wording of the item `POP4`.
 Yet, due to an unfortunate translation error in Qualtrics, we cannot use the item `POP4` in our analysis.
@@
 
-Figure \ref{fig:results-h1} shows the results of a difference of means test for the two treatment groups (ethnic vs. civic wording) for both items -- Table A.5 in the OA shows the coefficients. 
-There is a statistically significant difference in respondent agreement with the ethnic and civic conception of the people. 
-When 'the people' is conceived as _das Volk_ respondents are more likely to agree with the item's statement compared to the civic wording of _Bürger_. 
+The left-hand panel of Figure \ref{fig:results-h1} shows the results of a difference of means test for the two treatment groups (ethnic vs.
+civic wording) for both items -- Table A.5 in the OA shows the coefficients.
+There is a statistically significant difference in respondent agreement with the ethnic and civic conception of the people for the item `POP2` (''the people, not politicians, should make the most important political decisions''), but not for `POP1` (''The politicians need to follow the will of the people'').
+The negative coefficient for `POP2` indicates that when 'the people' is conceived as _das Volk_ respondents are more likely to agree with the item's statement compared to the civic wording of _Bürger_.
 Yet, as the results show, the difference is small in substantive terms. 
+The right-hand panel of Figure \ref{fig:results-h1} indicates that the non-effect for `POP1` is driven by the fact that for younger age groups (younger than 50 years old) there is no difference for the civic and ethnic conception of the people, as indicated by the blue dots and whiskers in Figure \ref{fig:results-h1}.[^4]
+For the older population (50 years old and more), the right-hand panel of Figure \ref{fig:results-h1} demonstrates using an OLS regression, including an interaction between treatment and age groups, that for both `POP1` and `POP2`, people receiving the ethnic treatment report higher levels of agreement with the items compared to people receiving the civic treatment.
+The effect size is still small in substantive terms: between a 0.1 and 0.3 increase on a 5-point scale.
+
+[^4]: Our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md) demonstrates that there are no other socio-demographic variables that mediate the effect.
 
 How does the effect of an ethnic conception of the people vis-à-vis a civic conception vary across respondents? 
-The left-hand panel of Figure \ref{fig:results-h2} shows the results of an OLS regression analysis[^2] with the an interaction between the treatment and a variable measuring whether or not the respondent voted for the far right party _Alternative für Deutschland_ -- for more details see Table A.6 in the OA).
+The left-hand panel of Figure \ref{fig:results-h2} shows the results of an OLS regression analysis[^5] with the an interaction between the treatment and a variable measuring whether or not the respondent voted for the far right party _Alternative für Deutschland_ -- for more details see Table A.6 in the OA).
 We see that far right voters show much more agreement to items `POP1` and `POP2` when it is phrased in an ethnic way. 
@@
 
-[^2]: As specified in the Pre-Analysis Plan, we only include unbalanced covariates.
+[^5]: As specified in the Pre-Analysis Plan, we only include unbalanced covariates.
 OA p.
@@
 So how does an ethnic and civic framing of the items `POP1` and `POP2` affect the latent construct of populism? 
-A graded Item Response Theory (IRT) analysis [see also @vanhauwaert2020] moreover shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see Figure XX and XX in the Appendix).
+A graded Item Response Theory (IRT) analysis [see also @vanhauwaert2020] moreover shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see **Figure XX** and **XX** in the Appendix).
 Overall, however, the overall level of information yielded by the two latent constructs of populism are similar. 

### 2022-02-01 report/figures/table_descriptives.tex
add full flow

--- 2021-11-16 report/figures/table_descriptives.tex
@@
    <td style="text-align:right;"> 6.9 </td>
-   <td style="text-align:right;"> 2.64 </td>
+   <td style="text-align:right;"> 2.54 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:right;"> 3.6 </td>
-   <td style="text-align:right;"> 0.90 </td>
+   <td style="text-align:right;"> 0.89 </td>
    <td style="text-align:right;"> 1 </td>
@@
    <td style="text-align:right;"> 3.3 </td>
-   <td style="text-align:right;"> 1.18 </td>
+   <td style="text-align:right;"> 1.19 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:right;"> 3.8 </td>
-   <td style="text-align:right;"> 0.98 </td>
+   <td style="text-align:right;"> 1.00 </td>
    <td style="text-align:right;"> 0 </td>
@@
   <tr>
-   <td style="text-align:left;"> DV: Differences between elites and 
+   <td style="text-align:left;"> Differences between elites and 
  the people are bigger than 
@@
    <td style="text-align:right;"> 3.5 </td>
-   <td style="text-align:right;"> 1.00 </td>
+   <td style="text-align:right;"> 1.03 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
+   <td style="text-align:left;"> Too much talk, no action </td>
+   <td style="text-align:right;"> 4.0 </td>
+   <td style="text-align:right;"> 1.01 </td>
+   <td style="text-align:right;"> 0 </td>
+   <td style="text-align:right;"> 5 </td>
+  </tr>
+  <tr>
+   <td style="text-align:left;"> Compromise is selling out </td>
+   <td style="text-align:right;"> 3.2 </td>
+   <td style="text-align:right;"> 1.15 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:right;"> 4.2 </td>
-   <td style="text-align:right;"> 0.83 </td>
+   <td style="text-align:right;"> 0.87 </td>
    <td style="text-align:right;"> 0 </td>
@@
    <td style="text-align:right;"> 2.9 </td>
-   <td style="text-align:right;"> 1.10 </td>
+   <td style="text-align:right;"> 1.09 </td>
    <td style="text-align:right;"> 1 </td>

### 2022-02-01 src/analysis/analyses.Rmd
add full flow

@@
 d %>%
-  select(POST_2, POST_3, POST_4, ethnic) %>%
-  pivot_longer(cols = POST_2:POST_4,
+  select(POST_2, POST_3, ethnic) %>%
+  pivot_longer(cols = POST_2:POST_3,
                names_to = "dvs") %>%
@@
                       `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
-                       `POST_3` = "DV: MPs should follow \n the will of the people",
-                       `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people"),
+                       `POST_3` = "DV: MPs should follow \n the will of the people"),
          ethnic = if_else(ethnic==0, "Civic Conception", "Ethnic Conception")) %>%
@@
 
+```{r "h1-extra", fig.align="center", fig.height=6, fig.width=12, echo = FALSE, fig.show = "hide"}
+p1 + pe2 + 
+  plot_layout(widths = c(1, 1.25))
+```
+
 ## Scaling fit

### 2022-02-01 src/data-processing/prep_data.Rmd
add full flow

@@
 source(here("src/data-processing/clean_data.R"))
-
-dem <- read_delim(here("data/raw-private/14651 data matched final.csv"), 
-                  delim = ";") %>%
-  select(id = tic, D2 = age, D1 = gender, D3 = education)
-
-d <- left_join(d, dem)
-rm(dem)
 ```

### 2022-02-01 src/analysis/balance-test.R

@@ -1,13 +1,6 @@
 covs <- d %>%
   select(ethnic, D1:D4, D7:PT8) %>%
-  filter(D1 != "NA",
-         D2 != "NA",
-         D3 != "NA",
-         D4 != "NA",
-         D7 != "NA",
-         D8 != "NA",
-         D9 != "NA",
-         D10 != "NA")
+  filter(ethnic != "NA")
 
 balanced <-bal.tab(ethnic ~ factor(D1) +  factor(D2) + factor(D3) + 
                      factor(D4) + D7 + D8 + factor(D9) +

### 2022-02-01 src/analysis/data-for-analyses.R

@@ -87,4 +87,12 @@ d <- d %>%
         POST_6 = POST_6 - 1,
         POST_8 = as_numeric(POST_8),
         POST_8 = POST_8 - 1,) %>%
-  select(id, D1, D2, D3, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_8)
+  select(id, D1, D2, D3, D4:D10, pol_know, PT7:PT8, HT4, Afd_vote, ethnic, POST_1:POST_8) %>%
+  mutate(D1 = if_else(D1 == "NA", median(D1, na.rm = T), D1),
+         D3 = if_else(D3 == "NA", median(D3, na.rm = T), D3),
+         D4 = if_else(D4 == "NA", median(D4, na.rm = T), D4),
+         D7 = if_else(is.na(D7), round(mean(D7, na.rm = T),0), D7),
+         D8 = if_else(is.na(D8), round(mean(D8, na.rm = T),0), D8),
+         D9 = if_else(D9 == "NA", median(D9, na.rm = T), D9),
+         D10 = if_else(D10 == "NA", median(D10, na.rm = T), D10)) %>%
+  drop_na(ethnic)

### 2022-02-01 src/analysis/explorative_analysis.R

@@ -1,12 +1,20 @@
 # Alternative specification
 df <- d 
-exp1 <- regression4(df, ethnic) 
+exp1 <- tidy(lm(POST_2 ~ ethnic + PT7 + D8, df))
+exp1 <- exp1 %>%
+  add_case(
+    tidy(lm(POST_3 ~ ethnic + PT7 + D8, df))
+  ) %>%
+  filter(term == "ethnic") %>%
+  mutate(y = c("POST_2", "POST_3"),
+         lower = estimate - (1.65 * std.error),
+         upper = estimate + (1.65 * std.error)) %>%
+  select(estimate, upper, lower, y)
 
 pe1 <- exp1 %>%
   mutate(y = recode(y,
                     `POST_2` = "DV: People, not politicians, \n should make the most \n important political decisions",
-                    `POST_3` = "DV: MPs should follow \n the will of the people",
-                    `POST_4` = "DV: Differences between elites and \n the people are bigger than \n differences between the people")) %>%
+                    `POST_3` = "DV: MPs should follow \n the will of the people")) %>%
   ggplot(aes(x = y, 
              y = estimate,
              color = y,
@@ -15,12 +23,9 @@ pe1 <- exp1 %>%
   geom_point(position = position_dodge(.5)) + 
   geom_errorbar(position = position_dodge(.5), width = 0) +
   theme_ipsum() +
+  theme(legend.position="none") +
   labs(x = "", y = "Effect of Ethnic Conception of the People",
        title = "Alternative Specification: Ethnic Conception hypothesis") +
-  theme(plot.title = element_text(hjust = 0.5),
-        plot.subtitle = element_text(hjust = 0.5),
-        legend.position="none",
-        legend.title = element_blank()) +
   scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
   coord_flip()
@@ -51,10 +56,10 @@ pe2 <- exp2 %>%
   theme_ipsum() +
   labs(x = "", 
        y = "Average Marginal Effects for Ethnic Conception of the People",
-       title = "Exploration: Age") +
+       title = "") +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5),
-        legend.position="none",
+        legend.position="right",
         legend.title = element_blank()) +
   scale_color_manual(values = fig_cols) +
[…]

### 2022-02-01 src/analysis/h1.R

@@ -24,13 +24,13 @@ p1 <- df %>%
              xmin = lower, 
              xmax = higher,
              color = name)) +
-  geom_point() + 
-  geom_errorbar(width = 0) +
+  geom_point(color = fig_cols[1]) + 
+  geom_errorbar(width = 0, color = fig_cols[1]) +
   theme_ipsum() +
   labs(y="", x= "Means Differences Test \n t statistic") +
   theme(plot.title = element_text(hjust = 0.5),
         legend.position="none") +
-  scale_color_manual(values = fig_cols) +
+  #scale_color_manual(values = fig_cols) +
   geom_vline(xintercept = 0.0, linetype = "dashed", size = .5, color = "gray80")
   
   

### 2022-02-01 src/analysis/h2a.R

@@ -13,8 +13,8 @@ p2a <- h2a %>%
              fill = y,
              ymin = lower,
              ymax = upper)) +
-  geom_line() + 
-  geom_ribbon(alpha = .2) +
+  geom_line(color = fig_cols[1]) + 
+  geom_ribbon(alpha = .2, fill = fig_cols[1], color = fig_cols[1]) +
   #geom_errorbar(position = position_dodge(.5), width = 0) +
   theme_ipsum() +
   labs(x = "Exclusive National Identity \n (1 = Low, 5 = High)", 
@@ -24,6 +24,6 @@ p2a <- h2a %>%
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",
         legend.title = element_blank()) +
-  scale_color_manual(values = fig_cols) +
-  scale_fill_manual(values = fig_cols) +
+  #scale_color_manual(values = fig_cols) +
+  #scale_fill_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed")

### 2022-02-01 src/analysis/h2b.R

@@ -16,8 +16,8 @@ p2b <- h2b %>%
              color = y,
              ymin = lower,
              ymax = upper)) +
-  geom_point(position = position_dodge(.5)) + 
-  geom_errorbar(position = position_dodge(.5), width = 0) +
+  geom_point(position = position_dodge(.5), color = fig_cols[1]) + 
+  geom_errorbar(position = position_dodge(.5), width = 0, color = fig_cols[1]) +
   theme_ipsum() +
   labs(x = "", y = "Average Marginal Effects of Voting for a Far Right Party") +
   facet_grid(.~ethnic) +
@@ -25,7 +25,7 @@ p2b <- h2b %>%
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",
         legend.title = element_blank()) +
-  scale_color_manual(values = fig_cols) +
+  #scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
   coord_flip()
 
@@ -43,8 +43,8 @@ p2c <- h2b %>%
              color = y,
              ymin = lower,
              ymax = upper)) +
-  geom_point(position = position_dodge(.5)) + 
-  geom_errorbar(position = position_dodge(.5), width = 0) +
+  geom_point(position = position_dodge(.5),color = fig_cols[1]) + 
+  geom_errorbar(position = position_dodge(.5), width = 0, color = fig_cols[1]) +
   theme_ipsum() +
   labs(x = "", y = "Average Marginal Effects of Voting for a Far Right Party \n for Ethnic Conception of the People") +
   #facet_grid(.~ethnic) +
@@ -52,6 +52,6 @@ p2c <- h2b %>%
         plot.subtitle = element_text(hjust = 0.5),
         legend.position="none",
         legend.title = element_blank()) +
-  scale_color_manual(values = fig_cols) +
+  #scale_color_manual(values = fig_cols) +
   geom_hline(yintercept = 0, size = .2, linetype = "dashed") +
   coord_flip()

### 2022-02-01 src/data-processing/clean_data.R

@@ -9,8 +9,8 @@ dem <- d %>%
   select(matches("D\\d"), id = tic) %>%
   select(-matches("D6_7_TEXT")) %>%
   select(id, D4:D10) %>%
-  drop_na()
-
+  mutate(D9 = if_else(is.na(D9), round(mean(D9, na.rm = T),0), D9),
+         D10 = if_else(is.na(D10), round(mean(D10, na.rm = T),0), D10))
 
 pret <- d %>%
   filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
@@ -20,8 +20,10 @@ pret <- d %>%
   select(matches("PT\\d"), matches("HT4_\\d+"), id = tic) %>%
   select(-matches("PT8_NPS_GROUP"), -matches("PT[13]"), -matches("PT[13]_\\d+")) %>%
   select(id, PT4, PT5 = PT5_1, PT6:HT4_4) %>%
-  drop_na()
-
+  mutate(HT4_1 = if_else(is.na(HT4_1), round(mean(HT4_1, na.rm = T),0), HT4_1),
+         HT4_2 = if_else(is.na(HT4_2), round(mean(HT4_2, na.rm = T),0), HT4_2),
+         HT4_3 = if_else(is.na(HT4_3), round(mean(HT4_3, na.rm = T),0), HT4_3),
+         HT4_4 = if_else(is.na(HT4_4), round(mean(HT4_4, na.rm = T),0), HT4_4))
 
 
 treat <- d %>%
@@ -31,7 +33,6 @@ treat <- d %>%
          tic != "f6b4160f5ab5dee05b7e925d50e5414") %>%
   select(id = tic, populism) %>%
   drop_na()
-
 
 post <- d %>%
   filter(Consent == 4, AC2_1 ==1, AC2_4 == 1,
@@ -45,12 +46,21 @@ post <- d %>%
   unite(POST_4, matches("POST1[ab]_4"), na.rm = TRUE) %>%
   unite(POST_5, matches("POST1[ab]_5"), na.rm = TRUE) %>%
   unite(POST_6, matches("POST1[ab]_6"), na.rm = TRUE) %>%
-  unite(POST_8, matches("POST1[ab]_8"), na.rm = TRUE) %>%
-  drop_na()
+  unite(POST_8, matches("POST1[ab]_8"), na.rm = TRUE) 
 
 d <- left_join(dem, pret, by = "id")
 d <- left_join(d, treat, by = "id")
[…]

### 2022-02-01 src/lib/functions.R

@@ -29,8 +29,9 @@ render_j2 = function(template, output, data, auto_unbox=TRUE, na="string") {
 regression <- function(df, a, ethnic){
   
   depVarList <- df %>% select(matches("POST_[23]"))
-  indepVarList <- df %>% select(a, ethnic, D8) 
-  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
+  indepVarList <- df %>% select(a, ethnic, PT7, D8) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + 
+                                                   PT7 + D8,
                                                  data= indepVarList))
   depVarList <- df %>% select(matches("POST_[23]")) %>% colnames()
   
@@ -38,15 +39,15 @@ regression <- function(df, a, ethnic){
     if(i==1){
       m <- summary(margins(allModels[[i]], variables = "a", at = list(ethnic = 0:1))) %>%
         mutate(y = depVarList[i],
-               lower = AME - (1.56 * SE),
-               upper = AME + (1.56 * SE)) %>%
+               lower = AME - (1.65 * SE),
+               upper = AME + (1.65 * SE)) %>%
         select(AME, upper, lower, y, ethnic)
     }
     else{
       tmp <- summary(margins(allModels[[i]], variables = "a", at = list(ethnic = 0:1))) %>%
         mutate(y = depVarList[i],
-               lower = AME - (1.56 * SE),
-               upper = AME + (1.56 * SE)) %>%
+               lower = AME - (1.65 * SE),
+               upper = AME + (1.65 * SE)) %>%
         select(AME, upper, lower, y, ethnic)
       m <- m %>%
         add_case(tmp)
@@ -59,8 +60,9 @@ regression <- function(df, a, ethnic){
 regression2 <- function(df, a, ethnic){
   
   depVarList <- df %>% select(matches("POST_[23]"))
-  indepVarList <- df %>% select(a, ethnic, D8) 
-  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + D8,
+  indepVarList <- df %>% select(a, ethnic, D8, PT7) 
+  allModels <- apply(depVarList,2,function(xl)lm(xl ~ a * ethnic + 
+                                                   PT7 + D8,
                                                  data= indepVarList))
   depVarList <- df %>% select(matches("POST_[23]")) %>% colnames()
   
@@ -68,15 +70,15 @@ regression2 <- function(df, a, ethnic){
[…]

### 2022-02-01 report/draft.Rmd
add full flow

@@
 OA p.
-A-7 demonstrates the balance checks, demonstrating that only income is unbalanced, and therefore included as a covariate.
+A-7 demonstrates the balance checks, demonstrating that only political interest and income are unbalanced, and therefore included as a covariate.
 
@@
 Overall, however, the overall level of information yielded by the two latent constructs of populism are similar. 
-This is not surprising, given that we varied the wording of `the people' only in two items of the full \@akkerman2014 item battery.
+This is not surprising, given that we varied the wording of `the people' only in two items of the full @akkerman2014 item battery. 
+Therefore, also overall difference between a latent construct of populism with two ethnically framed items and a latent construct with two civically framed items is small.
 
-Therefore, also overall difference between a latent construct of populism with two ethnically framed items and a latent construct with two civically framed items is small.
 We find no statistically significant difference between the two constructs estimated using Confirmatory Factor Analysis (see Table A.9 in the OA).
@@
 Interestingly, however, both the 'ethnic' and the 'civic' scale show a satisfactory model fit (`CFI > 0.9`; `RMSEA < 0.08`; and `SRMR < 0.02`) -- for more information see OA Table A.8.
+Yet, when looking at the additive scale (see Table **XX** in the OA), we see that the scale using the civic conception of the people has a statistically higher mean value compared to the ethnic conception.
+The same holds for constructing a scale using the approach of @wuttke2020whole -- i.e. using the lowest value on one of the items that construe the latent construct.
 
@@
 An ethnic conception of the people, overall, yielded more agreement with the items in question. 
-This is effect is particularly pronounced for voters of the far right. 
+This is effect is particularly pronounced for voters of the far right, as well as for older voters. 
 The difference between an ethnic and a civic conception of the people was also only significant for respondents who adhered a moderate to high level of exclusive national identity. 

### 2022-03-06 report/draft.Rmd
testing measurement invariance

@@
 options(kableExtra.latex.load_packages = FALSE)
+options(scipen = 1, digits = 2)
 
@@
 
-This begs the question whether a civic or ethnic conception of the people elicits differences in measurement of populist attitudes. 
-On the (far) right, 'the people' is often construed in ethnic, cultural, or even racial terms. 
-On the left, 'the people' is often conceived of in more civic or economic terms. 
-Ideally, however, populist attitude scale captures populist ideation across different ideological predispositions (see the critique of @castanho2020 of populist item scales including nativist items). 
-Using a wording experiment in Germany (`N=7,034`), we examine whether an ethnic or a civic conception of the people affects respondents' agreement with the two items of the populist attitude scale that directly juxtapose 'the people' with the elites.[^1]
-We further examine whether far right voters and respondents with a exclusive national identity respond differently to ethnic conceptions of the people.
-In addition, we examine whether the differences found affect the overall latent construct of populist attitudes (**EXPAND/SPECIFY LATER**).
+The assumption is that the different conceptions of the people (i.e. civic or ethnic) functions similar -- also known as measurement invariance or measurement equivalence.[^1]
+In this paper, we test the degree to which the populist attitude scale is invariant across civic and ethnic concpetions of the people: 
+That is, do people exposed to a civic conception of the people have a similar populist attitude score as people exposed to an ethnic one.
+While ideally opulist attitude scale captures populist ideation across different ideological predispositions (see the critique of @castanho2020 of populist item scales including nativist items), 'the people' is often construed in ethnic, cultural, or even racial terms on the (far) right and conceived of in more civic or economic terms on the (far) left.
+Using a wording experiment in Germany (`N=7,034`), we examine measurement invariance in multiple ways.
+First, we study whether an ethnic or a civic conception of the people affects respondents' agreement with the two items of the populist attitude scale that directly juxtapose 'the people' with the elites -- i.e.
+assessing structural, metric, or weak invariance [@hirschfeld2014improving].[^2]
+We further examine this structural invariance, by testing whether far right voters and respondents with a exclusive national identity respond differently to ethnic conceptions of the people. 
+In addition, we examine whether the differences found affect the overall latent construct of populist attitudes, looking whether the intercept and the error terms are invariant (i.e.
+scalar and strict invariance) [@hirschfeld2014improving].
 Given the more pronounced ethnic connotation with the concept of 'people' or _Volk_ in the German language, the German case is particularly suitable to tease out differences between ethnic and civic conceptions of the people in key populist attitude items.
 
-[^1]: All analytical material for replication can be found in our online Research Compendium: https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md (anonymized for the review process).
+[^1]: A scale is measurement invariant across groups if subjects with identical levels of the latent construct have the same expected raw-score on the measure [@drasgow1985equivalence].
+[^2]: All analytical material for replication can be found in our online Research Compendium: https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md (anonymized for the review process).
 
@@
 We have `3,507` respondents in the group that received the ethnic phrasing and `3,527` respondents in the group with the civic phrasing. 
-This large sample size allows us to detect also small effects of question wording differences.[^2]
+This large sample size allows us to detect also small effects of question wording differences.[^3]
 
-[^2]: A power analysis is conducted and reported on our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).
+[^3]: A power analysis is conducted and reported on our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).
 
 ```{r dv, topcaption=TRUE}
-library(tidyverse) 
-library(kableExtra)
+source(here::here("src/lib/functions.R"))
 df <- tibble(Variable = c("POP1","POP2","POP3",
@@
 ```
-```{r results-h1,out.width = "99%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Results: H1"}
-knitr::include_graphics(here::here("report/figures", "h1-extra-1.png"))
+```{r results-h1,out.width = "99%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Differences in Ethnic and Civic Conceptions of the People"}
+knitr::include_graphics(here("report/figures", "h1-extra-1.png"))
 ```
@@
 The upper two items in Table \ref{tab:popatt} shows the differences in wording for the two items `POP1` and `POP2` in English and German. 
-All the other items were kept constant.[^3].
+All the other items were kept constant.[^4].
 
-[^3]:Our intention was to also vary the wording of the item `POP4`.
+[^4]:Our intention was to also vary the wording of the item `POP4`.
 Yet, due to an unfortunate translation error in Qualtrics, we cannot use the item `POP4` in our analysis.
@@
 Yet, as the results show, the difference is small in substantive terms. 
-The right-hand panel of Figure \ref{fig:results-h1} indicates that the non-effect for `POP1` is driven by the fact that for younger age groups (younger than 50 years old) there is no difference for the civic and ethnic conception of the people, as indicated by the blue dots and whiskers in Figure \ref{fig:results-h1}.[^4]
+The right-hand panel of Figure \ref{fig:results-h1} indicates that the non-effect for `POP1` is driven by the fact that for younger age groups (younger than 50 years old) there is no difference for the civic and ethnic conception of the people, as indicated by the blue dots and whiskers in Figure \ref{fig:results-h1}.[^5]
 For the older population (50 years old and more), the right-hand panel of Figure \ref{fig:results-h1} demonstrates using an OLS regression, including an interaction between treatment and age groups, that for both `POP1` and `POP2`, people receiving the ethnic treatment report higher levels of agreement with the items compared to people receiving the civic treatment.
@@
 
-[^4]: Our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md) demonstrates that there are no other socio-demographic variables that mediate the effect.
+[^5]: Our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md) demonstrates that there are no other socio-demographic variables that mediate the effect.
 
 How does the effect of an ethnic conception of the people vis-à-vis a civic conception vary across respondents? 
-The left-hand panel of Figure \ref{fig:results-h2} shows the results of an OLS regression analysis[^5] with the an interaction between the treatment and a variable measuring whether or not the respondent voted for the far right party _Alternative für Deutschland_ -- for more details see Table A.6 in the OA).
+The left-hand panel of Figure \ref{fig:results-h2} shows the results of an OLS regression analysis[^6] with the an interaction between the treatment and a variable measuring whether or not the respondent voted for the far right party _Alternative für Deutschland_ -- for more details see Table A.6 in the OA).
 We see that far right voters show much more agreement to items `POP1` and `POP2` when it is phrased in an ethnic way. 
@@
 
-[^5]: As specified in the Pre-Analysis Plan, we only include unbalanced covariates.
+[^6]: As specified in the Pre-Analysis Plan, we only include unbalanced covariates.
 OA p.
 A-7 demonstrates the balance checks, demonstrating that only political interest and income are unbalanced, and therefore included as a covariate.
+
+```{r results-h2, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-h2}Average Marginal Effects for Ethnic Conception of the People"}
+knitr::include_graphics(here("report/figures", "h2-1.png"))
+```
 
@@
 `>2.5` on the exclusive national identity scale).
-Both the analyses from the left and right-hand panel of \ref{fig:results-h2} suggest that far right voters and respondents with an exclusive national identity interpret `the people' (_das Volk_) in an ethno-cultural way.
+Both the analyses from the left and right-hand panel of \ref{fig:results-h2} suggest that far right voters and respondents with an exclusive national identity interpret 'the people' (_das Volk_) in an ethno-cultural way.
+The results of Figures \ref{fig:results-h1} and \ref{fig:results-h2} seem to suggest that the assumption of measurement invariance is not met, as we find statistically significant difference for the `POP2` (''the people, not politicians, should make the most important political decisions'') item.
 
-So how does an ethnic and civic framing of the items `POP1` and `POP2` affect the latent construct of populism? 
-A graded Item Response Theory (IRT) analysis [see also @vanhauwaert2020] moreover shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see **Figure XX** and **XX** in the Appendix).
-Overall, however, the overall level of information yielded by the two latent constructs of populism are similar. 
-This is not surprising, given that we varied the wording of `the people' only in two items of the full @akkerman2014 item battery. 
-Therefore, also overall difference between a latent construct of populism with two ethnically framed items and a latent construct with two civically framed items is small.
-
-We find no statistically significant difference between the two constructs estimated using Confirmatory Factor Analysis (see Table A.9 in the OA).
+Does an ethnic and civic framing of the items `POP1` and `POP2` affect the measurement invariance assumption of the latent construct of populist attitudes? 
+We first test the measurement variance in a Confirmatory Factor Analysis (see Table A.9 in the OA). 
+The averages of the civic and ethnic conception scales of populist attitudes differ significantly:
+Respondents exposed to the civic conception score higher (`0.44` on a 5-point scale) on the populist attitudes scales than respondents in the ethnic conception condition. 
 In terms of model fit, both constructs show very similar goodness-of-fit statistics (i.e., CFI, BIC, RMSEA, and SRMR).
 Interestingly, however, both the 'ethnic' and the 'civic' scale show a satisfactory model fit (`CFI > 0.9`; `RMSEA < 0.08`; and `SRMR < 0.02`) -- for more information see OA Table A.8.
-Yet, when looking at the additive scale (see Table **XX** in the OA), we see that the scale using the civic conception of the people has a statistically higher mean value compared to the ethnic conception.
-The same holds for constructing a scale using the approach of @wuttke2020whole -- i.e. using the lowest value on one of the items that construe the latent construct.
+Moreover, when testing metric and scalar invariance -- i.e.
+is the magnitude of loadings similar accross groups or are the magnitude of loadings and the intercept difference accross groups -- we find statistical significant Chi-square differences for the metric invariance and scalar invariance models, shown in Table \ref{tab:mi-cfa}.
+This indicates that the assumption that the different conceptions of the people function similar is not met.
 
-```{r results-h2, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-h2}Results: H2"}
-knitr::include_graphics(here::here("report/figures", "h2-1.png"))
-```
-
-```{r "scale", fig.align="center", fig.height=8, fig.width=8, eval = FALSE}
-source(here::here("src/lib/functions.R"))
+```{r mi-cfa, topcaption=TRUE}
 load(here("data/intermediate/cleaned_experiment.RData"))
@@
 
-kbl(m_cfa, booktabs =T, caption = "\\label{tab:CFA}Confirmatory Factor Analysis - Fit Statistics") %>%
+mi %>%
+  select(Models, AIC, BIC, `Chisq diff`, `Pr(>Chisq)`) %>%
+  kbl(booktabs =T, caption = "\\label{tab:mi-cfa}Measurement Invariance - CFA Models") %>%
   kable_styling(latex_options = c("striped", "hold_position"),
@@
   column_spec(1, width = "4cm") %>%
-  column_spec(2, width = "4cm")  %>%
-  column_spec(2, width = "4cm") %>%
-  column_spec(2, width = "4cm") 
+  column_spec(2, width = "2cm") %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "2cm") %>%
+  column_spec(5, width = "2cm")   
 ```
+
+Additionally, we have estimated a graded Item Response Theory (IRT) analysis [see also @vanhauwaert2020].
+This scaling model shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see **Figure XX** and **XX** in the Appendix).
+While the means of the scales with the different conceptions of the people are not different, testing configural, metric and scalar invariance -- see Table \ref{tab:mi-irt} -- we see that the equal slope assumption (metric invariance) as well as one form of scalar invariance (i.e.
+the one with free means) are not met.
+This indicates that even varying the wording of ‘the people’ in two items of the full @akkerman2014 item battery is enough to demonstrate that the scales are not equivalent anymore.
+
+```{r "irt-code", fig.align="center", fig.height=8, fig.width=12, echo=FALSE, message=FALSE, warning=FALSE,results = 'hide'}
+# Measurement Invariance
+library(mirt)
+dat <- matrix(data = NA, nrow = dim(d)[1], ncol = 5)
+dat[,1] <- d$POST_1
+dat[,2] <- d$POST_2
+dat[,3] <- d$POST_3
+dat[,4] <- d$POST_5
+dat[,5] <- d$POST_6
+colnames(dat) <- c("item1", "item2", "item3", "item4", "item5")
+group <- d$ethnic
+group <- if_else(group==0, "C1", "E1")
+
+mod_configural <- multipleGroup(dat, 1, group = group)
+mod_metric <- multipleGroup(dat, 1, group = group, invariance=c('slopes')) #equal slopes
+mod_scalar2 <- multipleGroup(dat, 1, group = group, #equal intercepts, free variance and means
+                             invariance=c('slopes', 'intercepts', 'free_var','free_means'))
+mod_scalar1 <- multipleGroup(dat, 1, group = group, #fixed means
+                             invariance=c('slopes', 'intercepts', 'free_var'))
+
+a1 <- anova(mod_metric, mod_configural) #equal slopes only
+a2 <- anova(mod_scalar2, mod_metric) #equal intercepts, free variance and mean
+a3 <- anova(mod_scalar1, mod_scalar2) #fix mean
+
+dat <- a1[2,] %>% 
+  add_case(a2[2,]) %>% 
+  add_case(a3[2,]) %>% 
+  mutate(`Equivalence Tests` = c("Equal Slopes",
+             "Equal Slopes, Intercepts, Free Variance and Mean", 
+             "Equal Slopes, Intercepts, Free Variance and Fixed Mean")) %>% 
+  dplyr::select(`Equivalence Tests`, AIC, BIC, `LogLikelihood` = logLik, `Significant Difference` = p)
+```
+```{r "irr-code2"}
+dat %>%
+  kbl(booktabs =T, caption = "\\label{tab:mi-irt}Measurement Invariance - IRT Models") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "5cm") %>%
+  column_spec(2, width = "2cm") %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "2cm") %>%
+  column_spec(5, width = "3cm") 
+```
+
+Moreover, we have created an additive scale (see Table **XX** in the OA), as well as constructed a scale using the approach of @wuttke2020whole -- i.e.
+using the lowest value on one of the items that construe the latent construct.
+For both scales, we find statistical significant average values for the scales based on ethnic and civic conception of the people.
+For both scaling methods, people in the civic conception have on average a higher mean value compared to the ethnic conception.
+While we are not able to formally test all forms of measurement invariance, a statistically significant mean indicates that the measurements are not equivalent.
 
@@
 
-We find that there are statistically significant differences between the two wordings. 
-An ethnic conception of the people, overall, yielded more agreement with the items in question. 
+We find that the measurement invariance assumption does not hold: 
+Using different wordings does not lead to equivalent measaures.
+Moreover, there are statistically significant differences between the two wordings. 
+We only varied the ethnic and civic conception for two items.
+It is likely to be more consequential in survey batteries that predominantly include items contrast 'the people' with elites to measure populist attitudes [for an overview of different batteries, see @castanho2020].
+The populist attitude scales proposed by @schulz2018 and @stanley2011, for instance, contain references to 'the people' in 7/9 and 7/8 of the items, respectively.
+
+An ethnic conception of the people, overall, yielded more agreement with the items in question -- but not with the latent construct. 
 This is effect is particularly pronounced for voters of the far right, as well as for older voters. 
@@
 
-Nevertheless, we found that a civic or an ethnic wording of items referring to 'the people' makes little difference in a latent construct that also comprises other items that were kept constant. 
-Yet, while this might make little difference in a latent construct that also comprises items that do not solely rely on items that juxtapose 'the people' with the elite, it is likely to be more consequential in survey batteries that predominantly include items contrast 'the people' with elites to measure populist attitudes [for an overview of different batteries, see @castanho2020].
-The populist attitude scales proposed by @schulz2018 and @stanley2011, for instance, contain references to 'the people' in 7/9 and 7/8 of the items, respectively.
-
 Importantly, the degree to which 'the people' is understood in denoting a specific ethno-cultural group likely differs across countries.
-This type of differential item interpretation might therefore lead to measurement invariance when used in cross-national research [@castanho2020]. 
+This type of differential item interpretation might therefore lead to even more measurement invariance when used in cross-national research [@castanho2020]. 
 In other words, if the ethno-cultural connotation of the the people varies across countries, this may hamper cross-national application of populist attitude scales that include multiple items referring to 'the people'.
@@
 In addition, our results suggest that an ethnic framing of the citizens runs the, albeit small, risk overestimating the degree of populist attitudes among more nativist citizens. 
-To avoid priming respondents with an ethnic conception of the people, future studies should consider using a civic conception of ''citizens vs. the elite" when measuring populist attitudes.
+To avoid priming respondents with an ethnic conception of the people, future studies should use a consistent ethnic or civic conception of the people when measuring populist attitudes, bearing in mind that the civic conception does lead to higher values on the scale.
 

### 2022-03-06 src/analysis/analyses.Rmd
testing measurement invariance

@@
 
-cfa2
+mi %>%
+  select(Models, AIC, BIC, `Chisq diff`, `Pr(>Chisq)`) %>%
+  kbl(booktabs =T, caption = "Measurement Invariance - CFA Models") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "5cm") %>%
+  column_spec(2, width = "3cm") %>%
+  column_spec(3, width = "3cm") %>%
+  column_spec(4, width = "3cm") %>%
+  column_spec(5, width = "3cm") 
 ```
@@
 irt4
+
+dat %>%
+  kbl(booktabs =T, caption = "Measurement Invariance - IRT Models") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "5cm") %>%
+  column_spec(2, width = "3cm") %>%
+  column_spec(3, width = "3cm") %>%
+  column_spec(4, width = "3cm") %>%
+  column_spec(5, width = "3cm") 
 ```
@@
 
-exp <- exp %>%
-  dplyr::select(estimate, lower, upper, scale = id, treatment = ethnic, y)
-kbl(exp, booktabs =T, caption = "Explanatory Power: Scales Predicting Populist Vote - OLS Regression") %>%
-  kable_styling(latex_options = c("striped", "hold_position"),
-                full_width = F, fixed_thead = T, position = "center") %>%
-  column_spec(1, width = "2cm") %>%
-  column_spec(2, width = "2cm")  %>%
-  column_spec(3, width = "2cm") %>%
-  column_spec(4, width = "4cm") %>%
-  column_spec(5, width = "4cm") %>%
-  column_spec(6, width = "4cm")
 ```
@@
   column_spec(6, width = "4cm")
+
 ```

### 2022-03-06 src/analysis/IRT.R

@@ -1,6 +1,6 @@
 packages <- c( "ltm", "GPArotation", "Hmisc", "mirt",
               "lattice","lordif", "semPlot",
-              "semTools", "nFactors", "corrr")
+              "nFactors", "corrr")
 for (p in packages) {
   if (p %in% installed.packages()[,1]) require(p, character.only=T)
   else {
@@ -234,3 +234,35 @@ irt4 <- d %>%
   scale_fill_manual(values = fig_cols) +
   theme(legend.position="none",
         legend.title = element_blank())
+
+
+# Measurement Invariance
+dat <- matrix(data = NA, nrow = dim(d)[1], ncol = 5)
+dat[,1] <- d$POST_1
+dat[,2] <- d$POST_2
+dat[,3] <- d$POST_3
+dat[,4] <- d$POST_5
+dat[,5] <- d$POST_6
+colnames(dat) <- c("item1", "item2", "item3", "item4", "item5")
+group <- d$ethnic
+group <- if_else(group==0, "C1", "E1")
+
+mod_configural <- multipleGroup(dat, 1, group = group)
+mod_metric <- multipleGroup(dat, 1, group = group, invariance=c('slopes')) #equal slopes
+mod_scalar2 <- multipleGroup(dat, 1, group = group, #equal intercepts, free variance and means
+                             invariance=c('slopes', 'intercepts', 'free_var','free_means'))
+mod_scalar1 <- multipleGroup(dat, 1, group = group, #fixed means
+                             invariance=c('slopes', 'intercepts', 'free_var'))
+
+
+a1 <- anova(mod_metric, mod_configural) #equal slopes only
+a2 <- anova(mod_scalar2, mod_metric) #equal intercepts, free variance and mean
+a3 <- anova(mod_scalar1, mod_scalar2) #fix mean
+
+dat <- a1[2,] %>% 
+  add_case(a2[2,]) %>% 
+  add_case(a3[2,]) %>% 
+  mutate(Models = c("Equal Slopes",
+             "Equal Slopes, Intercepts, Free Variance and Mean", 
+             "Equal Slopes, Intercepts, Free Variance and Fixed Mean")) %>% 
+  dplyr::select(Models, AIC, BIC, `LogLikelihood` = logLik, `Significant Difference` = p)

### 2022-03-06 src/analysis/additive-scale.R

@@ -4,6 +4,7 @@ as_e <- d %>%
                           POST_5 + POST_6)/5) %>%
   select(id, add_pa)
 
+
 as_df <- d %>%
   filter(ethnic == 0) %>%
   mutate(add_pa = (POST_1 + POST_2 + POST_3 + 
@@ -55,4 +56,3 @@ add2 <- d %>%
 
 d <- left_join(x = d, y = as_df, by = "id") %>%
   distinct()
-

### 2022-03-06 src/analysis/explorative_cfa.R

@@ -85,6 +85,27 @@ cfa2 <- d %>%
   theme(legend.position="none",
         legend.title = element_blank())
 
+
+## Multi group testing - measurement invariance
+# configural invariance
+fit1 <- cfa(pa_model, data = d, group = "ethnic")
+
+# weak invariance
+fit2 <- cfa(pa_model, data = d, group = "ethnic",
+            group.equal = "loadings")
+
+# strong invariance
+fit3 <- cfa(pa_model, data = d, group = "ethnic",
+            group.equal = c("intercepts", "loadings"))
+
+# model comparison tests
+mi <- lavTestLRT(fit1, fit2, fit3)
+
+mi <- tibble(mi) %>%
+  mutate(`Pr(>Chisq)` = as.numeric(`Pr(>Chisq)`),
+         Models = c("Configural Invariance",
+                    "Metric Invariance", "Scalar Invariance"))
+
 d <- full_join(x = d, y = cfa_df, by = "id") %>%
   distinct()
   

### 2022-03-06 src/lib/functions.R

@@ -13,6 +13,7 @@ library(sjlabelled)
 library(patchwork)
 library(qualtRics)
 library(lavaan)
+library(semTools)
 
 fig_cols <- yarrr::piratepal(palette = "basel", 
              trans = .2)

### 2022-03-06 report/draft.Rmd
testing measurement invariance

@@
 mi %>%
-  select(Models, AIC, BIC, `Chisq diff`, `Pr(>Chisq)`) %>%
+  select(`Equivalence Tests` = Models, AIC, BIC, `Chisq diff`, `Pr(>Chisq)`) %>%
+   filter(`Equivalence Tests` != "Configural Invariance") %>% 
   kbl(booktabs =T, caption = "\\label{tab:mi-cfa}Measurement Invariance - CFA Models") %>%
@@
 This scaling model shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see **Figure XX** and **XX** in the Appendix).
-While the means of the scales with the different conceptions of the people are not different, testing configural, metric and scalar invariance -- see Table \ref{tab:mi-irt} -- we see that the equal slope assumption (metric invariance) as well as one form of scalar invariance (i.e.
+While the means of the scales with the different conceptions of the people are not different, testing metric and scalar invariance -- see Table \ref{tab:mi-irt} -- we see that the equal slope assumption (metric invariance) as well as one form of scalar invariance (i.e.
 the one with free means) are not met.
@@
   add_case(a3[2,]) %>% 
-  mutate(`Equivalence Tests` = c("Equal Slopes",
-             "Equal Slopes, Intercepts, Free Variance and Mean", 
-             "Equal Slopes, Intercepts, Free Variance and Fixed Mean")) %>% 
+  mutate(`Equivalence Tests` = c("Metric Invariance",
+             "Scalar Invariance", 
+             "Scalar Invariance (Fixed Mean)")) %>% 
   dplyr::select(`Equivalence Tests`, AIC, BIC, `LogLikelihood` = logLik, `Significant Difference` = p)

### 2022-03-07 report/appendix.Rmd
update appendix

@@
   column_spec(2, width = "3cm")
+
+mi %>%
+  select(`Equivalence Tests` = Models, AIC, BIC, `Chisq diff`, `Pr(>Chisq)`) %>%
+   filter(`Equivalence Tests` != "Configural Invariance") %>% 
+  kbl(booktabs =T, caption = "\\label{tab:mi-cfa}Measurement Invariance - CFA Models") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "4cm") %>%
+  column_spec(2, width = "2cm") %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "2cm") %>%
+  column_spec(5, width = "2cm")   
 ```
@@
 ## IRT Analyse
-```{r "oa-irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide'}
+```{r "oa-irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide',message=FALSE,warning=FALSE}
 source(here("src/analysis/IRT.R"))
@@
 
-```{r "oa-irt2", fig.align="center", fig.height=8, fig.width=12}
+```{r "oa-irt2", fig.align="center", fig.height=8, fig.width=12,message=FALSE,warning=FALSE}
 kbl(irt3, booktabs =T, caption = "IRT Analysis") %>%
@@
   column_spec(2, width = "3cm")
+
+dat %>%
+  kbl(booktabs =T, caption = "\\label{tab:mi-irt}Measurement Invariance - IRT Models") %>%
+  kable_styling(latex_options = c("striped", "hold_position"),
+                full_width = F, fixed_thead = T, position = "center") %>%
+  column_spec(1, width = "4cm") %>%
+  column_spec(2, width = "2cm") %>%
+  column_spec(3, width = "2cm") %>%
+  column_spec(4, width = "2cm") %>%
+  column_spec(5, width = "4cm") 
 ```
@@
 source(here("src/analysis/predict-pop-vote-scales.R"))
-dv1 <- exp2 %>%
-  filter(y == "Voted: Populist Party") %>%
+dv1 <- exp %>%
+  dplyr::filter(y == "Voted: Populist Party") %>%
   dplyr::select(`Regression Coefficient` = estimate,
@@
 
-dv2<- exp2 %>%
-  filter(y == "Voted: AfD") %>%
+dv2<- exp %>%
+  dplyr::filter(y == "Voted: AfD") %>%
   dplyr::select(`Regression Coefficient` = estimate,
@@
 
-dv3 <- exp2 %>%
-  filter(y == "Voted: Left") %>%
+dv3 <- exp %>%
+  dplyr::filter(y == "Voted: Left") %>%
   dplyr::select(`Regression Coefficient` = estimate,
@@
 source(here("src/analysis/predict-pop-vote-items.R"))
-dv1 <- exp2 %>%
-  filter(y == "Voted: Populist Party") %>%
+dv1 <- exp %>%
+  dplyr::filter(y == "Voted: Populist Party") %>%
   dplyr::select(`Regression Coefficient` = estimate,

### 2022-03-07 report/draft.Rmd
update appendix

@@
 Additionally, we have estimated a graded Item Response Theory (IRT) analysis [see also @vanhauwaert2020].
-This scaling model shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see **Figure XX** and **XX** in the Appendix).
+This scaling model shows that `POP1` and `POP2` contribute slightly more information to the latent construct when the items are ethnically phrased, as opposed to a civic framing (see Figure A.5 and Table A.13 for more information in the OA).
 While the means of the scales with the different conceptions of the people are not different, testing metric and scalar invariance -- see Table \ref{tab:mi-irt} -- we see that the equal slope assumption (metric invariance) as well as one form of scalar invariance (i.e.
@@
                              invariance=c('slopes', 'intercepts', 'free_var','free_means'))
-mod_scalar1 <- multipleGroup(dat, 1, group = group, #fixed means
-                             invariance=c('slopes', 'intercepts', 'free_var'))
 
@@
 a2 <- anova(mod_scalar2, mod_metric) #equal intercepts, free variance and mean
-a3 <- anova(mod_scalar1, mod_scalar2) #fix mean
 
@@
   add_case(a2[2,]) %>% 
-  add_case(a3[2,]) %>% 
   mutate(`Equivalence Tests` = c("Metric Invariance",
-             "Scalar Invariance", 
-             "Scalar Invariance (Fixed Mean)")) %>% 
+             "Scalar Invariance")) %>% 
   dplyr::select(`Equivalence Tests`, AIC, BIC, `LogLikelihood` = logLik, `Significant Difference` = p)
@@
                 full_width = F, fixed_thead = T, position = "center") %>%
-  column_spec(1, width = "5cm") %>%
+  column_spec(1, width = "4cm") %>%
   column_spec(2, width = "2cm") %>%
@@
   column_spec(4, width = "2cm") %>%
-  column_spec(5, width = "3cm") 
+  column_spec(5, width = "4cm") 
 ```
 
-Moreover, we have created an additive scale (see Table **XX** in the OA), as well as constructed a scale using the approach of @wuttke2020whole -- i.e.
+Moreover, we have created an additive scale (see Table A.11 in the OA), as well as constructed a scale using the approach of @wuttke2020whole  (see Table A.12 in the OA) -- i.e.
 using the lowest value on one of the items that construe the latent construct.

### 2022-03-07 src/analysis/predict-pop-vote-items.R

@@ -2,7 +2,7 @@ Ethnic <- c(0,1)
 
 for(i in 1:length(Ethnic)){
   df <- d %>%
-    filter(ethnic == Ethnic[i]) %>%
+    dplyr::filter(ethnic == Ethnic[i]) %>%
     mutate(pop_vote = ifelse(D6 == "AfD", 1,
                              ifelse(D6 == "Left", 1, 0)),
            Linke_vote = ifelse(D6 == "Left", 1,0)) %>%
@@ -224,7 +224,7 @@ exp <- exp %>%
                 ethnic = dplyr::recode(ethnic,
                                        `1` = "Ethnic Conception",
                                        `0` = "Civic Conception")) %>%
-  filter(term == "scale") 
+  dplyr::filter(term == "scale") 
 
 exp1 <- exp %>%
   ggplot(aes(x = y, 

### 2022-03-07 src/analysis/predict-pop-vote-scales.R

@@ -20,7 +20,7 @@ Ethnic <- c(0,1)
 
 for(i in 1:length(Ethnic)){
     df <- d %>%
-    filter(ethnic == Ethnic[i]) %>%
+    dplyr::filter(ethnic == Ethnic[i]) %>%
     mutate(pop_vote = ifelse(D6 == "AfD", 1,
                       ifelse(D6 == "Left", 1, 0)),
            Linke_vote = ifelse(D6 == "Left", 1,0)) %>%
@@ -200,7 +200,7 @@ exp <- exp %>%
          ethnic = dplyr::recode(ethnic,
                                 `1` = "Ethnic Conception",
                                 `0` = "Civic Conception")) %>%
-  filter(term == "scale") 
+  dplyr::filter(term == "scale") 
 
 exp1 <- exp %>%
   ggplot(aes(x = y, 

### 2022-09-09 report/accepted-manuscript.Rmd
final version

--- 2022-03-07 report/draft.Rmd
@@
 title: "The People as 'Volk' or 'Bürger'? The Implications of Ethnic and Civic Conceptions of the People for the Measurement of Populist Attitudes"
-thanks: "Replication files are available on the author's Github account (https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).
-**Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: Maurits Meijers"
 author:
   - name: Maurits Meijers
-  affiliation: Radboud University Nijmegen
+  - affiliation: Radboud University Nijmegen
   - name: Mariken A.C.G. van der Velden
-  affiliation: Vrije Universiteit Amsterdam
+  - affiliation: Vrije Universiteit Amsterdam
+thanks: "Replication files are available on the author's Github account (https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).
+**Current version**: `r format(Sys.time(), '%B %d, %Y')`;"
 anonymous: FALSE
@@
 Yet, the people can be construed in ethnic terms or in civic terms.
-Using a novel wording experiment in Germany (N=6,713), we examine ethnic or civic conceptions of `the people' affect respondents' adherence agreement to key populist attitude items.
-We find that there are small, but statistically significant differences between items framed in an ethnic and a civic manner -- and that this differs per item.
+Using a novel wording experiment in Germany (N=7,034), we examine whether ethnic or civic conceptions of 'the people' affect respondents' adherence agreement to key populist attitude items.
+'_Volk_' in German has an ethno-nationalist connotation and has been used throughout history to signify 'ethnic Germans'.
+The concept '_Bürger_', or citizens, by contrast, lacks an ethnic undercurrent.
+Similar ethnic connotations of 'the people' are also common in other languages.
+We find that there are statistically significant differences between items framed in an ethnic and a civic manner -- and that this differs per item.
 This relationship is significantly moderated by respondents' degree of exclusive national identity and voting behaviour for the radical right.
-Our findings suggest that the way in which the people is conceptualized has important implications for the measurement of populist attitudes."
-keywords: "Experiment, Populist Attitudes"
+Our findings suggest that the way in which the people is conceptualized has important implications for the measurement of populist attitudes.
+When populist attitudes are measured with an ethnic understanding of the 'the people', the construct is biased toward right-wing populism, inhibiting the measurement of populism as a `thin-ideology'.
+Moreover, we demonstrate the importance of careful translations in comparative research, since some translated synonyms carry different meanings, and thereby change the concept under investigation."
+
+keywords: "Wording Experiment, Populist Attitudes, Scaling, Measurement Invariance, Populism"
 geometry: margin=1in
@@
 While in some  cultural contexts, there is no strong semantic difference between 'the people' and 'citizens' (e.g.
-in the English-speaking world), in other contexts, such as the Germanic one, 'the people' (i.e., _das Volk_) has a strong ethnic connotation.
+in the English-speaking world), in many other contexts, 'the people' (i.e., _das Volk_) has a strong ethnic connotation.
+For example, in Italian _il popolo_ has a stronger ethnic character than _i cittadini_ or _le persone_.
+In Polish the term _naród_ signifies the 'nation' as an ethnic group, compared to _społeczeństwo_ ('the public') [@zubrzycki2001we].
+While difference is particularly outspoken in German, the difference exists in more Germanic, Slavic and Roman languages.
 In the 1800s, the term _Volk_ and _völkisch_ became strongly associated with an ethnic and racial conception of 'Germanness'. 
 After World War I, the terms _Volk_ and _Volksdeutsche_ were used to describe a ethnically and culturally homogeneous German diaspora, who were citizens of different states after the Versailles Treaty of 1919 [@gosewinkel2003].
+_Das deutsche Volk_ was also used by the Nazis to delineate ethnic Germans from non-ethnic Germans.
+In 1935, poet and playwright Bertold Brecht therefore called for the use of _Bevölkerung_ ('population' or 'the public') instead of _Volk_ to to avoid the Nazis' "foul mysticism" [@brecht1993funf].
 
@@
 Yet one item in the @akkerman2014 scale contrasts 'the citizen' with 'politicians' (`POP4`) - an item that nonetheless contributes significantly to the latent construct of populism [@vanhauwaert2020].
-What is more, 'the people' has been translated differently in different translations of the populist attitude scale. 
+It is also likely that differences arise from inconsistencies across translations of they original survey items.
+For instance, 'the people' has been translated differently in different translations of the populist attitude scale.
 For instance, in the French context 'the people' has been translated as _le peuple_ in some items, but as _les citoyens_ in other items [@ivaldi2018]. 
@@
 In Italian, 'the people' is sometimes referred to as _il popolo_, and sometimes as _le persone_ [@castanho2020].
+In Polish, 'the people' has been measured as _społeczeństwo_ (`the public') and the more ethnic _naród_.
 
@@
 In this paper, we test the degree to which the populist attitude scale is invariant across civic and ethnic concpetions of the people: 
-That is, do people exposed to a civic conception of the people have a similar populist attitude score as people exposed to an ethnic one.
-While ideally opulist attitude scale captures populist ideation across different ideological predispositions (see the critique of @castanho2020 of populist item scales including nativist items), 'the people' is often construed in ethnic, cultural, or even racial terms on the (far) right and conceived of in more civic or economic terms on the (far) left.
-Using a wording experiment in Germany (`N=7,034`), we examine measurement invariance in multiple ways.
+That is, do people exposed to a civic conception of the people have a similar populist attitude score as people exposed to an ethnic one?
+This is important because populist attitudes aim to operationalize populism as a `thin ideology' as propagated by @mudde2004.
+This perspective posits that populism is usually combined with other, left- or right-wing, ideologies.
+Hence, the populist attitude scale should capture populist ideation across different ideological predispositions.
+In a similar vein, @castanho2020 criticize populist items scales which include nativist items.
+
+Using a wording experiment in Germany (`N=7,034`), we examine measurement invariance across ethic and civic conception of `the people'.
 First, we study whether an ethnic or a civic conception of the people affects respondents' agreement with the two items of the populist attitude scale that directly juxtapose 'the people' with the elites -- i.e.
@@
 scalar and strict invariance) [@hirschfeld2014improving].
-Given the more pronounced ethnic connotation with the concept of 'people' or _Volk_ in the German language, the German case is particularly suitable to tease out differences between ethnic and civic conceptions of the people in key populist attitude items.
+We show that the populist attitudes scale based on a civic conception is not the measurement equivalent of the one using the ethnic conception.
+The assumption of measurement invariance is thus not met. 
+Using an civic conception leads to higher scores on the populist attitude scale compared to using an ethnic conception.
+This suggest that the way in which the people is conceptualized has important implications for the measurement of populist attitudes as well as for its explanatory power.
+Our findings also suggest that political scientists should pay much more attention to the translations they commission for their surveys.
+While new survey items are carefully constructed, translations are often not put to the same scrutiny.
+We demonstrate that using some English synonyms (e.g.
+_Volk_ for the 'people') slightly changes the concept; instead of measuring populist attitudes, we introduce nativist as well as populist attitudes.
+Hence, by careless translations we run the risk of colluding the measure.
 
@@
 
-# Civic versus Ethnic Conception of "the People"
+# A Civic versus Ethnic Conception of "the People"
 To test whether an ethnic or civic framing of the people affects respondents' agreement with key populist items we conduct a wording experiment. 
@@
 We rely on a nationally representative sample of German citizens over 18 years old (`N=7,034`). 
-The sample is from an online panel provided by the survey company Respondi -- for an overview of all variables in the study, as well as the descriptive information, see Online Appendix (OA pp.
+Given the more pronounced ethnic connotation with the concept of 'people' or _Volk_ in the German language, the German case is particularly suitable to tease out differences between ethnic and civic conceptions of the people in key populist attitude items.
+Our sample is from an online panel provided by the survey company Respondi -- for an overview of all variables in the study, as well as the descriptive information, see Online Appendix (OA pp.
 A2-A6).
@@
 ```
-```{r results-h1,out.width = "99%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Differences in Ethnic and Civic Conceptions of the People"}
-knitr::include_graphics(here("report/figures", "h1-extra-1.png"))
+```{r results-h1,out.width = "85%", fig.align = 'center', fig.cap = "\\label{fig:results-h1}Differences in Ethnic and Civic Conceptions of the People"}
+knitr::include_graphics(here("report/figures", "h1-1.png"))
 ```
@@
 
-The left-hand panel of Figure \ref{fig:results-h1} shows the results of a difference of means test for the two treatment groups (ethnic vs.
+Figure \ref{fig:results-h1} shows the results of a difference of means test for the two treatment groups (ethnic vs.
 civic wording) for both items -- Table A.5 in the OA shows the coefficients.
@@
 Yet, as the results show, the difference is small in substantive terms.
-The right-hand panel of Figure \ref{fig:results-h1} indicates that the non-effect for `POP1` is driven by the fact that for younger age groups (younger than 50 years old) there is no difference for the civic and ethnic conception of the people, as indicated by the blue dots and whiskers in Figure \ref{fig:results-h1}.[^5]
-For the older population (50 years old and more), the right-hand panel of Figure \ref{fig:results-h1} demonstrates using an OLS regression, including an interaction between treatment and age groups, that for both `POP1` and `POP2`, people receiving the ethnic treatment report higher levels of agreement with the items compared to people receiving the civic treatment.
-The effect size is still small in substantive terms: between a 0.1 and 0.3 increase on a 5-point scale.
 
@@
 
-How does the effect of an ethnic conception of the people vis-à-vis a civic conception vary across respondents? 
+_How does the effect of an ethnic conception of the people vis-à-vis a civic conception vary across respondents?_
 The left-hand panel of Figure \ref{fig:results-h2} shows the results of an OLS regression analysis[^6] with the an interaction between the treatment and a variable measuring whether or not the respondent voted for the far right party _Alternative für Deutschland_ -- for more details see Table A.6 in the OA).
@@
 
-Does an ethnic and civic framing of the items `POP1` and `POP2` affect the measurement invariance assumption of the latent construct of populist attitudes? 
+In addition, we have explored how the effect of an ethnic conception of the people vis-à-vis a civic conception vary across age and region.
+People that are born during or closely after WWII  as well as people born and/or living in certain regions in Germany (e.g.
+the East or Bavaria) could potentially have a different reaction to the two conceptions of the people -- all figures can be found in the Online Appendix (Figure A-2, p.
+A9) as well as in our Online Research Compendium.
+**_Age_.** We demonstrate in the upper-left panel of Figure A-2 in the OA that for younger age groups (i.e.
+all age groups younger than 50 years old) there is no difference for the civic and ethnic conception of the people.
+Yet, for the older population (50 years old and more) we see that people receiving the ethnic treatment report higher levels of agreement with the items compared to people receiving the civic treatment for both `POP1` (''The politicians need to follow the will of the people''), the effect size is about half a point (i.e.
+half a standard deviation) and `POP2` (''the people, not politicians, should make the most important political decisions'').
+The effect size is still small in substantive terms: between a `0.1` and `0.3` increase on a 5-point scale.
+**_Region_.** We show in the upper-right panel of Figure A-2 in the OA that while for most regions in Germany, there is no statistically significant difference between receiving an ethnic or a civic treatment.
+Yet, for the regions Sleswig-Holstein (i.e.
+the region bordering Denmark) and Hessen (mid-Germany), we see that people receiving the ethnic treatment report lower levels of agreement with the items compared to people receiving the civic treatment for both `POP1` and `POP2`.
+The same effect holds for the region Bremen for `POP1` and for Berlin and North-Rhine Westphalia for `POP2`.
+This indicates that in Western districts, people are sensitive to the ethnic conception of the 'people' and all else equal, under-report their populist attitudes by approximately `0.5` points on a 5-point scale.
+
+We also explored whether the difference in civic and ethnic conception is only for voters of far right parties or also exists for people placing themselves on the edges of the ideological spectrum.
+An interaction between the treatment and ideological self-placement -- for more details see lower-left panel of Figure A-2 in the OA) -- demonstrates that for `POP1` (''The politicians need to follow the will of the people'') there is a positive, yet insignificant, relationship between ideology and receiving the ethnic treatment; i.e.
+the more right-wing, the higher your score on the item when receiving the ethnic treatment compared to the civic treatment.
+For `POP2` (''the people, not politicians, should make the most important political decisions''), we see the opposite: Left wing people report higher scores on this item when shown the ethnic conception of the people compared to the civic conception.
+Yet, the effect is substantially small, between approximately a `0.2` and `0.05` decrease on a 5-point scale.
+This effect is negative, meaning that the more right-wing, the smaller the difference between the score for the item for the two treatments.
+The effect becomes insignificant for an ideology score of 7 and higher.
+In addition, we explored the differences between those who are opponents and proponents of political pluralism, as the civic conception of the people might invite a more pluralistic view on who are included in the people.
+The lower-right panel of Figure A-2 in the OA demonstrates the opposite: Respondents who are negative towards political pluralism (i.e.
+low scores) that receive the ethnic treatment report lower levels of agreement with the items compared those who are positive towards political pluralism (i.e.
+high scores)  for both `POP1` and `POP2`.
+The effect is bigger for `POP2` than for `POP1`.
+
+_Does an ethnic and civic framing of  the items `POP1` and `POP2` affect the measurement invariance assumption of the latent construct of populist attitudes?_
+To answer this question, we cannot just compare the means of the group, since we would assume that the measures function similar in these different groups [e.g.
+see @hirschfeld2014improving; @van2021methods; @bieda2017universal].
+We therefore need to test the degree to which measures are invariant across groups.
+To do so, Multiple-Group Confirmatory Factor Analysis (MG-CFA) has become the de-facto standard in psychology [@chen2008happens].
 We first test the measurement variance in a Confirmatory Factor Analysis (see Table A.9 in the OA). 
@@
 Moreover, when testing metric and scalar invariance -- i.e.
-is the magnitude of loadings similar accross groups or are the magnitude of loadings and the intercept difference accross groups -- we find statistical significant Chi-square differences for the metric invariance and scalar invariance models, shown in Table \ref{tab:mi-cfa}.
-This indicates that the assumption that the different conceptions of the people function similar is not met.
+is the magnitude of loadings similar across groups or are the magnitude of loadings and the intercept difference across groups -- we find statistical significant Chi-square differences for the metric invariance and scalar invariance models, shown in Table \ref{tab:mi-cfa}.
+This indicates that the assumption that the different conceptions of the people function similarly is not met.
 
@@
 the one with free means) are not met.
-This indicates that even varying the wording of ‘the people’ in two items of the full @akkerman2014 item battery is enough to demonstrate that the scales are not equivalent anymore.
+This indicates that even varying the wording of 'the people' in two items of the full @akkerman2014 item battery is enough to demonstrate that the scales are not equivalent anymore.
 
@@
 # Conclusion
-Existing populist attitudes scales have been inconsistent in using 'ethnic' or 'civic' conceptions of the people. 
-Using a wording experiment we examined whether German respondents presented with an ethnic framing of 'the people' (_das Volk_) answered key populist attitude items differently than respondents who recevied an ethnic framing of `the people' as citizens (_Bürger_).
+The populist attitude construct aims to operationalize populism as a thin-centered ideology on the individual level [@akkerman2014; @hawkins2012].
+From this perspective, populist ideation is present both on the left and the right side of the political spectrum.
+The concept 'the people' is an empty signifier that is discursively filled in different ways by left- and right-wing populists.
+Therefore it is important that the 'populist attitudes' construct is not biased toward one group or the other.
+Yet, existing populist attitudes scales have been inconsistent in using 'ethnic' or 'civic' conceptions of the people.
+Moreover, in many languages, the concept of `the people` has a clear ethnic connotation.
+This could hinder individual-level measurement of populism as a thin-centred ideology.
+
+Using a wording experiment, we therefore examined whether German respondents presented with an ethnic framing of 'the people' (_das Volk_) answered key populist attitude items differently than respondents who recevied an ethnic framing of `the people' as citizens (_Bürger_).
 
@@
 
-An ethnic conception of the people, overall, yielded more agreement with the items in question -- but not with the latent construct. 
-This is effect is particularly pronounced for voters of the far right, as well as for older voters. 
-The difference between an ethnic and a civic conception of the people was also only significant for respondents who adhered a moderate to high level of exclusive national identity. 
-This finding is highly suggestive of the 'ethnic' interpretation of `the people' -- at least in the German language.
+While respondents receiving the items with an ethnic conception of the people scored overall higher on the items, their overall score on the populist attitude scale was not higher (shown in OA pp.A10--A13).
+The higher levels of agreement with the items displaying an ethnic conception of the people is particularly pronounced for voters of the far right (shown in the left panel of Figure 2), as well as for older voters (shown in OA pp.A8--A9).
+The difference between an ethnic and a civic conception of the people in the items was also only significant for respondents who adhered a moderate to high level of exclusive national identity (shown in OA pp.A8--A9).
+This finding is highly suggestive of the 'ethnic' interpretation of `the people' -- at least in the German language -- thereby conflating populism with nationalism.
 
@@
 
-One can argue theoretically that 'the people' captures the meaning of the concept of populism better than 'citizens'. 
+Crucially, our findings suggest that populist attitude scales that rely on ethnic measures of 'the people' might not be entirely appropriate for measuring populism as thin-ideology that attaches itself to both inclusive and exclusionary ideologies.
+What is more, While (ethnic) nationalism and populism often go hand in hand, it is important that we keep both concepts analytically distinct, both conceptually and empirically [@bonikowski2017ethno].
+An ethnic priming of 'the people' in the populist attitudes scale, makes it more difficult to keep ethnic nationalism and populism distinct.
+
+One could argue theoretically that 'the people' captures the meaning of the concept of populism better than 'citizens'. 
 After all, it populism assumes the people to be a homogeneous entity. 
 Yet, our findings suggest that also a civic framing of the concept yields a satisfactory model fit when estimating a Confirmatory Factor Analysis. 
-In addition, our results suggest that an ethnic framing of the citizens runs the, albeit small, risk overestimating the degree of populist attitudes among more nativist citizens. 
+In addition, our results suggest that an ethnic framing of the citizens runs the risk overestimating the degree of populist attitudes among more nativist citizens. 
 To avoid priming respondents with an ethnic conception of the people, future studies should use a consistent ethnic or civic conception of the people when measuring populist attitudes, bearing in mind that the civic conception does lead to higher values on the scale.
+
+What is more, our results suggest that political scientists should be careful when commissioning translations of survey items.
+While different translations of key concepts may seem equivalent to non-specialists, our findings show that such nuances can yield measurement invariance - impeding comparison across countries.
 

### 2022-09-09 report/online-appendix.Rmd
final version

--- 2022-03-07 report/appendix.Rmd
@@
 options(scipen = 1, digits = 2)
+knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
 # Uncomment below if you want code captions
@@
 # Pre-Registered and Explorative Analysis
+## Differences in Ethnic and Civic Conceptions of the People
 Table \ref{tab:h1} demonstrates the results as visualized in Figure 1 in the paper.
+
 ```{r "h1", fig.align="center", fig.height=5, fig.width=6}
@@
 
-kbl(p1, booktabs =T, caption = "\\label{tab:h1}Table Results H1") %>%
+kbl(p1, booktabs =T, caption = "\\label{tab:h1}Differences in Ethnic and Civic Conceptions of the People") %>%
   kable_styling(latex_options = c("striped", "hold_position"),
@@
   column_spec(3, width = "4cm")
-
 ```
@@
 
+## Average Marginal Effects for Ethnic Conception of the People
 Table \ref{tab:h2a} and \ref{tab:h2b} demonstrate the results as visualized in Figure 2 in the paper.
@@
 
-kbl(h2a, booktabs =T, caption = "\\label{tab:h2a}Table Results H2a") %>%
+kbl(h2a, booktabs =T, caption = "\\label{tab:h2a}Average Marginal Effects for Ethnic Conception of the People") %>%
   kable_styling(latex_options = c("striped", "hold_position"),
@@
   column_spec(5, width = "2cm")
+```
+
+## Exploration with Age, Region, Ideoligy and Attitude towards Political Pluralism
+```{r results-explor, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-h2}Average Marginal Effects for Ethnic Conception of the People"}
+knitr::include_graphics(here("report/figures", "explorative-2.png"))
 ```
@@
 ```
+
+\newpage
 ## Additive scale
@@
 
+\newpage
 ## Wüttke et al. Approach
@@
 
+\newpage
 ## IRT Analyse
@@
 ```
+
+\newpage
+# References

### 2022-09-09 src/analysis/analyses.Rmd
final version

@@
 
-#(pe2 + pe3)/ (pe4 + pe5)
+(pe2 + pe3)/ (pe4 + pe5)
 ```
 
-```{r "h1-extra", fig.align="center", fig.height=6, fig.width=12, echo = FALSE, fig.show = "hide"}
+```{r "h1-extra", fig.align="center", fig.height=6, fig.width=12, echo = FALSE, fig.show = "hide", eval = FALSE}
 p1 + pe2 + 

### 2022-09-09 report/old_text.R

@@ -1,105 +1,0 @@
-# Data, Measurement & Method
-To investigate whether a civic or ethnic conception of the people influences the populist attitude constructs, we conducted a survey experiment in Germany between the 13th of October 2021 and the 11th of November 2021.
-The sample, recruited through [Respondi](https://www.respondi.com/EN/), consists of 8,000 participants of 18 years and older.
-Respondi works with opt-in respondents, so we have implemented quota on age, gender, and education.
-Moreover, we measured some more demographic background variables.
-Balance checks are conducted to demonstrate whether certain categories are over represented in a certain experimental group (see [the Methods Section](#method), Figure \ref{fig:balance}).
-  The study has been approved by the [Research Ethics Review Committee](https://fsw.vu.nl/nl/onderzoek/research-ethics-review/index.aspx) of the \textit{Vrije Universiteit Amsterdam} (see the approval [here](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes/blob/master/docs/pap/pap.pdf)).
-  To ensure good quality of our data, two attention checks are included.
-  All variables and their operationalization have been described in our [pre-analysis plan](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes/blob/master/docs/pap/pap.pdf).
-  
-  The dependent variables under study are the three of the six items measuring populist attitudes that mention _the people_: 1) _The people, not politicians, should make the most important political decisions_; 2) _The politicians in the German Bundestag need to follow the will of the people_; and 3) _The political differences between elites and the people are greater than the differences among citizens_.
-We rely on those three items in the populism scale, see Table \ref{tab:dv} in the [Appendix](# Appendix A. Wording of the questionaire) for the exact phrasing of the question.
-  Each item is measured on a 5-point likert scale: from `very much disagree` (value of `0`) till `very much agree` (value of `5`).
-  The average for each of the items lies between 3 and 4 (with a standard deviation around 1, as shown in Table \ref{tab:descr-dv}), meaning that people are neutral till positive about these statements. 
-  
-  ```{r descriptive-table, echo = FALSE}
-  rm(list=ls())
-  here::i_am("report/draft.Rmd")
-  source(here::here("src/lib/functions_draft.R"))
-  load(here("data/intermediate/cleaned_experiment.RData"))
-  source(here("src/analysis/data-for-analyses.R"))
-  
-  descr <- d %>%
-    select(matches("POST_[234]")) %>%
-    pivot_longer(cols = everything()) %>%
-    mutate(Variable = recode(name,
[…]

### 2022-09-09 src/lib/functions.R

@@ -267,7 +267,7 @@ regression7 <- function(df, scale){
   return(m)
 }
 
-theme_ipsum <- function(base_family="Arial Narrow", base_size = 11.5,
+theme_ipsum <- function(base_family="Arial Narrow", base_size = 14,
                         plot_title_family=base_family, plot_title_size = 18,
                         plot_title_face="bold", plot_title_margin = 10,
                         subtitle_family=base_family, subtitle_size = 12,
@@ -277,7 +277,7 @@ theme_ipsum <- function(base_family="Arial Narrow", base_size = 11.5,
                         caption_family = base_family, caption_size = 9,
                         caption_face = "italic", caption_margin = 10,
                         axis_text_size = base_size,
-                        axis_title_family = subtitle_family, axis_title_size = 9,
+                        axis_title_family = subtitle_family, axis_title_size = 12,
                         axis_title_face = "plain", axis_title_just = "rt",
                         plot_margin = margin(30, 30, 30, 30),
                         grid_col = "#cccccc", grid = TRUE,

### 2022-09-09 report/accepted-manuscript.Rmd
final version

@@
   - affiliation: Vrije Universiteit Amsterdam
-thanks: "Replication files are available on the author's Github account (https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).
+thanks: "Replication files are available on the author's Github account (https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes).
 **Current version**: `r format(Sys.time(), '%B %d, %Y')`;"
@@
 [^1]: A scale is measurement invariant across groups if subjects with identical levels of the latent construct have the same expected raw-score on the measure [@drasgow1985equivalence].
-[^2]: All analytical material for replication can be found in our online Research Compendium: https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md (anonymized for the review process).
+[^2]: All analytical material for replication can be found in our online Research Compendium: https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes.
 
@@
 
-[^3]: A power analysis is conducted and reported on our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md).
+[^3]: A power analysis is conducted and reported on our [Online Research Compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes).
 
@@
 We randomize whether respondents received a ethnic framing (i.e., with reference to 'the people; or _das Volk_) or a civic framing (i.e., with reference to 'citizens', or _Bürger_). 
-A balance test, reported in our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md), demonstrates that the allocation of the treatment was fully random.
+A balance test, reported in our [Online Research Compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes), demonstrates that the allocation of the treatment was fully random.
 The upper two items in Table \ref{tab:popatt} shows the differences in wording for the two items `POP1` and `POP2` in English and German. 
@@
 
-[^5]: Our [Online Research Compendium](https://anonymous.4open.science/r/wording-experiment-populist-attitudes-F3B2/README.md) demonstrates that there are no other socio-demographic variables that mediate the effect.
+[^5]: Our [Online Research Compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes) demonstrates that there are no other socio-demographic variables that mediate the effect.
 
@@
 the East or Bavaria) could potentially have a different reaction to the two conceptions of the people -- all figures can be found in the Online Appendix (Figure A-2, p.
-A9) as well as in our Online Research Compendium.
+A9) as well as in our [Online Research Compendium](https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes).
 **_Age_.** We demonstrate in the upper-left panel of Figure A-2 in the OA that for younger age groups (i.e.

### 2022-09-09 report/accepted-manuscript.Rmd
final version

@@
   - affiliation: Vrije Universiteit Amsterdam
-thanks: "Replication files are available on the author's Github account (https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes).
-**Current version**: `r format(Sys.time(), '%B %d, %Y')`;"
+thanks: "Replication files are available on the author's Github account (https://github.com/MarikenvdVelden/wording-experiment-populist-attitudes); Authorship order is alphabetical due to equal contribution.
+_Current version accepted at European Journal of Political Research_"
 anonymous: FALSE
